### 2024-02-20 manuscript/paper.tex
Added stirrer in particle dispersion example (2d)

\documentclass[preprint,12pt]{elsarticle}
% \documentclass[draft,12pt]{elsarticle}

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{relsize}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[section]{placeins}
\usepackage{booktabs}
\usepackage{url}

% For the TODOs
\usepackage{xcolor}
\usepackage{xargs}
\usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
\newcommand{\todoin}{\todo[inline]}
% from here: https://tex.stackexchange.com/questions/9796/how-to-add-todo-notes
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}

%Boldtype for greek symbols
\newcommand{\teng}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\ten}[1]{\ensuremath{\mathbf{#1}}}

\usepackage{lineno}
% \linenumbers

\journal{}

\begin{document}

\begin{frontmatter}

  \title{}
  \author[XXX]{Dinesh Adepu\corref{cor1}}
  \ead{d.dinesh@surrey.ac.uk}
  \author[University of Surrey]{Chuan Yu Wu}
  \ead{XXX}
\address[xxx]{xxx}

\cortext[cor1]{Corresponding author}

\begin{abstract}
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
{xxx}, {xxx}, {xxx}

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

% \linenumbers

\section{Governing equations}

\begin{equation}
  \label{eq:ce}
  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
\end{equation}
and conservation of linear momentum,
\begin{equation}
  \label{eq:me}
  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
  + g_i,
\end{equation}
where $\rho$ is the density, $u_i$ is the $i$\textsuperscript{th} component of
the velocity field, $x_j$ is the $j$\textsuperscript{th} component of the
position vector, $g_i$ is the component of body force per unit mass and
$\sigma_{ij}$ is stress tensor.

The stress tensor is split into isotropic and deviatoric parts,
\begin{equation}
  \label{eq:stress_tensor_decomposition}
  \sigma_{ij} = - p \; \delta_{ij} + \sigma'_{ij},
\end{equation}
%
where $p$ is the pressure, $\delta_{ij}$ is the Kronecker delta function, and
$\sigma'_{ij}$ is the deviatoric stress.

The Jaumann's formulation for Hooke's stress provides us with the rate of
change of deviatoric stress,
\begin{equation}
  \label{eq:jaumann-stress-rate}
  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
  \dot{\epsilon}_{kk} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
  \Omega_{ik} \sigma^{'}_{kj},
\end{equation}
where $G$ is the shear modulus, $\dot{\epsilon}_{ij}$ is the strain rate tensor,
\begin{equation}
  \label{eq:strain-tensor}
  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
  \frac{\partial u_j}{\partial x_i} \bigg),
\end{equation}
and $\Omega_{ij}$ is the rotation tensor,
\begin{equation}
  \label{eq:rotational-tensor}
  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
  \frac{\partial u_j}{\partial x_i} \bigg).
\end{equation}

For a weakly-compressible or incompressible fluid, a viscous force is added:
\begin{equation}
  \label{eq:fluid-stress-decomposition}
  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
\end{equation}
where $\eta$ is the kinematic viscosity of the fluid.

In both fluid and solid modelling the pressure is computed using an
isothermal equation of state, given as,
\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively. For solids,
$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
Poisson ratio, $E$ is the Young's modulus.

\section{Smoothed Particle Hydrodynamics}
In the current section, we introduce the basics of smoothed particle
hydrodynamics. A fundamental overview of the discrete approximations of
function, derivative, and divergence is discussed.

\subsection{Function Approximation}
From the dirac delta function definition, the function value of a smooth
function $A$ defined over a domain $\Omega$ at point $x$ can be written as
\begin{equation}
  \label{eq:dirac_repr}
  A(\ten{x}) = \int_{\Omega}\> A(\ten{x}') \> \delta(\ten{x} - \ten{x}') \> d\ten{x}',
\end{equation}
where $\delta(\ten{x} - \ten{x}')$ is a Dirac-delta function with
\begin{equation}
  \label{eq:unity}
  \int_{\Omega}\> \delta(\ten{x}) \> d\ten{x} = 1.
\end{equation}
In SPH, the Dirac delta function is replaced with a compact, smooth function $W$,
chosen to be as an even function. The function value of $A$ at $\ten{x}$
interpolated with the smooth kernel $W$ is given by
\begin{equation}
  \label{eq:kernel_repr}
  A(\ten{x}) = \int_{\Omega}\> A(\ten{x}') \> W(\ten{x} - \ten{x}', h)  \> d\ten{x}' + O(h^2).
\end{equation}
Here, kernel $W$ satisfies the following conditions,
\begin{equation}
  \label{eq:unity}
  \int_{\Omega}\> W(\ten{x} - \ten{x}', h)  \> d\ten{x}' = 1.
\end{equation}

\begin{equation}
  \label{eq:kernel_delta}
  \lim_{h \to 0} W(\boldsymbol{x} - \boldsymbol{x}', h) = \delta(\boldsymbol{x} - \boldsymbol{x}', h).
\end{equation}
\begin{equation}
  \label{eq:compact_support}
  W(\boldsymbol{x} - \boldsymbol{x}', h) = 0 \>\>\>\>    \text{when}  \>\>\> |\boldsymbol{x} - \boldsymbol{x}'| > kh.
\end{equation}
Here k is a constant, which determines the the non-zero region $W$ for a point
at position vector $\boldsymbol{x}$. In the current work we have used Quintic
% spline in all our simulation cases. Quintic spline \parencite{Violeau16}, is
given as,
\begin{equation}
  \label{eq:quintic_spline}
  W(r, h) =
  \begin{cases}
    \sigma_5\left( (3-q)^5 - 6(2-q)^5 + 15(1-q)^5 \right), & \textrm{for} \ 0\leq q \leq 1,\\
    \sigma_5\left( (3-q)^5 - 6(2-q)^5 \right), & \textrm{for} \ 1 <  q \leq 2,\\
    \sigma_5 \ (3-q)^5 , & \textrm{for} \ 2 < q \leq 3,\\
    0, & \textrm{for} \ q>3,
  \end{cases}
\end{equation}
This type of interpolation leads to a 2nd order function accuracy
% \parencite{fatehi2011error}.

Assume that the domain is discretized into N particles with mass
$m_i$ and volume $\Delta v_i$, We have
\begin{equation}
  \label{eq:mass_repr}
  m_j = \Delta v_i \> \rho_i.
\end{equation}
Using \eqref{eq:mass_repr}, \eqref{eq:kernel_repr} is converted to
discrete form as follows
\begin{equation}
  \label{eq:discrete_form}
  A_i = \sum_{j \in \text{Neigh}(i)}\> \frac{m_j}{\rho_j} A_j\> W(\ten{x}_i - \ten{x}_j, h),
\end{equation}
where $A(\boldsymbol{x}_i) = A_i$ is the value of the field property of particle
i, similarly for $A_j$. Here, $\text{Neigh}(i)$ is the neighbours of particle $i$.

\subsection{Derivative Approximation}
% The discretized form of the derivative approximation~\parencite{Violeau16} is given
as,
\begin{equation}
  \label{intro:eq:derivative-discrete_form}
  \nabla A(\ten{x}_i) = \sum_j\> \frac{m_j}{\rho_j} A_j\> \nabla W(\ten{x}_i - \ten{x}_j, h).
\end{equation}

An alternative expression of the derivative approximation is derived by employing
density, i.e,
\begin{equation}
  \label{intro:eq:sph-continu-derivative-final}
  \nabla (A \rho^n) = n A \rho^{n - 1} \nabla \rho + \rho^n \nabla A,
\end{equation}
where $n$ is a real number. The new identity for the derivative of $A$ is
\begin{equation}
  \nabla A = \frac{1}{\rho^n} \left[ n A \rho^{n - 1} \nabla \rho + \rho^n \nabla A  \right],
\end{equation}
using \cref{eq:discrete_form,intro:eq:derivative-discrete_form}, the new
derivative approximation can be written as
\begin{equation}
  \label{intro:eq:derivative-discrete_form}
  \nabla A(\ten{x}_i) = \frac{1}{\rho^n(\ten{x}_i)} \sum\>
  m_j \left(A_j \rho^{n-1}(\ten{x}_j) - n A_i \rho^{n-1}(\ten{x}_i) \right)\> \nabla W(\ten{x}_i - \ten{x}_j, h).
\end{equation}
In the current work, we use a symmetric expression, with $n=-1$, resulting in
\begin{equation}
  \nabla A(\ten{x}_i) = \rho_i \sum_{j} m_j \left(\frac{A_i}{\rho_i^2} + \frac{A_j}{\rho_j^2}\right) \nabla W_{ij}.
\end{equation}
A symmetric gradient operator ensures equal and opposite forces acting on the
particles.

\subsection{Divergence Approximation}
We now look at an SPH approximation of the divergence operator. An approximation
of the divergence operator is used to discretize the \cref{eq:ce}. It is given
as,
\begin{equation}
  \label{intro:eq:discrete_derivative}
  \nabla \cdot \ten{v}_i = \sum\> \frac{m_j}{\rho_j} \ten{v}_j \cdot \nabla W(\ten{x}_i - \ten{x}_j, h).
\end{equation}
Similar to the derivative approximation, we utilize the following identity to approximate the divergence operator,
\begin{equation}
  \label{intro:eq:sph-continu-div-intermediate}
  \nabla \cdot (\ten{v} \rho^n) = \rho^n \nabla \cdot \ten{v} + n  \rho^{n - 1} \ten{v} \cdot \nabla \rho.
\end{equation}
In the current work, we employ expression for $n=1$. The discrete SPH approximation for $n=1$ is given as
\begin{equation}
  \label{intro:eq:sph-continu-div-final}
  \nabla \cdot \ten{v}(\ten{x}_i) = \frac{1}{\rho_i} \sum_{j} m_j \left(\ten{v}_j - \ten{v}_i\right) \cdot \nabla W_{ij}.
\end{equation}

\subsection{SPH Discretization}\label{sec:ctvf-sph-equations}

In the current work, both fluid and solid modelling uses the same continuity
and pressure evolution equation. The SPH discretization of the continuity
equation~\eqref{eq:ce-tvf} and the pressure evolution
equation~\eqref{eq:edac-p-evolve} respectively are,
\begin{equation}
  \label{eq:sph-discretization-continuity}
  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
  (\rho \; (\tilde{\ten{u}} \; - \;
  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
\end{equation}

\begin{multline}
  \label{eq:sph-discretization-edac}
  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; + \;
  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
  4 \; \nu_{edac}
  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + 0.01 h_{ab}^{2})} \ten{r}_{ab}
  \bigg) \; \cdot \nabla_{a} W_{ab}.
\end{multline}
%
Similarly, the discretized momentum equation for fluids is written as,
\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
  \bigg) \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
  \ten{g}_{a},
\end{multline}
where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
% fluid and \textcite{morris1997modeling} formulation is used to discretize the
viscosity term.

We add to the momentum equation an additional artificial viscosity term
% $\Pi_{ab}$~\parencite{monaghan-review:2005} to maintain the stability of the
numerical scheme, given as,
\begin{align}
  \label{eq:mom-av}
  \Pi_{ab} =
  \begin{cases}
\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
\end{cases}
\end{align}
where,
%
\begin{equation}
  \label{eq:av-phiij}
  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
\end{equation}
%
where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
viscosity parameter.

%
For solid mechanics the momentum equation is written as,
\begin{equation}
  \label{eq:sph-momentum-solid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
  \ten{g}_{a},
\end{equation}
we have not considered the correction stress term $\ten{A}$ in momentum
equation of solid mechanics as it has a negligible effect.

In addition to these three equations, the Jaumann stress rate equation is also
solved. In the current work we use the momentum velocity $\ten{u}$ rather than
% $\tilde{\ten{u}}$ as in the GTVF~\parencite{zhang_hu_adams17} in the computation of
gradient of velocity. The SPH discretization of the gradient of velocity is
given as,
\begin{equation}
  \label{eq:sph-vel-grad}
  \nabla \ten{u}_a =
  - \sum_{b} \frac{m_b}{\rho_{b}} (\ten{u}_{a} - \ten{u}_{b}) \otimes (\nabla_{a} W_{ab}),
\end{equation}
where $\otimes$ is the outer product.

The SPH discretization of the modified Jaumann stress rate
\cref{eq:modified-jaumann-stress-rate} is given as,
\begin{multline}
  \label{eq:sph-modified-jaumann-stress}
  \frac{\tilde{d}\teng{\sigma}^{'}_{a}}{dt} = 2G (\dot{\teng{\epsilon}}_{a} -
  \frac{1}{3} \dot{\teng{\epsilon}}_{a} \ten{I}) + \teng{\sigma}^{'}_{a}
  \teng{\Omega}_{a}^{T} +
  \teng{\Omega}_{a} \teng{\sigma}^{'}_{a} + \\
  + \sum_{b} \; \frac{m_b}{\rho_{b}} \; (\teng{\sigma}^{'} \otimes (\tilde{\ten{u}} -
  \ten{u}))_{ab} \; \cdot \nabla_{a} W_{ab}
  + \teng{\sigma}^{'}_{a} \sum_{b} \; \frac{m_b}{\rho_{b}} \;
  (\tilde{\ten{u}} - \ten{u})_{ab} \; \cdot \nabla_{a} W_{ab}.
\end{multline}

\FloatBarrier%
\section{Rigid body modeling}
\label{sec:conclusions}

\FloatBarrier%
\section{Numerical Methodology}
\label{sec:rfc:rbd}
% The rigid body is discretized into particles with equal spacing each particle
% with mass $m_i$ and density $\rho_i$. Rigid body has a total 6 degrees of
% freedom (DOF), divided into $3$ translational and $3$ rotational.
The equations governing the dynamics of a rigid body are, balance of linear and
angular momentum given by,
\begin{equation}
  \label{eq:rfc:balance_linear_mom}
  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i,
\end{equation}
\begin{equation}
  \label{eq:rfc:balance_angular_mom}
  \frac{d \ten{L}}{d t} = \teng{\tau}_{cm},
\end{equation}
where $M$, $\ten{v}_{cm}$ are the mass and velocity of the center of mass of the rigid body.
$\ten{F}_i, \teng{\tau}_{cm}, \ten{L} $ are force acting at point $i$, torque and
angular momentum about the center of mass of the rigid body. In the current
case, force acting on the particle $i$, $\ten{F}_i$, is due to the interaction
with the other bodies and with the fluid particles, and any other body forces.
The torque $\teng{\tau}_{cm}$ and angular momentum $\ten{L}$ are computed as,
\begin{equation}
  \label{eq:rfc:torque}
 \teng{\tau}_{cm} = \sum_i \ten{F}_i \times (\ten{x}_{cm} - \ten{x}_{i}),
\end{equation}
\begin{equation}
  \label{eq:rfc:moi}
  \teng{L} =
  \sum_i \; \ten{r}_i \times \; (\teng{\omega} \times \ten{r}_i)
  = \sum_i \; m_i \; [(\ten{r}_i \cdot \ten{r}_i) \ten{I} - \ten{r}_i \otimes \ten{r}_i].
\end{equation}
Here $\ten{x}_{cm}$ and $\omega$ are the position of the center of mass and
angular velocity of the rigid body. $m_i$, $\ten{x}_{i}$, $\ten{r}_i$ are the
mass, position of particle, and position of particle $i$ with respect to vector
center of mass.

% \begin{figure}[!htpb]
%   \centering
%   \includegraphics[width=0.7\textwidth]{images/rfc/images/rigid_body/rigid_body}
%   \caption{Body frame and local frame description of rigid body}
%   \label{fig:gloabl_body_frame_rb}
% \end{figure}
We use two coordinate frames to capture the dynamics of the rigid body, a
global frame and a body frame as shown in
\cref{fig:gloabl_body_frame_rb}. The body fixed frame, which moves with
rigid body is always located at the center of mass ($\ten{x}_{cm}$). The
state of the rigid body at a given time ($t$) can be described using position
($\ten{x}_{cm}$) and velocity ($\ten{v}_{cm}$) of the center of mass, a
rotation matrix($\ten{R}$) to represent the orientation of the rigid body with
respect to the global frame, and angular velocity($\teng{\omega}$). The center
of mass is computed as
\begin{equation}
  \label{eq:rfc:center_of_mass}
  \ten{x}_{cm} = \frac{\sum_i m_i \; \ten{x}_{i} }{\sum_i m_i }.
\end{equation}
The position of the discretized particle ($i$) in
\cref{fig:gloabl_body_frame_rb} belonging to the rigid body at time $t$ can be
computed as,
\begin{equation}
  \label{eq:rfc:rb_particle_pos_update}
  \ten{x}_i = \ten{x}_{cm} + \ten{r}_{i},
\end{equation}
with
\begin{equation}
  \label{eq:rfc:rb_particle_pos_update}
  \ten{r}_i = \ten{R} \overline{\ten{r}}_{i}.
\end{equation}
Here $\overline{\ten{r}}_{i}$ is the position of the particle $i$ about the body
frame axis and remains constant through out the simulation. The rotation matrix
$\ten{R}$ is used to bring the body frame position vector to the global frame
$\ten{O}$. Similarly the velocity vector is computed as,
\begin{equation}
  \label{eq:rfc:rb_particle_vel_update}
  \ten{v}_i = \ten{v}_{cm} + \teng{\omega} \times \ten{r}_{i}.
\end{equation}

We evolve the state of the rigid body through the integration of the
\cref{eq:rfc:balance_linear_mom,eq:rfc:balance_angular_mom}. The linear velocity of the
center of mass ($\ten{v}_{cm}$) and angular momentum ($\ten{L}$) at the next
timestep are computed as,
\begin{equation}
  \label{eq:rfc:lin_vel_cm_update}
  \ten{v}_{cm}^{n+1} = \ten{v}_{cm}^{n} + \frac{\ten{F}_{cm}}{M} \; \Delta t,
\end{equation}
\begin{equation}
  \label{eq:rfc:ang_mom_update}
  \ten{L}^{n+1} = \ten{L}^{n} + \teng{\tau}_{cm} \; \Delta t.
\end{equation}
Here, $\ten{F}_{cm} = \sum_i \ten{F}_i$.

The position of the center of mass and the rotation matrix ($\ten{R}$) are updated
by,
\begin{equation}
  \label{eq:rfc:lin_pos_cm_update}
  \ten{x}_{cm}^{n+1} = \ten{x}_{cm}^{n} + \ten{v}_{cm}^{n} \; \Delta t,\\
  \ten{R}^{n+1} = \ten{R}^{n} + \tilde{\teng{\omega}}^{n} \, \ten{R}^{n} \; \Delta t,
\end{equation}
where $\tilde{\teng{\omega}}^{n}$ is matrix formulation of angular velocity
$\omega$. The angular velocity at the new time step is computed with
\begin{equation}
  \label{eq:rfc:ang_velocity_update}
  \teng{\omega}^{n+1} = (\textit{\teng{I}}^{-1})^{n+1} \; \ten{L}^{n+1}.
\end{equation}
Here, moment of inertia at the new time step is computed as,
\begin{equation}
  \label{eq:rfc:moi_update}
  (\textit{\teng{I}}^{-1})^{n+1} = \ten{R}^{n+1} \textit{\teng{\overline{I}}}^{-1} (\ten{R}^{n+1})^T.
\end{equation}
where moment of inertia ($\textit{\teng{\overline{I}}}^{-1}$) in body frame is
used to compute in global frame at every time instant for faster computations.
The moment of inertia ($\textit{\teng{\overline{I}}}$) is computed as,
\begin{equation*}
\textit{\teng{\overline{I}}} =
\begin{bmatrix}
\sum_i m_i (y_i^2 + z_i^2) & -\sum_i m_i x_iy_i & -\sum_i m_i x_iz_i\\
-\sum_i m_i x_iy_i & \sum_i m_i (x_i^2 + z_i^2) &  -\sum_i m_i y_iz_i\\
-\sum_i m_i  x_iz_i & -\sum_i m_i y_iz_i & \sum_i m_i (x_i^2 + y_i^2)
\end{bmatrix}.
\end{equation*}

The position and velocity of the particles of the rigid body are updated by
\begin{eqnarray}
  \label{eq:rfc:rb_particle_pos_update}
  \ten{r}_i = \ten{R} \cdot \overline{\ten{r}}_{i},\\
  \ten{x}_i = \ten{x}_{cm} + \ten{r}_{i},\\
  \ten{v}_i = \ten{v}_{cm} + \teng{\omega} \times \ten{r}_{i}.
\end{eqnarray}

The force acting on particle $i$ is composed of interaction with the other rigid
bodies, and the fluid, given as
\begin{eqnarray}
  \label{eq:rfc:rb_particle_pos_update}
  \ten{F}_i = \ten{F}_{\text{Fl}}^i + \ten{F}_{\text{cont}}^i
\end{eqnarray}
We follow \cref{sec:contact-algorithm} to compute force
$\ten{F}_{\text{cont}}^a$ acting on particle $i$ due to the interaction with
the rigid bodies. The force $\ten{F}_{\text{Fl}}^i$ acting due to the
interaction with the fluid particles follows \cref{subsec:fsi}.

% We model the fluid with the CTVF \parencite{adepu2021corrected} scheme
developed in \cref{chap:ctvf}. Similar to the fluid modeling in
\cref{chap:fsi}, we modify the momentum equation to include the force acting due
to the interaction with a solid body. The discretized momentum equation of the
fluid particle including the interaction force is given as
\begin{multline}
  \label{eq:rfc:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
  \bigg) \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
  \ten{g}_{a} + \frac{\ten{F}^a_{\text{Fl}}}{m_a}.
\end{multline}
The particles are transported with a transport velocity as described in
\cref{chap:ctvf,chap:fsi}. The boundaries are handled using the dummy particle
approach as described in \cref{chap:ctvf}.

\subsection{Time Integration}

Rigid body and the fluid follow the kick-drift-kick time integration scheme. The
modeling of rigid-rigid interaction requires lower time step than the fluid. We
choose the minimum of both the timesteps to move the system forward in time. For
the numerical stability of fluid, the time step depends on the CFL condition as,
\begin{equation}
  \label{eq:rfc:time-step-cfl}
  \Delta t_{\text{fluid}} = \mathrm{min} \bigg( 0.25 \; \frac{h}{c + |U|} ,  0.25 \; \frac{h^2}{\nu},  0.25 \; \frac{h^2}{g} \bigg),
\end{equation}
where $|U|$ is the maximum velocity magnitude, $c$ is the speed of sound
typically chosen as $10 |U|$ for fluids in this work. For rigid body, the time
step is constrained as,
\begin{equation}
  \label{eq:rfc:time-step-body-force}
  \Delta t_{\text{rb}} \leq \frac{\pi}{50} \sqrt{\frac{m}{K_r}}.
\end{equation}
A minimum timestep is chosen as
\begin{equation}
  \label{eq:rfc:time-step-body-force}
  \Delta t = min(\Delta t_{\text{fluid}}, \Delta t_{\text{rb}}).
\end{equation}

\FloatBarrier%
\section{Discrete element method}
\label{sec:conclusions}

\FloatBarrier%
\section{Rigid fluid coupling}
\label{sec:conclusions}

\FloatBarrier%
\section{Results}
\label{sec:results}

\FloatBarrier%
\subsection{Stirrer in a fluid tank}
\label{sec:stirrer_fluid_result}

\FloatBarrier%
\subsection{Mixing of spherical particles in a tank}
\label{sec:stirrer_fluid_result}

\FloatBarrier%
\subsection{Mixing of spherical particles in a fluid tank}
\label{sec:mixing-spherical-particles-in-fluid-tank}

\FloatBarrier%
\section{Conclusions}
\label{sec:conclusions}

\section*{References}

\bibliographystyle{model6-num-names}
\bibliography{references}
\end{document}

% ============================
% Table template for reference
% ============================
% \begin{table}[!ht]
%   \centering
%   \begin{tabular}[!ht]{ll}
%     \toprule
%     Quantity & Values\\
%     \midrule
%     $L$, length of the domain & 1 m \\
%     Time of simulation & 2.5 s \\
%     $c_s$ & 10 m/s \\
%     $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
%     Reynolds number & 200 \& 1000 \\
%     Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
%     Smoothing length factor, $h/\Delta x$ & 1.0\\
%     \bottomrule
%   \end{tabular}
%   \caption{Parameters used for the Taylor-Green vortex problem.}%
%   \label{tab:tgv-params}
% \end{table}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% fill-column: 78
%%% End:

### 2024-02-20 automate.py

@@ -1,0 +1,422 @@
+#!/usr/bin/env python
+import os
+import matplotlib.pyplot as plt
+
+from itertools import cycle, product
+import json
+from automan.api import PySPHProblem as Problem
+from automan.api import Automator, Simulation, filter_by_name
+from automan.jobs import free_cores
+from pysph.solver.utils import load, get_files
+from automan.api import (Automator, Simulation, filter_cases, filter_by_name)
+
+import numpy as np
+import matplotlib
+matplotlib.use('agg')
+from cycler import cycler
+from matplotlib import rc, patches, colors
+from matplotlib.collections import PatchCollection
+
+rc('font', **{'family': 'Helvetica', 'size': 12})
+rc('legend', fontsize='medium')
+rc('axes', grid=True, linewidth=1.2)
+rc('axes.grid', which='both', axis='both')
+# rc('axes.formatter', limits=(1, 2), use_mathtext=True, min_exponent=1)
+rc('grid', linewidth=0.5, linestyle='--')
+rc('xtick', direction='in', top=True)
+rc('ytick', direction='in', right=True)
+rc('savefig', format='pdf', bbox='tight', pad_inches=0.05,
+   transparent=False, dpi=300)
+rc('lines', linewidth=1.5)
+rc('axes', prop_cycle=(
+    cycler('color', ['tab:blue', 'tab:green', 'tab:red',
+                     'tab:orange', 'm', 'tab:purple',
+                     'tab:pink', 'tab:gray']) +
+    cycler('linestyle', ['-.', '--', '-', ':',
+                         (0, (3, 1, 1, 1)), (0, (3, 1, 1, 1, 1, 1)),
+                         (0, (3, 2, 1, 1)), (0, (3, 2, 2, 1, 1, 1)),
+                         ])
+))
+
+
+n_core = 32
+# n_core = 6
+n_thread = n_core * 2
+backend = ' --openmp '
+
+
+def pretty(d, indent=0):
+    for key, value in d.items():
+        print('\t' * indent + str(key))
+        if isinstance(value, dict):
+            pretty(value, indent + 1)
+        else:
+            print('\t' * (indent + 1) + str(value))
+
+
+def scheme_opts(params):
+    if isinstance(params, tuple):
+        return params[0]
+    return params
+
+
+def get_files_at_given_times(files, times):
+    from pysph.solver.utils import load
+    result = []
+    count = 0
+    for f in files:
+        data = load(f)
+        t = data['solver_data']['t']
+        if count >= len(times):
[…]

### 2024-02-20 code/dam_break.py

@@ -1,0 +1,221 @@
+"""3D dam break
+
+Run it using:
+
+python 3d_dam_break.py --openmp --tf 1 --alpha 0.1 --tank-length-ratio 3.
+
+"""
+import numpy as np
+
+# imports related to the application class
+from pysph.solver.application import Application
+from pysph.sph.scheme import (SchemeChooser,
+                              add_bool_argument)
+
+# geometry imports
+from sph_dem.geometry import (
+    get_fluid_tank_3d, get_truncated_circle_from_3d_block,
+    hydrostatic_tank_2d,
+    translate_system_with_left_corner_as_origin,
+    create_tank_2d_from_block_2d)
+
+from sph_dem.fluids import (FluidsScheme,
+                            get_particle_array_fluid,
+                            get_particle_array_boundary)
+
+
+class Problem(Application):
+    def add_user_options(self, group):
+        group.add_argument("--fluid-length-ratio", action="store", type=float,
+                           dest="fluid_length_ratio", default=8,
+                           help="Ratio between the fluid length and rigid body diameter")
+
+        group.add_argument("--fluid-height-ratio", action="store", type=float,
+                           dest="fluid_height_ratio", default=6,
+                           help="Ratio between the fluid height and rigid body diameter")
+
+        group.add_argument("--fluid-depth-ratio", action="store", type=float,
+                           dest="fluid_depth_ratio", default=3,
+                           help="Ratio between the fluid depth and rigid body diameter (z-direction)")
+
+        group.add_argument("--tank-length-ratio", action="store", type=float,
+                           dest="tank_length_ratio", default=3,
+                           help="Ratio between the tank length and fluid length")
+
+        group.add_argument("--tank-height-ratio", action="store", type=float,
+                           dest="tank_height_ratio", default=1.4,
+                           help="Ratio between the tank height and fluid height")
+
+        group.add_argument("--tank-depth-ratio", action="store", type=float,
+                           dest="tank_depth_ratio", default=1,
+                           help="Ratio between the tank depth and fluid depth (z-direction)")
+
+        group.add_argument("--N", action="store", type=int, dest="N",
+                           default=7,
+                           help="Number of particles in diamter of a rigid cylinder")
+
+        group.add_argument("--dimension", action="store", type=int, dest="dim",
+                           default=2,
[…]

### 2024-02-20 code/hs_tank_with_stirrer.py

@@ -1,0 +1,274 @@
+"""3D dam break
+
+Run it using:
+
+python 3d_dam_break.py --openmp --tf 1 --alpha 0.1 --tank-length-ratio 3.
+
+"""
+import numpy as np
+
+# imports related to the application class
+from pysph.solver.application import Application
+from pysph.sph.scheme import (SchemeChooser,
+                              add_bool_argument)
+
+# geometry imports
+import pysph.tools.geometry as G
+from sph_dem.geometry import (
+    get_fluid_tank_3d, get_truncated_circle_from_3d_block,
+    hydrostatic_tank_2d,
+    translate_system_with_left_corner_as_origin,
+    create_tank_2d_from_block_2d,
+    get_2d_block)
+
+from sph_dem.fluids import (FluidsScheme,
+                            get_particle_array_fluid,
+                            get_particle_array_boundary)
+
+
+class Problem(Application):
+    def add_user_options(self, group):
+        group.add_argument("--fluid-length-ratio", action="store", type=float,
+                           dest="fluid_length_ratio", default=8,
+                           help="Ratio between the fluid length and rigid body diameter")
+
+        group.add_argument("--fluid-height-ratio", action="store", type=float,
+                           dest="fluid_height_ratio", default=6,
+                           help="Ratio between the fluid height and rigid body diameter")
+
+        group.add_argument("--fluid-depth-ratio", action="store", type=float,
+                           dest="fluid_depth_ratio", default=3,
+                           help="Ratio between the fluid depth and rigid body diameter (z-direction)")
+
+        group.add_argument("--tank-length-ratio", action="store", type=float,
+                           dest="tank_length_ratio", default=1,
+                           help="Ratio between the tank length and fluid length")
+
+        group.add_argument("--tank-height-ratio", action="store", type=float,
+                           dest="tank_height_ratio", default=1.4,
+                           help="Ratio between the tank height and fluid height")
+
+        group.add_argument("--tank-depth-ratio", action="store", type=float,
+                           dest="tank_depth_ratio", default=1,
+                           help="Ratio between the tank depth and fluid depth (z-direction)")
+
+        group.add_argument("--N", action="store", type=int, dest="N",
+                           default=7,
+                           help="Number of particles in diamter of a rigid cylinder")
+
[…]

### 2024-02-20 code/particle_dispersion_2d.py

@@ -1,0 +1,621 @@
+"""Rigid body falling in tank but 2D
+
+Run it using:
+
+python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme combined -d rb_falling_in_hs_tank_combined_output
+
+python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme master -d rb_falling_in_hs_tank_master_output
+
+
+TODO:
+
+1. Create many particles
+2. Run it on HPC
+3. Change the speed
+4. Change the dimensions
+5. Commit SPH-DEM and current repository
+6. Validate 1 spherical particle settled in hs tank
+7. Validate 2 spherical particles settled in hs tank
+8. Complete the manuscript
+9. Different particle diameter
+10. Different density
+"""
+import numpy as np
+import sys
+
+from pysph.examples import dam_break_2d as DB
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.tools.geometry import get_3d_sphere
+import pysph.tools.geometry as G
+from pysph.base.utils import get_particle_array
+
+from pysph.examples import cavity as LDC
+from pysph.sph.equation import Equation, Group
+from pysph.sph.scheme import add_bool_argument
+sys.path.insert(0, "./../")
+from pysph_rfc_new.fluids import (get_particle_array_fluid, get_particle_array_boundary)
+
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import SchemeChooser
+
+from pysph_dem.rigid_body.boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, translate_system_with_left_corner_as_origin
+# from geometry import hydrostatic_tank_2d, create_circle_1
+
[…]

### 2024-02-20 code/spherical_bodies_settling_in_tank_DEM_2D.py

@@ -1,0 +1,240 @@
+"""Change this
+
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
+                                              set_linear_velocity,
+                                              set_angular_velocity,
+                                              get_master_and_slave_rb,
+                                              add_contact_properties_body_master,
+                                              RigidBody3DScheme)
+from pysph_dem.dem_simple import (setup_wall_dem)
+
+
+class Case0(Application):
+    def add_user_options(self, group):
+        # group.add_argument(
+        #     "--re", action="store", type=float, dest="re", default=0.0125,
+        #     help="Reynolds number of flow."
+        # )
+
+        group.add_argument("--no-of-bodies", action="store", type=int, dest="no_of_bodies",
+                           default=10,
+                           help="Number of freely moving bodies")
+
+        # group.add_argument(
+        #     "--remesh", action="store", type=float, dest="remesh", default=0,
+        #     help="Remeshing frequency (setting it to zero disables it)."
+        # )
+
+    def consume_user_options(self):
+        # ======================
+        # Get the user options and save them
+        # ======================
+        self.no_of_bodies = self.options.no_of_bodies
+        # ======================
+        # ======================
+
+        self.rho0 = 2700.0
+        self.hdx = 1.0
+        self.dy = 0.1
+        self.kn = 1e4
+        self.mu = 0.5
+        self.en = 1.0
+        self.dim = 2
+        self.body_diameter = 1.
+        self.dx = self.body_diameter / 20
+        self.gy = -9.81
+        # self.gy = 0.
+
+        self.dt = 5e-4
+        self.tf = 3.
+
+    def create_particles(self):
+        from pysph_dem.geometry import create_circle_1
+        dx = self.dx
+        x1, y1 = create_circle_1(self.body_diameter, dx)
+        x1 = x1.ravel()
+        y1 = y1.ravel()
+        x = np.array([])
+        y = np.array([])
[…]

### 2024-02-20 code/spherical_bodies_settling_in_tank_DEM_3D.py

@@ -1,0 +1,291 @@
+"""
+
+Run it using:
+
+python 04_3d_multiple_rigid_bodies_settling_in_tank.py --openmp
+
+"""
+import numpy as np
+import sys
+
+import pysph.tools.geometry as G
+from pysph.base.utils import get_particle_array
+
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import SchemeChooser
+
+from sph_dem.geometry import (get_fluid_tank_3d, get_truncated_circle_from_3d_block)
+
+from sph_dem.rigid_body.rigid_body_3d import (RigidBody3DScheme,
+                                              setup_rigid_body,
+                                              set_linear_velocity,
+                                              set_angular_velocity,
+                                              get_master_and_slave_rb,
+                                              add_contact_properties_body_master)
+
+from pysph_dem.dem_simple import (setup_wall_dem)
+
+
+class Problem(Application):
+    def add_user_options(self, group):
+        group.add_argument("--N", action="store", type=int, dest="N",
+                           default=10,
+                           help="Number of particles in diamter of a rigid cylinder")
+
+        group.add_argument("--rigid-body-rho", action="store", type=float,
+                           dest="rigid_body_rho", default=1500,
+                           help="Density of rigid cylinder")
+
+        group.add_argument("--rigid-body-diameter", action="store", type=float,
+                           dest="rigid_body_diameter", default=1e-3,
+                           help="Diameter of each particle")
+
+        group.add_argument("--no-of-bodies", action="store", type=int,
+                           dest="no_of_bodies", default=50,
+                           help="Total no of rigid bodies")
+
+        group.add_argument("--z-rb-layers", action="store", type=int,
+                           dest="z_rb_layers", default=3,
+                           help="No of layers of rigid bodies in z-direction")
+
+    def consume_user_options(self):
+        # ======================
+        # Dimensions
+        # ======================
+        # tank geometry
+        self.tank_layers = 0.
+        # dimensions rigid body dimensions
+        # All the particles are in circular or spherical shape
+        self.rigid_body_diameter = 0.11
+        self.rigid_body_velocity = 0.
+        self.no_of_bodies = self.options.no_of_bodies
[…]

### 2024-02-20 code/spherical_bodies_stirring_DEM_2D.py

@@ -1,0 +1,317 @@
+"""Change this
+
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from sph_dem.geometry import (get_2d_block)
+
+from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
+                                              set_linear_velocity,
+                                              set_angular_velocity,
+                                              get_master_and_slave_rb,
+                                              add_contact_properties_body_master,
+                                              RigidBody3DScheme)
+
+from pysph_dem.dem_simple import (setup_wall_dem)
+
+
+class Case0(Application):
+    def add_user_options(self, group):
+        # group.add_argument(
+        #     "--re", action="store", type=float, dest="re", default=0.0125,
+        #     help="Reynolds number of flow."
+        # )
+
+        group.add_argument("--no-of-bodies", action="store", type=int, dest="no_of_bodies",
+                           default=10,
+                           help="Number of freely moving bodies")
+
+        # group.add_argument(
+        #     "--remesh", action="store", type=float, dest="remesh", default=0,
+        #     help="Remeshing frequency (setting it to zero disables it)."
+        # )
+
+    def consume_user_options(self):
+        # ======================
+        # Get the user options and save them
+        # ======================
+        self.no_of_bodies = self.options.no_of_bodies
+        # ======================
+        # ======================
+
+        self.rho0 = 2700.0
+        self.hdx = 1.0
+        self.dy = 0.1
+        self.kn = 1e4
+        self.mu = 0.5
+        self.en = 1.0
+        self.E = 69. * 1e5
+        self.dim = 2
+        self.body_diameter = 1.
+        self.dx = self.body_diameter / 20
+        self.gy = -9.81
+        # self.gy = 0.
+
+        # x - axis
+        self.stirrer_length = self.body_diameter
+        # y - axis
+        self.stirrer_height = 5. * self.body_diameter
+        # z - axis
+        self.stirrer_depth = 4. * self.body_diameter
[…]

### 2024-02-20 code/stirrer_spherical_particle_force_test.py

@@ -1,0 +1,237 @@
+"""Change this
+
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from sph_dem.geometry import (get_2d_block)
+
+from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
+                                              set_linear_velocity,
+                                              set_angular_velocity,
+                                              get_master_and_slave_rb,
+                                              add_contact_properties_body_master,
+                                              RigidBody3DScheme)
+
+from pysph_dem.dem_simple import (setup_wall_dem)
+
+
+class Case0(Application):
+    def add_user_options(self, group):
+        # group.add_argument(
+        #     "--re", action="store", type=float, dest="re", default=0.0125,
+        #     help="Reynolds number of flow."
+        # )
+
+        group.add_argument("--no-of-bodies", action="store", type=int, dest="no_of_bodies",
+                           default=10,
+                           help="Number of freely moving bodies")
+
+        # group.add_argument(
+        #     "--remesh", action="store", type=float, dest="remesh", default=0,
+        #     help="Remeshing frequency (setting it to zero disables it)."
+        # )
+
+    def consume_user_options(self):
+        # ======================
+        # Get the user options and save them
+        # ======================
+        self.no_of_bodies = self.options.no_of_bodies
+        # ======================
+        # ======================
+
+        self.rho0 = 2700.0
+        self.hdx = 1.0
+        self.dy = 0.1
+        self.kn = 1e4
+        self.mu = 0.5
+        self.en = 1.0
+        self.E = 69. * 1e9
+        self.dim = 2
+        self.body_diameter = 1.
+        self.dx = self.body_diameter / 20
+        self.gy = -9.81
+        # self.gy = 0.
+
+        # x - axis
+        self.stirrer_length = self.body_diameter
+        # y - axis
+        self.stirrer_height = 5. * self.body_diameter
+        # z - axis
+        self.stirrer_depth = 4. * self.body_diameter
+        self.stirrer_velocity = 5.
[…]

### 2024-03-01 manuscript/paper.tex
Add more examples and add content to paper

@@
 
-  \title{}
+  \title{Study of mixing behaviour of spherical particles in fluid using stirrer}
   \author[XXX]{Dinesh Adepu\corref{cor1}}
@@
 \begin{abstract}
+  Particle dispersion is a fundamental physical phenomenon encountered in
+  various industries where powder and fluid interactions are
+  pivotal. Particularly, processes involving the mixing of powder with fluid
+  using a stirrer are commonplace. While experimental investigation of such
+  processes is often impractical due to their highly nonlinear nature,
+  numerical methods offer a viable alternative. Among these, Smoothed Particle
+  Hydrodynamics coupled with Discrete Element Method (SPH-DEM) stands out for
+  its ability to handle free surface fluid dynamics and model the complex
+  physics inherent in dispersion processes.
+
+  In this study, we initially develop and validate both the DEM and SPH
+  solvers. Validation includes testing against fundamental benchmarks such as
+  two-particle head-on collisions and particle-wall impacts for the DEM
+  solver, and Poiseuille flow for the fluid solver. Additionally, we validate
+  the rigid-fluid model through simulations of a single cylindrical body
+  entering a steady tank and the settling of two tandem cylinders in a
+  fluid-filled tank.
+
+  With confidence in the fidelity of our solver established, we delve into
+  investigating the mixing behavior of spherical particles dispersed in
+  water. Our study encompasses various scenarios, including particles with
+  densities higher or lower than the surrounding fluid, as well as particles
+  with varying radii. We also examine combinations of these factors.
+  \todoin{What factor have you considered to quantify the mixing
+    behaviour.}
+
+  \todoin{Write the findings}
 \end{abstract}
@@
 
-\section{Governing equations}
+\FloatBarrier%
+\section{Introduction}
 
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/hs_tank_fluid_with_particles}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:gloabl_body_frame_rb}
+\end{figure}
+
+\begin{itemize}
+\item Fluid modeling using smoothed particle hydrodynamics
+  (\cref{sec:fluid--modeling})
+\item Interaction among the discrete spherical rigid particle units by
+  discrete element method (\cref{sec:rbd})
+\end{itemize}
+
+While the interaction among the rigid spherical particle and fluid particles
+are modeled by sampling the spherical particles into dummy SPH particles. This
+is explained in \cref{sec:rfc}.
+
+% \FloatBarrier%
+% \section{Fluid modeling}
+
+% \FloatBarrier%
+% \subsection{Boundary conditions}
+
+% \FloatBarrier%
+% \section{Solid phase modeling}
+
+% \FloatBarrier%
+% \subsection{Discrete element method}
+
+% \FloatBarrier%
+% \subsection{Rigid body equations}
+
+% \FloatBarrier%
+% \section{Rigid fluid coupling}
+
+% \FloatBarrier%
+% \section{Results}
+
+\FloatBarrier%
+\subsection{Fluid modeling}
+\label{sec:fluid--modeling}
+
+In the current work, we follow a weakly-compressible SPH approach to model the
+fluid. The SPH discretization of the continuity
+equation~\cref{eq:sph-discretization-continuity} and the momentum equation
+~\cref{eq:sph-momentum-fluid} respectively are,
 \begin{equation}
-  \label{eq:ce}
-  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
-\end{equation}
-and conservation of linear momentum,
-\begin{equation}
-  \label{eq:me}
-  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
-  + g_i,
-\end{equation}
-where $\rho$ is the density, $u_i$ is the $i$\textsuperscript{th} component of
-the velocity field, $x_j$ is the $j$\textsuperscript{th} component of the
-position vector, $g_i$ is the component of body force per unit mass and
-$\sigma_{ij}$ is stress tensor.
-
-The stress tensor is split into isotropic and deviatoric parts,
-\begin{equation}
-  \label{eq:stress_tensor_decomposition}
-  \sigma_{ij} = - p \; \delta_{ij} + \sigma'_{ij},
-\end{equation}
-%
-where $p$ is the pressure, $\delta_{ij}$ is the Kronecker delta function, and
-$\sigma'_{ij}$ is the deviatoric stress.
-
-The Jaumann's formulation for Hooke's stress provides us with the rate of
-change of deviatoric stress,
-\begin{equation}
-  \label{eq:jaumann-stress-rate}
-  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
-  \dot{\epsilon}_{kk} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
-  \Omega_{ik} \sigma^{'}_{kj},
-\end{equation}
-where $G$ is the shear modulus, $\dot{\epsilon}_{ij}$ is the strain rate tensor,
-\begin{equation}
-  \label{eq:strain-tensor}
-  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
-  \frac{\partial u_j}{\partial x_i} \bigg),
-\end{equation}
-and $\Omega_{ij}$ is the rotation tensor,
-\begin{equation}
-  \label{eq:rotational-tensor}
-  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
-  \frac{\partial u_j}{\partial x_i} \bigg).
+  \label{eq:sph-discretization-continuity}
+  \frac{{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \;
+  \rho_{a} \; {\ten{u}}_{ab} \; \cdot \nabla_{a} W_{ab},
 \end{equation}
 
-For a weakly-compressible or incompressible fluid, a viscous force is added:
-\begin{equation}
-  \label{eq:fluid-stress-decomposition}
-  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
-\end{equation}
-where $\eta$ is the kinematic viscosity of the fluid.
-
-In both fluid and solid modelling the pressure is computed using an
-isothermal equation of state, given as,
-\begin{equation}
-  \label{eq:pressure-equation}
-  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
-\end{equation}
-where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
-$\rho_0$ are the reference speed of sound and density, respectively. For solids,
-$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
-Poisson ratio, $E$ is the Young's modulus.
-
-\section{Smoothed Particle Hydrodynamics}
-In the current section, we introduce the basics of smoothed particle
-hydrodynamics. A fundamental overview of the discrete approximations of
-function, derivative, and divergence is discussed.
-
-\subsection{Function Approximation}
-From the dirac delta function definition, the function value of a smooth
-function $A$ defined over a domain $\Omega$ at point $x$ can be written as
-\begin{equation}
-  \label{eq:dirac_repr}
-  A(\ten{x}) = \int_{\Omega}\> A(\ten{x}') \> \delta(\ten{x} - \ten{x}') \> d\ten{x}',
-\end{equation}
-where $\delta(\ten{x} - \ten{x}')$ is a Dirac-delta function with
-\begin{equation}
-  \label{eq:unity}
-  \int_{\Omega}\> \delta(\ten{x}) \> d\ten{x} = 1.
-\end{equation}
-In SPH, the Dirac delta function is replaced with a compact, smooth function $W$,
-chosen to be as an even function. The function value of $A$ at $\ten{x}$
-interpolated with the smooth kernel $W$ is given by
-\begin{equation}
-  \label{eq:kernel_repr}
-  A(\ten{x}) = \int_{\Omega}\> A(\ten{x}') \> W(\ten{x} - \ten{x}', h)  \> d\ten{x}' + O(h^2).
-\end{equation}
-Here, kernel $W$ satisfies the following conditions,
-\begin{equation}
-  \label{eq:unity}
-  \int_{\Omega}\> W(\ten{x} - \ten{x}', h)  \> d\ten{x}' = 1.
-\end{equation}
-
-\begin{equation}
-  \label{eq:kernel_delta}
-  \lim_{h \to 0} W(\boldsymbol{x} - \boldsymbol{x}', h) = \delta(\boldsymbol{x} - \boldsymbol{x}', h).
-\end{equation}
-\begin{equation}
-  \label{eq:compact_support}
-  W(\boldsymbol{x} - \boldsymbol{x}', h) = 0 \>\>\>\>    \text{when}  \>\>\> |\boldsymbol{x} - \boldsymbol{x}'| > kh.
-\end{equation}
-Here k is a constant, which determines the the non-zero region $W$ for a point
-at position vector $\boldsymbol{x}$. In the current work we have used Quintic
-% spline in all our simulation cases. Quintic spline \parencite{Violeau16}, is
-given as,
-\begin{equation}
-  \label{eq:quintic_spline}
-  W(r, h) =
-  \begin{cases}
-    \sigma_5\left( (3-q)^5 - 6(2-q)^5 + 15(1-q)^5 \right), & \textrm{for} \ 0\leq q \leq 1,\\
-    \sigma_5\left( (3-q)^5 - 6(2-q)^5 \right), & \textrm{for} \ 1 <  q \leq 2,\\
-    \sigma_5 \ (3-q)^5 , & \textrm{for} \ 2 < q \leq 3,\\
-    0, & \textrm{for} \ q>3,
-  \end{cases}
-\end{equation}
-This type of interpolation leads to a 2nd order function accuracy
-% \parencite{fatehi2011error}.
-
-Assume that the domain is discretized into N particles with mass
-$m_i$ and volume $\Delta v_i$, We have
-\begin{equation}
-  \label{eq:mass_repr}
-  m_j = \Delta v_i \> \rho_i.
-\end{equation}
-Using \eqref{eq:mass_repr}, \eqref{eq:kernel_repr} is converted to
-discrete form as follows
-\begin{equation}
-  \label{eq:discrete_form}
-  A_i = \sum_{j \in \text{Neigh}(i)}\> \frac{m_j}{\rho_j} A_j\> W(\ten{x}_i - \ten{x}_j, h),
-\end{equation}
-where $A(\boldsymbol{x}_i) = A_i$ is the value of the field property of particle
-i, similarly for $A_j$. Here, $\text{Neigh}(i)$ is the neighbours of particle $i$.
-
-\subsection{Derivative Approximation}
-% The discretized form of the derivative approximation~\parencite{Violeau16} is given
-as,
-\begin{equation}
-  \label{intro:eq:derivative-discrete_form}
-  \nabla A(\ten{x}_i) = \sum_j\> \frac{m_j}{\rho_j} A_j\> \nabla W(\ten{x}_i - \ten{x}_j, h).
-\end{equation}
-
-An alternative expression of the derivative approximation is derived by employing
-density, i.e,
-\begin{equation}
-  \label{intro:eq:sph-continu-derivative-final}
-  \nabla (A \rho^n) = n A \rho^{n - 1} \nabla \rho + \rho^n \nabla A,
-\end{equation}
-where $n$ is a real number. The new identity for the derivative of $A$ is
-\begin{equation}
-  \nabla A = \frac{1}{\rho^n} \left[ n A \rho^{n - 1} \nabla \rho + \rho^n \nabla A  \right],
-\end{equation}
-using \cref{eq:discrete_form,intro:eq:derivative-discrete_form}, the new
-derivative approximation can be written as
-\begin{equation}
-  \label{intro:eq:derivative-discrete_form}
-  \nabla A(\ten{x}_i) = \frac{1}{\rho^n(\ten{x}_i)} \sum\>
-  m_j \left(A_j \rho^{n-1}(\ten{x}_j) - n A_i \rho^{n-1}(\ten{x}_i) \right)\> \nabla W(\ten{x}_i - \ten{x}_j, h).
-\end{equation}
-In the current work, we use a symmetric expression, with $n=-1$, resulting in
-\begin{equation}
-  \nabla A(\ten{x}_i) = \rho_i \sum_{j} m_j \left(\frac{A_i}{\rho_i^2} + \frac{A_j}{\rho_j^2}\right) \nabla W_{ij}.
-\end{equation}
-A symmetric gradient operator ensures equal and opposite forces acting on the
-particles.
-
-\subsection{Divergence Approximation}
-We now look at an SPH approximation of the divergence operator. An approximation
-of the divergence operator is used to discretize the \cref{eq:ce}. It is given
-as,
-\begin{equation}
-  \label{intro:eq:discrete_derivative}
-  \nabla \cdot \ten{v}_i = \sum\> \frac{m_j}{\rho_j} \ten{v}_j \cdot \nabla W(\ten{x}_i - \ten{x}_j, h).
-\end{equation}
-Similar to the derivative approximation, we utilize the following identity to approximate the divergence operator,
-\begin{equation}
-  \label{intro:eq:sph-continu-div-intermediate}
-  \nabla \cdot (\ten{v} \rho^n) = \rho^n \nabla \cdot \ten{v} + n  \rho^{n - 1} \ten{v} \cdot \nabla \rho.
-\end{equation}
-In the current work, we employ expression for $n=1$. The discrete SPH approximation for $n=1$ is given as
-\begin{equation}
-  \label{intro:eq:sph-continu-div-final}
-  \nabla \cdot \ten{v}(\ten{x}_i) = \frac{1}{\rho_i} \sum_{j} m_j \left(\ten{v}_j - \ten{v}_i\right) \cdot \nabla W_{ij}.
-\end{equation}
-
-\subsection{SPH Discretization}\label{sec:ctvf-sph-equations}
-
-In the current work, both fluid and solid modelling uses the same continuity
-and pressure evolution equation. The SPH discretization of the continuity
-equation~\eqref{eq:ce-tvf} and the pressure evolution
-equation~\eqref{eq:edac-p-evolve} respectively are,
-\begin{equation}
-  \label{eq:sph-discretization-continuity}
-  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
-  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
-  (\rho \; (\tilde{\ten{u}} \; - \;
-  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
-\end{equation}
-
-\begin{multline}
-  \label{eq:sph-discretization-edac}
-  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
-  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; + \;
-  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
-  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
-  4 \; \nu_{edac}
-  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + 0.01 h_{ab}^{2})} \ten{r}_{ab}
-  \bigg) \; \cdot \nabla_{a} W_{ab}.
-\end{multline}
 %
@@
   \label{eq:sph-momentum-fluid}
-  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
-  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
-  \bigg) \bigg]
-  \cdot \nabla_{a} W_{ab} \\
-  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
-  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
-    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
-  \ten{g}_{a},
+  \frac{{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg)
+  \nabla_{a} W_{ab}
+ \;+\;
+  \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}  \;+\;
+  \ten{g}_{a} + \text{force due to rb},
 \end{multline}
-where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
-$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
+where $\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
 % fluid and \textcite{morris1997modeling} formulation is used to discretize the
@@
 %
-where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
-\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
-$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
-viscosity parameter.
-
-%
-For solid mechanics the momentum equation is written as,
+where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$,
+$\ten{u}_{ab} = \ten{u}_a - \ten{u}_b$, $h_{ab} = (h_a + h_b)/2$,
+$\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$, $\bar{c}_{ab} = (c_a + c_b) / 2$, and
+$\alpha$ is the artificial viscosity parameter.  The pressure $p_a$ is evaluated
+using an equation of state:
 \begin{equation}
-  \label{eq:sph-momentum-solid}
-  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
-  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
-  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
-  \ten{g}_{a},
+\label{eqn:sph-eos}
+  p_a = K \bigg(\frac{\rho_a}{\rho_{0}} - 1 \bigg).
 \end{equation}
-we have not considered the correction stress term $\ten{A}$ in momentum
-equation of solid mechanics as it has a negligible effect.
-
-In addition to these three equations, the Jaumann stress rate equation is also
-solved. In the current work we use the momentum velocity $\ten{u}$ rather than
-% $\tilde{\ten{u}}$ as in the GTVF~\parencite{zhang_hu_adams17} in the computation of
-gradient of velocity. The SPH discretization of the gradient of velocity is
-given as,
-\begin{equation}
-  \label{eq:sph-vel-grad}
-  \nabla \ten{u}_a =
-  - \sum_{b} \frac{m_b}{\rho_{b}} (\ten{u}_{a} - \ten{u}_{b}) \otimes (\nabla_{a} W_{ab}),
-\end{equation}
-where $\otimes$ is the outer product.
-
-The SPH discretization of the modified Jaumann stress rate
-\cref{eq:modified-jaumann-stress-rate} is given as,
-\begin{multline}
-  \label{eq:sph-modified-jaumann-stress}
-  \frac{\tilde{d}\teng{\sigma}^{'}_{a}}{dt} = 2G (\dot{\teng{\epsilon}}_{a} -
-  \frac{1}{3} \dot{\teng{\epsilon}}_{a} \ten{I}) + \teng{\sigma}^{'}_{a}
-  \teng{\Omega}_{a}^{T} +
-  \teng{\Omega}_{a} \teng{\sigma}^{'}_{a} + \\
-  + \sum_{b} \; \frac{m_b}{\rho_{b}} \; (\teng{\sigma}^{'} \otimes (\tilde{\ten{u}} -
-  \ten{u}))_{ab} \; \cdot \nabla_{a} W_{ab}
-  + \teng{\sigma}^{'}_{a} \sum_{b} \; \frac{m_b}{\rho_{b}} \;
-  (\tilde{\ten{u}} - \ten{u})_{ab} \; \cdot \nabla_{a} W_{ab}.
-\end{multline}
+Where, $K=\rho_0 \, c_0^2$ is bulk modulus of the body, with
+$c_0=10 \times V_{\text{max}}$ is speed of sound, while $\rho_0$ as the
+initial density of the particles.
 
 \FloatBarrier%
-\section{Rigid body modeling}
-\label{sec:conclusions}
+\subsection{Boundary conditions}
+\label{sec:boundary_conditions}
 
 \FloatBarrier%
-\section{Numerical Methodology}
-\label{sec:rfc:rbd}
+\section{Rigid body dynamics}
+\label{sec:rbd}
 % The rigid body is discretized into particles with equal spacing each particle
@@
 
-% \begin{figure}[!htpb]
-%   \centering
-%   \includegraphics[width=0.7\textwidth]{images/rfc/images/rigid_body/rigid_body}
-%   \caption{Body frame and local frame description of rigid body}
-%   \label{fig:gloabl_body_frame_rb}
-% \end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{images/rigid_body/rigid_body}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:gloabl_body_frame_rb}
+\end{figure}
 We use two coordinate frames to capture the dynamics of the rigid body, a
@@
 
-% We model the fluid with the CTVF \parencite{adepu2021corrected} scheme
-developed in \cref{chap:ctvf}. Similar to the fluid modeling in
-\cref{chap:fsi}, we modify the momentum equation to include the force acting due
-to the interaction with a solid body. The discretized momentum equation of the
-fluid particle including the interaction force is given as
-\begin{multline}
-  \label{eq:rfc:sph-momentum-fluid}
-  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
-  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
-  \bigg) \bigg]
-  \cdot \nabla_{a} W_{ab} \\
-  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
-  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
-    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
-  \ten{g}_{a} + \frac{\ten{F}^a_{\text{Fl}}}{m_a}.
-\end{multline}
-The particles are transported with a transport velocity as described in
-\cref{chap:ctvf,chap:fsi}. The boundaries are handled using the dummy particle
-approach as described in \cref{chap:ctvf}.
+\FloatBarrier%
+\subsection{Contact resolution}
+\label{sec:dem}
 
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{images/spherical_particles_dem_representation}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:gloabl_body_frame_rb}
+\end{figure}
+
+We resolve the contact among the spherical particles using discrete element
+method. In the current work we have utilized the contact force model proposed
+by \citet{mohseni2021particle}. The force acting on a particle $a$ due to the
+interaction with the particle $b$ can be resolved into a normal and tangential
+component. The normal force component is utilised to make sure that the
+particle do not penetrate into each other, while the tangential component is
+used to model the friction between the interacting solids.  The normal force
+($\teng{F}_a^{n}$) on particle $a$ due to the interaction with the particles
+$b$ is given as,
+\begin{equation}
+  \label{eq:contact-algorithm-normal}
+  \ten{F}_a^n = k_r \delta_{n^{c}}^{a} \ten{n}_a^{c}.
+\end{equation}
+Here, the overlap $\delta_{n^{c}}^{a}$ is computed using
+\begin{equation}
+  \label{eq:cf-overlap}
+  \delta_{n^{c}}^{a} = \Delta x - d_a,
+\end{equation}
+where the normal contact vector $\ten{n}_a^{c}$ is computed using
+\begin{equation}
+  \label{eq:cf-normal-vector}
+  \ten{\hat{n}}_a^{c} = \frac{
+    \displaystyle\sum\limits_{b = 1}^{\text{NP}^{b}} \;
+    \frac{\ten{r}_{ab}}{r_{ab}}  \frac{m_b}{\rho_b} W_{ab}}
+  {
+    \displaystyle\sum\limits_{b = 1}^{\text{NP}^{b}} \;
+    \frac{m_b}{\rho_b} W_{ab}},
+\end{equation}
+\begin{equation}
+  \label{eq:cf-normal-vector}
+  \ten{n}_a^{c} = \frac{\teng{\hat{n}}_a^{c}}{||\teng{\hat{n}}_a^{c}||}.
+\end{equation}
+With $\Delta x$ being the initial spacing between the particles, $k_r$ is the normal
+spring stiffness coefficient. Note that while computing the overlap of
+particle $a$ with the body $B$ we have computed an effective overlap, rather
+than per particle interaction. This effectively is able to model the
+interaction between non smooth surfaces in contrast with particle-particle
+force computation.
+
+\subsection{Tangential force computation}
+\label{sec:tangential-force-computation}
+We associate a tangential spring attached to particle $i$ and body $B$ to
+compute the tangential force, which initially has a magnitude of zero
+($|\Delta \textit{\textbf{l}}_a|=0$). And the tangential spring is activated
+when the particle comes into contact with body $B$. The tangential force is
+history-dependent. The contact friction force is proportional to the
+tangential spring displacement, which is integrated over the contact time as
+\begin{equation}
+  \label{eq:tangential-force}
+  \ten{F}_{a}^{t^{n+1}} =
+  -k_f \Delta \textit{\textbf{l}}_a^{\,n + 1} =
+  -k_f \big[\big(\Delta {\textit{\textbf{l}}}_a^{\,n} \
+  + \ten{v}_{ab}^{n + 1} \Delta t\big) \cdot \ten{t}_a^{n + 1} \big] \
+  \ten{t}_a^{n + 1},
+\end{equation}
+where $\Delta t$ is the time step, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is
+the relative velocity of the primary particle $a$ with respect to the
+closest secondary particle $b$, and $k_f$ is the tangential spring stiffness
+coefficient. The tangential unit vector is computed by,
+\begin{equation}
+  \label{eq:tangential-vect}
+  \ten{t}_a = \frac{\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}_a^{c}) \ten{n}_a^{c}}{|\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}_a^{c}) \ten{n}_a^{c}|}.
+\end{equation}
+
+The tangential force is coupled to the normal force through the Coulomb's law,
+\begin{equation}
+  \label{eq:Coulomb-law}
+  \ten{F}_{a}^{t} = \min(\mu |\ten{F}_{a}^{n}|, |\ten{F}_{a}^{t}|) \
+  \frac{\ten{F}_{a}^{t}}{|\ten{F}_{a}^{t}|}.
+\end{equation}
+This allows us to impose the sliding friction condition between the
+interacting solids. Finally, the total force acting on the particle $a$ due to
+the interaction with body $B$ is:
+\begin{equation}
+  \label{eq:contact-force}
+  \ten{F}_{a}^{\text{cont}} = \ten{F}_{a}^{n} + \ten{F}_{a}^{t}
+\end{equation}
+
+% \begin{figure}[!htpb]
+%   \centering
+%   \includegraphics[width=0.3\textwidth]{images/contact_force/contact_force_description_3}
+%   \caption{Force transfer to the secondary particles $b$ from the primary body particle $a$}
+% \label{fig:secondary_particle_contact_foce_transfer}
+% \end{figure}
+An equal and opposite force of the same magnitude is applied to the closest
+secondary particle $b$ of $a$ as shown in
+\cref{fig:secondary_particle_contact_foce_transfer},
+\begin{equation}
+  \label{eq:contact-force}
+  \ten{F}_{b}^{\text{cont}} = - \ten{F}_{a}^{\text{cont}}.
+\end{equation}
+
+% =========================================== %
+% ------ Results start ---------------------- %
+% =========================================== %
+
+\FloatBarrier%
+\subsection{Rigid fluid coupling}
+\label{sec:rfc}
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.22\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/real_spherical_particles}
+    \subcaption{}%\label{fig:rings:ipst-nu-0.47-0}
+  \end{subfigure}\hspace{15mm}%
+  \begin{subfigure}{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/sph_sampled_spherical_particles}
+    \subcaption{}%\label{fig:rings:ipst-nu-0.47-1}
+  \end{subfigure}
+  \caption{}
+\label{fig:real_particle_sph_sampling}
+\end{figure}
+In order to compute the force acting on the spherical particle due to the
+interacting fluid we sample the spherical particle with dummy SPH particles,
+as shown in \cref{fig:real_particle_sph_sampling}. Here the spherical particle
+is sampled using dummy SPH particles, while SPH particles are being placed
+equispaced. With spherical particles being discretized into SPH particles and
+immersed in fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{images/rfc_zoomed_combined}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:many_rb_in_fluid_sph_particles}
+\end{figure}
+
+Force on each sampled SPH particles consisting of the rigid body due to the
+interaction with the fluid particle is given as. The mass of each dummy
+particle being sampled in the spherical particle is considered as
+hydrodynamics mass. The force on the fluid particle due to the interaction
+with the sampled dummy SPH particles is considered in the momentum and the
+continuity equation. The force acting on the sampled dummy SPH particle due to
+the interaction with the fluid is given by,
+\begin{equation}
+  \label{eq:sph-discretization-continuity}
+  \frac{{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \;
+  \rho_{a} \; {\ten{u}}_{ab} \; \cdot \nabla_{a} W_{ab},
+\end{equation}
+The force here is composed of two components, one is due to the pressure and
+due to viscosity.
+
+\FloatBarrier%
 \subsection{Time Integration}
@@
 \FloatBarrier%
-\section{Discrete element method}
-\label{sec:conclusions}
-
-\FloatBarrier%
-\section{Rigid fluid coupling}
-\label{sec:conclusions}
-
-\FloatBarrier%
 \section{Results}
@@
 \FloatBarrier%
-\subsection{Stirrer in a fluid tank}
-\label{sec:stirrer_fluid_result}
+\subsection{Poiseuille's flow}
+\label{sec:poiseuille_flow}
+% https://onlinelibrary.wiley.com/doi/epdf/10.1002/nag.898
+
+\begin{itemize}
+\item Unsteady flow between two infinite, parallel paltes at rest in presence
+  of pressure gradient.
+\item Write about the location of the plates.
+\item Which way the flow is going (positive x or negative x)
+\item In this exact conditions, the Navier-Stokes equations admit the time
+  dependent solution (Write solution (equation 19))
+\item Periodic boundary conditions
+\item The accuracy of the results presented here validate the developed
+  no-slip boundary method inthe presence of straight boundaries.  The
+  remainder of this section addresses the more complexcase of non-straight
+  boundaries.
+\item Write about the schematic
+\item Write the resulting velocity profile
+\item Numerical parameters are important
+\item A body force of 1e-5
+\item Viscosity 0.01
+\item Time of 50 seconds
+\item spacing of 1 / 60
+\item Length in y is 2 * self.d=0.5
+\item Length in x 0.4 * self.Ly
+\item self.re = self.options.re
+\item self.Vmax = self.nu*self.re/(2*self.d)
+\item self.c0 = 10*self.Vmax
+\item self.p0 = self.c0**2*self.rho0
+\item self.fx = self.Vmax * 2*self.nu/(self.d**2)
+\end{itemize}
+
+The analytical solution from Morris is given as
+
+\begin{equation}
+  \label{eq:sph-discretization-continuity}
+  v_x(y, t) = \frac{F}{2 \nu}y(y - L) + \sum_{n=0}^{\infty}\frac{4FL^2}{\nu \pi^3 (2n + 1)^3} \sin\bigg(\frac{\pi y}{L} (2 n + 1) \bigg) \exp\bigg(\frac{ (2 n + 1)^2 \pi^2 \nu}{L^2} t\bigg)
+\end{equation}
+
+$\nu$ is kinematic viscosity ($\frac{\mu}{\rho_0}$)
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/fluid_01_benchmark_poisuelle/poiseuille_schematic}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:gloabl_body_frame_rb}
+\end{figure}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.png}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:gloabl_body_frame_rb}
+\end{figure}
 
 \FloatBarrier%
-\subsection{Mixing of spherical particles in a tank}
-\label{sec:stirrer_fluid_result}
+\subsection{DEM validation 1: Normal impact of spherical particle}
+\label{sec:DEM_validation_1_normal_impact}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/results_dem_1_validation_particle_particle_impact/dem_01_head_on_schematic}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:result:dem_1_schematic}
+\end{figure}
+For the initial validation of the Discrete Element Method (DEM), we examine
+the head-on collision of two spherical particles. In
+\cref{fig:result:dem_1_schematic}, the initial setup depicts both particles
+moving towards each other with an initial velocity of $10$
+m\,s\textsuperscript{-1}.  Each disk has a radius of $0.01$ m and is composed
+of glass. The glass material has a Young's modulus of $4.8 \times 10^{10}$
+N\,m\textsuperscript{-2}, a Poisson ratio of $0.2$, and a density of $2800$
+kg\,m\textsuperscript{-3}.  For the current scenario, we assume there is no
+friction or gravity acting on the particles.
+\Cref{fig:result:dem_1_force_vs_overlap} depicts the variation of the normal
+force and the amount of overlap, compared to the analytical findings presented
+in \citet{xxxx}. The force curve generated by our current implementation
+closely matches the analytical result, confirming the validation of our DEM
+solver's normal contact force model.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:result:dem_1_force_vs_overlap}
+\end{figure}
+
+\FloatBarrier%
+\subsection{DEM validation 2: Particle wall impact}
+\label{sec:DEM_validation_2_particle_wall_impact}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/results_dem_2_validation_particle_wall_impact/schematic}
+  \caption{}
+  \label{fig:result:dem_sw_contact_schematic}
+\end{figure}
+As part of our validation test cases, we consider the collision of a spherical
+particle with wall with different incident angles and a constant velocity in
+magnitude. This test case is helpful in testing the tangential part of our DEM
+implementation. The schematic of the body and wall is shown in
+\cref{fig:result:dem_sw_contact_schematic}. The radius of the impacting particle is
+$0.0025$ m and is made of aluminium oxide. The particle has a Young's modulus
+of $3.8 \times 10^{11}$ N\,m\textsuperscript{-2}, a Poisson ratio of $0.23$, and a
+density of $4000$ kg\,m\textsuperscript{-3}. The impact velocity has a
+magnitude of $3.9$ m\,s\textsuperscript{-1}. The friction coefficient among
+the wall and the particle is $0.092$.
+
+In \cref{fig:result:dem_sw_contact_omega_vs_theta}, we plot the variation of
+the rebound angular velocity with the incident impact angle, compared against
+the experimental result given in \citet{xxxx}. The variation of the angular
+velocity produced by our current implementation matches with the experimental
+result, confirming the validation of our DEM solver's tangential part of the
+contact force model.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/benchmark_4_sw_colliding_oblique/angle_vs_ang_vel.pdf}
+  \caption{Body frame and local frame description of rigid body}
+  \label{fig:result:dem_sw_contact_omega_vs_theta}
+\end{figure}
+
+\FloatBarrier%
+\subsection{RFC validation 1: Single particle entering into a tank}
+\label{sec:rfc_validation_1_single_particle_entry}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/rfc_01_skillen_2013_particle_entry_in_hs_tank/Skillen_2013_particle_entry_in_hs_tank}
+  \caption{Half Buoyant}
+  \label{fig:results_rfc_01_skillen_2013}
+\end{figure}
+To validate the rigid fluid coupling solver, we study the motion of a circular
+cylinder dropping into a steady tank. This problem has been studied
+experimentally by Greenhow and Lin
+\citet{xxxx}. \Cref{fig:results_rfc_01_skillen_2013} shows the initial
+configuration of the cylinder placed at $0.5$ m from the free surface. The
+radius of the disc is taken as $0.11$ m, while we consider two cases with the
+density of $500$ and $1000$ kg\,m\textsuperscript{-1}. The cylinder falls
+under the gravity into the tank.
+
+\todoin{Initial spacing, viscosity, gravity, h value, speed of sound, number of
+  particles, resolution write in a table}
+
+\cref{fig:result_rfc_01_result_displacement}, depicts the evolution of the
+depth of penetration of the cylinder, compared against the experimental result
+by \citet{xxxx}, numerical techniques of boundary element method
+(BEM)(\cite{xxx}) and delta-plus SPH (\cite{xxx}). From
+\cref{fig:result_rfc_01_result_displacement}, we find that the current solver
+matches well with the experimental result and also converges while increasing
+the resolution.
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/skillen_2013_water_entry_half_buoyant/penetration_vs_t}
+    \subcaption{}%\label{fig:rings:ipst-nu-0.47-0}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/skillen_2013_water_entry_neutrally_buoyant/penetration_vs_t}
+    \subcaption{}%\label{fig:rings:ipst-nu-0.47-1}
+  \end{subfigure}
+  \caption{}
+\label{fig:result_rfc_01_result_displacement}
+\end{figure}
+
+\FloatBarrier%
+\subsection{RFC validation 2: Two tandem particles entering into a tank}
+\label{sec:rfc_validation_2_single_particle_entry}
 
@@
 \FloatBarrier%
+\subsection{Mixing of spherical particles of variable size in a fluid tank}
+\label{sec:mixing-spherical-particles-in-fluid-tank}
+
+\FloatBarrier%
 \section{Conclusions}
@@
 
-\section*{References}
+% \section*{References}
 

### 2024-03-01 automate.py

@@ -39,8 +39,8 @@ rc('axes', prop_cycle=(
 ))
 
 
-n_core = 32
-# n_core = 6
+# n_core = 32
+n_core = 6
 n_thread = n_core * 2
 backend = ' --openmp '
 
@@ -97,6 +97,56 @@ def get_files_at_given_times_from_log(files, times, logfile):
                     time_count += 1
                 file_count += 1
     return result
+
+
+class ManuscriptRFCImageGenerator(Problem):
+    """
+    Pertains to Figure 14 (a)
+    """
+    def get_name(self):
+        return 'manuscript_rfc_image_generator'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/manuscript_rfc_image_generator.py' + backend
+
+
+        # Base case info
+        self.case_info = {
+            'case_1': (dict(
+            ), 'Case 1'),
+        }
+
+        self.cases = [
+            Simulation(get_path(name), cmd,
+                       job_info=dict(n_core=n_core,
+                                     n_thread=n_thread), cache_nnps=None,
+                       **scheme_opts(self.case_info[name][0]))
+            for name in self.case_info
+        ]
+
+    def run(self):
+        self.make_output_dir()
+        self.move_figures()
+
+    def move_figures(self):
+        import shutil
+        import os
+
+        source = "code/manuscript_rfc_image_generator_output/"
+
+        target_dir = "manuscript/figures/manuscript_rfc_image_generator_output/"
+        os.makedirs(target_dir, exist_ok=True)
+        # print(target_dir)
+
+        file_names = os.listdir(source)
+
+        for file_name in file_names:
+            # print(file_name)
+            if file_name.endswith((".jpg", ".pdf", ".png")):
+                # print(target_dir)
+                shutil.copy(os.path.join(source, file_name), target_dir)
 
 
 class DamBreak(Problem):
@@ -400,6 +450,9 @@ class ParticleDispersion3D(Problem):
 
 if __name__ == '__main__':
     PROBLEMS = [
+        # Image generator
+        ManuscriptRFCImageGenerator,
+
         # Problem  no 1 (Dam break 2d and 3d)
         DamBreak,
         # Problem  no 2

### 2024-03-01 code/manuscript_rfc_image_generator.py

@@ -1,0 +1,227 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+import matplotlib.patches as patches
+
+from pysph_dem.geometry import create_circle_1
+from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, translate_system_with_left_corner_as_origin
+from pysph.base.utils import get_particle_array
+import pysph.tools.geometry as G
+
+
+rigid_body_diameter = 0.3
+rigid_body_radius = 0.3 / 2.
+dx = rigid_body_diameter / 10
+fluid_length_ratio = 5.
+fluid_height_ratio = 5.
+tank_length_ratio = 1.2
+tank_height_ratio = 1.2
+
+
+# x - axis
+fluid_length = fluid_length_ratio * rigid_body_diameter
+# y - axis
+fluid_height = fluid_height_ratio * rigid_body_diameter
+# z - axis
+fluid_depth = 0.
+
+# x - axis
+tank_length = tank_length_ratio * fluid_length
+# y - axis
+tank_height = tank_height_ratio * fluid_height
+# z - axis
+tank_depth = 0.0
+
+tank_layers = 3
+
+
+def hs_tank_with_spherical_particles():
+    xf, yf, xt, yt = hydrostatic_tank_2d(fluid_length, fluid_height,
+                                         tank_height, tank_layers,
+                                         dx, dx, False)
+
+    fluid = get_particle_array(name='rb',
+                               x=xf,
+                               y=yf,
+                               h=1.2 * dx)
+    tank = get_particle_array(name='rb',
+                              x=xt,
+                              y=yt,
+                              h=1.2 * dx)
+
+    x1, y1 = create_circle_1(rigid_body_diameter, dx)
+
+    x2, y2 = create_circle_1(rigid_body_diameter * 1.2, dx)
+    x2 += rigid_body_diameter
+    y2 -= rigid_body_diameter
+    x2 -= rigid_body_radius * 0.4
+    y2 += rigid_body_radius
+
+    x3, y3 = create_circle_1(rigid_body_diameter, dx)
+    x3 -= 1.5 * rigid_body_diameter
+    y3 += max(xf) - min(y3) - rigid_body_radius
+
+    x4, y4 = create_circle_1(rigid_body_diameter, dx)
+    x4 -= 1.5 * rigid_body_diameter
[…]

### 2024-03-01 code/mixing_particles_in_hs_tank_2d.py

@@ -1,0 +1,661 @@
+"""Rigid body falling in tank but 2D
+
+Run it using:
+
+python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme combined -d rb_falling_in_hs_tank_combined_output
+
+python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme master -d rb_falling_in_hs_tank_master_output
+
+
+TODO:
+
+1. Create many particles
+2. Run it on HPC
+3. Change the speed
+4. Change the dimensions
+5. Commit SPH-DEM and current repository
+6. Validate 1 spherical particle settled in hs tank
+7. Validate 2 spherical particles settled in hs tank
+8. Complete the manuscript
+9. Different particle diameter
+10. Different density
+"""
+import numpy as np
+import sys
+
+from pysph.examples import dam_break_2d as DB
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.tools.geometry import get_3d_sphere
+import pysph.tools.geometry as G
+from pysph.base.utils import get_particle_array
+
+from pysph.examples import cavity as LDC
+from pysph.sph.equation import Equation, Group
+from pysph.sph.scheme import add_bool_argument
+sys.path.insert(0, "./../")
+from pysph_rfc_new.fluids import (get_particle_array_fluid, get_particle_array_boundary)
+
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import SchemeChooser
+
+from pysph_dem.rigid_body.boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, translate_system_with_left_corner_as_origin
+# from geometry import hydrostatic_tank_2d, create_circle_1
+
[…]

### 2024-03-01 code/spherical_particle_figure_generator_for_manuscript.py

@@ -1,0 +1,127 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from pysph_dem.geometry import create_circle_1
+from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, translate_system_with_left_corner_as_origin
+from pysph.base.utils import get_particle_array
+import pysph.tools.geometry as G
+
+
+rigid_body_diameter = 0.3
+rigid_body_radius = 0.3 / 2.
+dx = rigid_body_diameter / 10
+fluid_length_ratio = 5.
+fluid_height_ratio = 5.
+tank_length_ratio = 1.2
+tank_height_ratio = 1.2
+
+
+# x - axis
+fluid_length = fluid_length_ratio * rigid_body_diameter
+# y - axis
+fluid_height = fluid_height_ratio * rigid_body_diameter
+# z - axis
+fluid_depth = 0.
+
+# x - axis
+tank_length = tank_length_ratio * fluid_length
+# y - axis
+tank_height = tank_height_ratio * fluid_height
+# z - axis
+tank_depth = 0.0
+
+tank_layers = 3
+
+
+def hs_tank_with_spherical_particles():
+    xf, yf, xt, yt = hydrostatic_tank_2d(fluid_length, fluid_height,
+                                         tank_height, tank_layers,
+                                         dx, dx, False)
+
+    fluid = get_particle_array(name='rb',
+                               x=xf,
+                               y=yf,
+                               h=1.2 * dx)
+    tank = get_particle_array(name='rb',
+                              x=xt,
+                              y=yt,
+                              h=1.2 * dx)
+
+    x1, y1 = create_circle_1(rigid_body_diameter, dx)
+
+    x2, y2 = create_circle_1(rigid_body_diameter * 1.2, dx)
+    x2 += rigid_body_diameter
+    y2 -= rigid_body_diameter
+    x2 -= rigid_body_radius * 0.4
+    y2 += rigid_body_radius
+
+    x3, y3 = create_circle_1(rigid_body_diameter, dx)
+    x3 -= 1.5 * rigid_body_diameter
+    y3 += max(xf) - min(y3) - rigid_body_radius
+
+    x4, y4 = create_circle_1(rigid_body_diameter, dx)
+    x4 -= 1.5 * rigid_body_diameter
[…]

### 2024-04-27 manuscript/paper.tex
First draft with some additional examples

@@
 \usepackage[utf8]{inputenc}
-\usepackage{cleveref}
+\usepackage[capitalise]{cleveref}
 \usepackage{algorithm}
@@
 \begin{abstract}
-  Particle dispersion is a fundamental physical phenomenon encountered in
-  various industries where powder and fluid interactions are
-  pivotal. Particularly, processes involving the mixing of powder with fluid
-  using a stirrer are commonplace. While experimental investigation of such
-  processes is often impractical due to their highly nonlinear nature,
-  numerical methods offer a viable alternative. Among these, Smoothed Particle
-  Hydrodynamics coupled with Discrete Element Method (SPH-DEM) stands out for
-  its ability to handle free surface fluid dynamics and model the complex
-  physics inherent in dispersion processes.
 
-  In this study, we initially develop and validate both the DEM and SPH
-  solvers. Validation includes testing against fundamental benchmarks such as
-  two-particle head-on collisions and particle-wall impacts for the DEM
-  solver, and Poiseuille flow for the fluid solver. Additionally, we validate
-  the rigid-fluid model through simulations of a single cylindrical body
-  entering a steady tank and the settling of two tandem cylinders in a
-  fluid-filled tank.
-
-  With confidence in the fidelity of our solver established, we delve into
-  investigating the mixing behavior of spherical particles dispersed in
-  water. Our study encompasses various scenarios, including particles with
-  densities higher or lower than the surrounding fluid, as well as particles
-  with varying radii. We also examine combinations of these factors.
-  \todoin{What factor have you considered to quantify the mixing
-    behaviour.}
-
-  \todoin{Write the findings}
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-{xxx}, {xxx}, {xxx}
+{particle dispersion}, {particle mixing}, {SPH-DEM}, {stirrer}
 
@@
 
+Particle dispersion is a fundamental physical phenomenon encountered in
+various industries where powder and fluid interactions are pivotal.  Petroleum
+industry \cite{wang2023developments}, The transport of bodies in internal
+systems \cite{Dai2021}, debris flow \cite{Qingyun2022}, the food processing
+industry \cite{Karunasena2014}, and ice-sea modeling \cite{Mintu2018} are a
+few areas to mention.  Particularly, processes involving the mixing of powder
+with fluid using a stirrer are commonplace \cite{li2022study}. While
+experimental investigation of such processes is often impractical due to their
+highly nonlinear nature, numerical methods offer a viable alternative. These
+systems are studied as part of two-way coupling models. The two-way coupling
+phenomena are nonlinear, and an analytical study is not feasible. A numerical
+study is preferable while handling such a phenomenon. A mesh-based or meshless
+technique can be utilized to study rigid fluid coupling (RFC) numerically.
+\Cref{fig:gloabl_body_frame_rb} illustrates a sample particle dispersion
+problem studied in the current work.
 \begin{figure}[!htpb]
@@
   \includegraphics[width=0.4\textwidth]{images/hs_tank_fluid_with_particles}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
+  \caption{An illustrative figure showcasing the dispersion of particles within a free surface tank.}
+  \label{intro:schematic}
 \end{figure}
 
-\begin{itemize}
-\item Fluid modeling using smoothed particle hydrodynamics
-  (\cref{sec:fluid--modeling})
-\item Interaction among the discrete spherical rigid particle units by
-  discrete element method (\cref{sec:rbd})
-\end{itemize}
+The combination of Discrete Element Method (DEM) for solid particle
+interactions and Computational Fluid Dynamics (CFD) for fluid modeling
+is a classic approach in handling particulate flow problem. In
+mesh-based CFD-DEM modeling, lattice Boltzmann method (LBM)
+\cite{xiong2014lbm} and finite volume method (FVM) \cite{kloss2012models} are
+utilized to handle the fluid dynamics. Similarly, in meshless schemes like
+Smoothed Particle Hydrodynamics (SPH) \cite{peng2021fully},
+Moving Particle Semi-implicit (MPS), and Particle Finite Element
+Method (PFEM) \cite{li2019modeling, franci2020pfem}, handles the fluid
+dynamics.  While handling the interaction between the fluid and solid
+particles, the interaction can be categorized into a resolved and unresolved
+coupling. In unresolved coupling, simplified models compute forces acting on
+solid particles within fluid flow, while fully resolved coupling computes
+forces comprehensively. Both strategies are applicable in both meshless
+\cite{cleary2015prediction, trujillo2020smooth} and mesh-based
+\cite{van2008numerical, ma2022review} CFD-DEM techniques. Research such as
+\cite{brosh2014accelerating} and \cite{peng2021fully} explore wide particle
+size distributions with CFD-DEM and SPH-DEM respectively.  Regarding
+non-Newtonian fluid modeling in mesh-based schemes, works like
+\cite{li2018dam} are notable and in meshless schemes, \cite{peng2021fully} is
+notable. \citet{zhu2008discrete} and \citet{ma2022review}
+delve into investigations on spherical and non-spherical particles
+respectively within CFD-DEM frameworks.  Meshless CFD-DEM, though fruitful,
+encounters challenges in handling problems with free surfaces and becomes
+computationally demanding with a large number of solid particles, especially
+in fully resolved coupling. In contrast, SPH offers advantages in such
+scenarios due to its inherent capability in handling free surfaces and
+adeptness in modeling large mesh deformation problems, facilitating the
+incorporation of novel physics.
 
-While the interaction among the rigid spherical particle and fluid particles
-are modeled by sampling the spherical particles into dummy SPH particles. This
-is explained in \cref{sec:rfc}.
+The SPH method is a meshless numerical method originally proposed by
+\citet{gingold1977smoothed} and \citet{lucy1977numerical} to model
+astrophysics problems. It has been extensively applied to simulate problems
+involving fluids, structural dynamics, fluid-structure interaction, granular
+physics, non-Newtonian fluid flows \cite{peng2021fully} among other areas
+\cite{monaghan2012smoothed}.  Various kind of particulate flows, involving,
+simple spherical particles mixing using unresolved coupling
+\cite{cleary2015prediction, markauskas2019coupled} and with debris
+flow \cite{canelas2016sph} with fully resolved coupling approach has been
+solved using SPH-DEM framework.  Handling particles of arbitrary shape in
+fluid flow is addressed in various works, including those by
+\citet{peng2021fully, canelas2016sph, amicarelli2015smoothed}.  Several
+variants of SPH, such as WCSPH \cite{peng2021fully, cleary2015}, and ISPH
+\cite{asai2021fluid}, are utilized for modeling fluid flow with particulate
+flows. The coupling between fluid and rigid bodies in the fully resolved
+category employs techniques such as the fixed ghost particle technique
+\cite{canelas2016sph, asai2021fluid}, single layers of dummy SPH particles
+\cite{peng2021fully}, and simple repulsive forces
+\cite{monaghan2009sph}. Coupling between SPH fluid particles and solid
+structures discretized as vertex edges is proposed by
+\cite{park2023new}. Particle settling with variable sizes is studied by
+\citet{zou2022study}.  Elastic behavior of spherical particles and dispersion
+studies are conducted by \citet{ng2021numerical}.  Interaction between rigid
+bodies of arbitrary sizes is addressed using various techniques, such as those
+discussed in papers by \citet{asai2021fluid}, citet{peng2021fully},
+\citet{canelas2016sph}.
 
-% \FloatBarrier%
-% \section{Fluid modeling}
+In the current work we cosider the particle dispersion within a large-scale
+under stirrer mixing phenomenon. We employ Smoothed Particle Hydrodynamics
+(SPH) to model fluid dynamics and the Discrete Element Method (DEM) to handle
+the dynamics and contact interactions among spherical particles. The
+interaction between solids and fluids is managed using a fixed ghost particle
+approach, ensuring a fully resolved simulation. We validate the fluid solver
+independently using Poiseuille flow and the DEM solver separately using
+fundamental benchmarks such as particle-particle and particle-wall
+impacts. Subsequently, the fully resolved coupled SPH-DEM solver is validated
+using three benchmarks: a single particle entering, two particles settling,
+and a forced wedge entry into a steady hydrostatic tank. Upon confirming the
+fidelity of the solver, we proceed with analyzing the mixing behavior of
+various spherical particles influenced by a stirrer in a water tank. We
+investigate scenarios involving particles of different densities, stirrer
+velocities, and variable sizes as part of our case study. The development work
+is conducted using PySPH\cite{ramachandran2021pysph}, an open-source code
+available at \url{https://github.com/pypr/pysph} . To ensure reproducibility,
+we utilize the automan package \cite{ramachandran2018automan} to automate all
+results generated in the current manuscript, aiming for a reproducible
+research approach.
 
-% \FloatBarrier%
-% \subsection{Boundary conditions}
-
-% \FloatBarrier%
-% \section{Solid phase modeling}
-
-% \FloatBarrier%
-% \subsection{Discrete element method}
-
-% \FloatBarrier%
-% \subsection{Rigid body equations}
-
-% \FloatBarrier%
-% \section{Rigid fluid coupling}
-
-% \FloatBarrier%
-% \section{Results}
+The structure of this paper is as follows: In
+\cref{sec:fluid-modeling}, we explain the numerical method used to model fluid
+dynamics. \Cref{sec:rbd} outlines the equations governing the dynamics
+of rigid bodies and the contact force model employed to resolve collisions
+among them. The coupling between rigid spherical particles and the fluid is
+detailed in \cref{sec:rfc}. Our results are presented in
+\cref{sec:results}, where various problems from the literature are simulated to
+validate the current solver, and particle dispersion is examined.
 
 \FloatBarrier%
-\subsection{Fluid modeling}
-\label{sec:fluid--modeling}
+\section{Fluid modeling}
+\label{sec:fluid-modeling}
+In the current work, we follow a weakly-compressible SPH approach to model the
+fluid. Smoothed particle hydrodynamics is initially developed by Lucy
+\cite{lucy1977numerical} and Gingold and Monaghan \cite{gingold1977smoothed}
+to model astrophysical problems. The continuum in SPH is modeled using
+particles, which has physical properties such as mass, velocity, and the
+particles interact based on the governing equations using a Guassian-like
+kernel \cite{SPH_papers}.
 
-In the current work, we follow a weakly-compressible SPH approach to model the
-fluid. The SPH discretization of the continuity
+\FloatBarrier%
+\subsection{Fluid governing equations}
+\label{sec:fluid--governing-equations}
+Equations governing the fluid motion are, conservation of mass
+\begin{equation}
+  \label{eq:ce}
+  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
+\end{equation}
+and conservation of linear momentum,
+\begin{equation}
+  \label{eq:me}
+  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
+  + g_i,
+\end{equation}
+where $\rho$ is the density, $u_i$ is the $i$\textsuperscript{th} component of
+the velocity field, $x_j$ is the $j$\textsuperscript{th} component of the
+position vector, $g_i$ is the component of body force per unit mass and
+$\sigma_{ij}$ is stress tensor.
+
+The stress tensor is split into a pressure and viscous parts,
+\begin{equation}
+  \label{eq:fluid-stress-decomposition}
+  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
+\end{equation}
+where $\eta$ is the kinematic viscosity of the fluid, $p$ is the pressure,
+$\delta_{ij}$ is the Kronecker delta function.
+
+\FloatBarrier%
+\subsection{Discretized fluid governing equations}
+\label{sec:sph--governing-equations}
+The governing equations involve function, derivative and divergence
+operators. In SPH, these operators are approximated based on the positions,
+mass and the kernel values of the discretized particles. Assume that the
+domain is discretized into N particles with mass $m_i$ and volume
+$\Delta v_i$, We have
+\begin{equation}
+  \label{eq:mass_repr}
+  m_j = \Delta v_i \> \rho_i.
+\end{equation}
+Based on this discretization, the discrete function approximation is given as,
+\begin{equation}
+  \label{eq:discrete_form}
+  A_i = \sum_{j \in \text{Neigh}(i)}\> \frac{m_j}{\rho_j} A_j\> W(\ten{x}_i - \ten{x}_j, h),
+\end{equation}
+where $A(\boldsymbol{x}_i) = A_i$ is the value of the field property of
+particle i, similarly for $A_j$. Here, $\text{Neigh}(i)$ is the neighbours of
+particle $i$.  A symmetric derivative approximation~\cite{Violeau16} is given
+as,
+\begin{equation}
+  \nabla A(\ten{x}_i) = \rho_i \sum_{j} m_j \left(\frac{A_i}{\rho_i^2} + \frac{A_j}{\rho_j^2}\right) \nabla W_{ij}.
+\end{equation}
+A symmetric gradient operator ensures equal and opposite forces acting on the
+particles.
+
+An approximation of the divergence operator is used to discretize the
+\cref{eq:ce}.  It is given as,
+\begin{equation}
+  \label{intro:eq:sph-continu-div-final}
+  \nabla \cdot \ten{v}(\ten{x}_i) = \frac{1}{\rho_i} \sum_{j} m_j \left(\ten{v}_j - \ten{v}_i\right) \cdot \nabla W_{ij}.
+\end{equation}
+
+% \subsection{Discretized fluid governing equations}
+The SPH discretization of the continuity
 equation~\cref{eq:sph-discretization-continuity} and the momentum equation
@@
     \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}  \;+\;
-  \ten{g}_{a} + \text{force due to rb},
+  \ten{g}_{a},
 \end{multline}
 where $\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
-% fluid and \textcite{morris1997modeling} formulation is used to discretize the
+fluid and \cite{morris1997modeling} formulation is used to discretize the
 viscosity term.
@@
 We add to the momentum equation an additional artificial viscosity term
-% $\Pi_{ab}$~\parencite{monaghan-review:2005} to maintain the stability of the
+$\Pi_{ab}$~\cite{monaghan-review:2005} to maintain the stability of the
 numerical scheme, given as,
@@
 \FloatBarrier%
-\subsection{Boundary conditions}
+\subsection{Boundary Conditions}
 \label{sec:boundary_conditions}
+
+The ghost particle approach of \cite{Adami2012} is used to model the
+boundaries. We use three layers of ghost particles to model the solid wall.
+The properties of the solid wall are interpolated from the fluid particles.
+
+When the viscous force is computed, the no slip boundary condition is used,
+where the velocity on the boundary set as,
+\begin{equation}
+  \label{eq:no-slip-bc-u}
+  \ten{u}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}}.
+\end{equation}
+The projected velocity $\ten{\hat{u}}_{\text{a}}$ on the ghost particles is
+computed using,
+\begin{equation}
+  \label{eq:v-ghost}
+  \ten{\hat{u}}_a = \frac{\sum_b\ten{u}_b W_{ab}}{\sum_b W_{ab}},
+\end{equation}
+where $\ten{u}_b$, is the momentum velocity
+of the fluid and $W_{ab}$ is the kernel value between the fluid
+particle and the ghost particle.
+
+The pressure of the boundary particle is extrapolated from its surrounding
+fluid particles by the following equation,
+\begin{equation}
+  \label{eq:pressure-bc}
+  p_w = \frac{\Sigma_f p_f W_{wf} + (\ten{g} - \ten{a}_{\ten{w}}) \cdot \Sigma_f
+    \rho_f \ten{r}_{wf} W_{wf}}{\Sigma_f W_{wf}},
+\end{equation}
+where $\ten{a}_w$ is the acceleration of the wall. The subscript $f$ denotes
+the fluid particles and $w$ denotes the wall particles.
 
@@
 % freedom (DOF), divided into $3$ translational and $3$ rotational.
+
+% An approach using quaternions is given in \cite{dietemann2020smoothed}
+% An another paper using quaternions \cite{guan2024numerical}
+
 The equations governing the dynamics of a rigid body are, balance of linear and
@@
 \end{eqnarray}
-We follow \cref{sec:contact-algorithm} to compute force
+We follow \cref{sec:dem} to compute force
 $\ten{F}_{\text{cont}}^a$ acting on particle $i$ due to the interaction with
-the rigid bodies. The force $\ten{F}_{\text{Fl}}^i$ acting due to the
-interaction with the fluid particles follows \cref{subsec:fsi}.
+the rigid bodies. The force $\ten{F}_{\text{rfc}}^i$ acting due to the
+interaction with the fluid particles follows \cref{sec:rfc}.
 
@@
   \includegraphics[width=0.7\textwidth]{images/spherical_particles_dem_representation}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
+  \caption{Demonstration of contact handling between two rigid spherical
+    particles immersed in a fluid tank.}
+  \label{fig:spherical-particles-in-tank-dem}
 \end{figure}
@@
 We resolve the contact among the spherical particles using discrete element
-method. In the current work we have utilized the contact force model proposed
-by \citet{mohseni2021particle}. The force acting on a particle $a$ due to the
-interaction with the particle $b$ can be resolved into a normal and tangential
-component. The normal force component is utilised to make sure that the
-particle do not penetrate into each other, while the tangential component is
-used to model the friction between the interacting solids.  The normal force
+method. In the current work we have utilized a non-linear contact force
+model. In DEM, the force acting on a particle $a$ due to the interaction with
+the particle $b$ is resolved into a normal and tangential component. The
+normal force component is utilised to make sure that the particle do not
+penetrate into each other, while the tangential component is used to model the
+friction between the interacting particles.  The normal force
 ($\teng{F}_a^{n}$) on particle $a$ due to the interaction with the particles
-$b$ is given as,
+$b$ is given by a non-linear, Hetzian model \citet{brilliantov1996model},
 \begin{equation}
   \label{eq:contact-algorithm-normal}
-  \ten{F}_a^n = k_r \delta_{n^{c}}^{a} \ten{n}_a^{c}.
+  \ten{F}_a^n = k_r \delta_{n} \ten{n}.
 \end{equation}
-Here, the overlap $\delta_{n^{c}}^{a}$ is computed using
+Here, the overlap $\delta_{n}$ is computed using
 \begin{equation}
   \label{eq:cf-overlap}
-  \delta_{n^{c}}^{a} = \Delta x - d_a,
+  \delta_{n} = R_{a} + R_{b} - r_{ab},
 \end{equation}
-where the normal contact vector $\ten{n}_a^{c}$ is computed using
-\begin{equation}
-  \label{eq:cf-normal-vector}
-  \ten{\hat{n}}_a^{c} = \frac{
-    \displaystyle\sum\limits_{b = 1}^{\text{NP}^{b}} \;
-    \frac{\ten{r}_{ab}}{r_{ab}}  \frac{m_b}{\rho_b} W_{ab}}
-  {
-    \displaystyle\sum\limits_{b = 1}^{\text{NP}^{b}} \;
-    \frac{m_b}{\rho_b} W_{ab}},
-\end{equation}
-\begin{equation}
-  \label{eq:cf-normal-vector}
-  \ten{n}_a^{c} = \frac{\teng{\hat{n}}_a^{c}}{||\teng{\hat{n}}_a^{c}||}.
-\end{equation}
-With $\Delta x$ being the initial spacing between the particles, $k_r$ is the normal
-spring stiffness coefficient. Note that while computing the overlap of
-particle $a$ with the body $B$ we have computed an effective overlap, rather
-than per particle interaction. This effectively is able to model the
-interaction between non smooth surfaces in contrast with particle-particle
-force computation.
+$k_r$ is the normal spring stiffness coefficient, which is computed using the
+material properties of the bodies in contact \cite{golshan2023lethe}.
 
@@
 \label{sec:tangential-force-computation}
-We associate a tangential spring attached to particle $i$ and body $B$ to
-compute the tangential force, which initially has a magnitude of zero
-($|\Delta \textit{\textbf{l}}_a|=0$). And the tangential spring is activated
-when the particle comes into contact with body $B$. The tangential force is
-history-dependent. The contact friction force is proportional to the
-tangential spring displacement, which is integrated over the contact time as
+To handle the frictional contact, we associate a tangential spring attached to
+particle $a$ and particle $b$ to compute the tangential force, which initially has
+a magnitude of zero ($|\Delta \textit{\textbf{l}}_a|=0$). The tangential spring
+is activated when the particle comes into contact with particle $b$. The
+tangential force is history-dependent. The contact friction force is
+proportional to the tangential spring displacement, which is integrated over
+the contact time as
 \begin{equation}
@@
 \end{equation}
-where $\Delta t$ is the time step, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is
-the relative velocity of the primary particle $a$ with respect to the
-closest secondary particle $b$, and $k_f$ is the tangential spring stiffness
-coefficient. The tangential unit vector is computed by,
+where $\Delta t$ is the time step, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is the
+relative velocity of particle $a$ with respect to the contacting particle $b$,
+and $k_f$ is the tangential spring stiffness coefficient. The tangential
+spring stiffness is computed similar to the normal spring
+stiffness\cite{golshan2023lethe}.  The tangential unit vector is computed by,
 \begin{equation}
   \label{eq:tangential-vect}
-  \ten{t}_a = \frac{\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}_a^{c}) \ten{n}_a^{c}}{|\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}_a^{c}) \ten{n}_a^{c}|}.
+  \ten{t}_a = \frac{\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}) \ten{n}}{|\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}) \ten{n}|}.
 \end{equation}
@@
 interacting solids. Finally, the total force acting on the particle $a$ due to
-the interaction with body $B$ is:
+the interaction with particle $b$ is:
 \begin{equation}
@@
 
-% \begin{figure}[!htpb]
-%   \centering
-%   \includegraphics[width=0.3\textwidth]{images/contact_force/contact_force_description_3}
-%   \caption{Force transfer to the secondary particles $b$ from the primary body particle $a$}
-% \label{fig:secondary_particle_contact_foce_transfer}
-% \end{figure}
-An equal and opposite force of the same magnitude is applied to the closest
-secondary particle $b$ of $a$ as shown in
-\cref{fig:secondary_particle_contact_foce_transfer},
+An equal and opposite force of the same magnitude is applied to
+particle $b$, given as
 \begin{equation}
@@
 
-% =========================================== %
-% ------ Results start ---------------------- %
-% =========================================== %
+\FloatBarrier%
+\section{Rigid fluid coupling}
+\label{sec:rfc}
 
-\FloatBarrier%
-\subsection{Rigid fluid coupling}
-\label{sec:rfc}
+% Coupling equation with single particles he2017coupled
+% Coupling with dummy particles \cite{guan2024numerical}
+% A different coupling equation meng2022hydroelastic
 
@@
     \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/real_spherical_particles}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-0}
+    \subcaption{A rigid spherical particle}%\label{fig:rings:ipst-nu-0.47-0}
   \end{subfigure}\hspace{15mm}%
@@
     \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/sph_sampled_spherical_particles}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-1}
+    \subcaption{A rigid spherical particle sampled with dummy SPH particles}%\label{fig:rings:ipst-nu-0.47-1}
   \end{subfigure}
@@
 \end{figure}
-In order to compute the force acting on the spherical particle due to the
-interacting fluid we sample the spherical particle with dummy SPH particles,
-as shown in \cref{fig:real_particle_sph_sampling}. Here the spherical particle
-is sampled using dummy SPH particles, while SPH particles are being placed
-equispaced. With spherical particles being discretized into SPH particles and
-immersed in fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
+To calculate the force exerted on the spherical particle by the surrounding
+fluid, we employ a method involving the sampling of the spherical particle
+using dummy Smoothed Particle Hydrodynamics (SPH) particles, depicted in
+\cref{fig:real_particle_sph_sampling}. These SPH particles are evenly
+distributed and remain stationary, moving in tandem with the velocity of the
+rigid particle at any given location. To establish the pressure of these SPH
+particles, we utilize the fixed ghost particle boundary technique outlined in
+\cref{sec:boundary_conditions}.
+
+With spherical particles being discretized into SPH particles and immersed in
+fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
 \begin{figure}[!htpb]
@@
   \includegraphics[width=0.7\textwidth]{images/rfc_zoomed_combined}
-  \caption{Body frame and local frame description of rigid body}
+  \caption{A rigid spherical particle sampled with dummy SPH particles being
+    immersed in a fluid tank. An SPH particle representation}
   \label{fig:many_rb_in_fluid_sph_particles}
 \end{figure}
-
-Force on each sampled SPH particles consisting of the rigid body due to the
-interaction with the fluid particle is given as. The mass of each dummy
-particle being sampled in the spherical particle is considered as
-hydrodynamics mass. The force on the fluid particle due to the interaction
-with the sampled dummy SPH particles is considered in the momentum and the
-continuity equation. The force acting on the sampled dummy SPH particle due to
-the interaction with the fluid is given by,
+The force on the fluid particle due to the
+interaction with the sampled dummy SPH particles is considered in the momentum
+\cref{eq:sph-momentum-fluid} and the continuity
+\cref{eq:sph-discretization-continuity}. The force acting on the sampled dummy
+SPH particle due to the interaction with the fluid is given by,
 \begin{equation}
-  \label{eq:sph-discretization-continuity}
-  \frac{{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \;
-  \rho_{a} \; {\ten{u}}_{ab} \; \cdot \nabla_{a} W_{ab},
+  \label{eq:rfc-force}
+  \ten{F}_{\text{rfc}}^a = -m_a \sum_{f} m_f \bigg(\frac{p_f}{\rho_{f}^2} +
+  \frac{p_a}{\rho_{a}^2}\bigg) \nabla_{a} W(x_{af}).
 \end{equation}
-The force here is composed of two components, one is due to the pressure and
-due to viscosity.
+Here, $m_a$ signifies the hydrodynamic mass of the sampled dummy SPH particle,
+and $\rho_a$ represents its hydrodynamic density. While $m_f$, $p_f$ and
+$\rho_f$ are mass, pressure and density of the fluid particle.
 
 \FloatBarrier%
-\subsection{Time Integration}
+\section{Time Integration}
 
-Rigid body and the fluid follow the kick-drift-kick time integration scheme. The
-modeling of rigid-rigid interaction requires lower time step than the fluid. We
-choose the minimum of both the timesteps to move the system forward in time. For
-the numerical stability of fluid, the time step depends on the CFL condition as,
+We use the kick-drift-kick scheme for the time integration. We move the
+velocities of the fluid and the solid particles to half time step,
+\begin{equation}
+  \label{eq:velocity-update-stage-1}
+  \ten{u}_a^{n+\frac{1}{2}} = \ten{u}_a^{n} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^n,
+\end{equation}
+Then the time derivative of density is calculated using the
+\cref{eq:sph-discretization-continuity} using the velocities at half time
+step. The new time step density and particle position is updated by,
+\begin{equation}
+  \label{eq:density-update-stage-2}
+  \rho_{a}^{n+1} = \rho_{a}^{n} + \Delta t \; \bigg(\frac{d\rho_{a}}{dt}\bigg)^{n+\frac{1}{2}},
+\end{equation}
+\begin{equation}
+  \label{eq:position-update-stage-2}
+  \ten{r}_{a}^{n+1} = \ten{r}_{a}^{n} + \Delta t \; \ten{u}_{a}^{n+1}.
+\end{equation}
+%
+Finally, at new time-step particle position, the momentum velocity is updated
+\begin{equation}
+  \label{eq:velocity-update-stage-3}
+  \ten{u}_a^{n+1} = \ten{u}_a^{n+\frac{1}{2}} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^{n+1}.
+\end{equation}
+
+The modeling of rigid-rigid interaction requires lower time step than the
+fluid. We choose the minimum of both the timesteps to move the system forward
+in time. For the numerical stability of fluid, the time step depends on the
+CFL condition as,
 \begin{equation}
@@
   \label{eq:rfc:time-step-body-force}
-  \Delta t_{\text{rb}} \leq \frac{\pi}{50} \sqrt{\frac{m}{K_r}}.
+  \Delta t_{\text{rb}} \leq \frac{\pi}{50} \sqrt{\frac{m}{k_r}}.
 \end{equation}
@@
 \label{sec:results}
+Initially, we validate our fluid solver through the resolution of the
+Poiseuille flow problem. Subsequently, we validate the Discrete Element Method
+(DEM) solver by simulating a normal head-on collision between two spherical
+particles and addressing a particle-wall impact scenario. We validate the
+coupled Smoothed Particle Hydrodynamics (SPH)-DEM solver is confirmed through
+simulations involving a spherical particle entering a steady tank and a
+falling solid in a water tank and a floating solid. Lastly, we investigate the
+mixing behavior of spherical particles under a stirrer, examining cases with
+varying densities and diameters.
 
@@
 
-\begin{itemize}
-\item Unsteady flow between two infinite, parallel paltes at rest in presence
-  of pressure gradient.
-\item Write about the location of the plates.
-\item Which way the flow is going (positive x or negative x)
-\item In this exact conditions, the Navier-Stokes equations admit the time
-  dependent solution (Write solution (equation 19))
-\item Periodic boundary conditions
-\item The accuracy of the results presented here validate the developed
-  no-slip boundary method inthe presence of straight boundaries.  The
-  remainder of this section addresses the more complexcase of non-straight
-  boundaries.
-\item Write about the schematic
-\item Write the resulting velocity profile
-\item Numerical parameters are important
-\item A body force of 1e-5
-\item Viscosity 0.01
-\item Time of 50 seconds
-\item spacing of 1 / 60
-\item Length in y is 2 * self.d=0.5
-\item Length in x 0.4 * self.Ly
-\item self.re = self.options.re
-\item self.Vmax = self.nu*self.re/(2*self.d)
-\item self.c0 = 10*self.Vmax
-\item self.p0 = self.c0**2*self.rho0
-\item self.fx = self.Vmax * 2*self.nu/(self.d**2)
-\end{itemize}
-
-The analytical solution from Morris is given as
-
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{images/fluid_01_benchmark_poisuelle/poiseuille_schematic}
+  \caption{Poiseuille flow problem: Schematic of a fluid being driven in
+    between two parlell plates due to a pressure gradient force.}
+  \label{fig:poiseuille_schematic}
+\end{figure}
+We study unsteady flow between two infinite, parallel paltes at rest in
+presence of pressure gradient to validate our fluid solver implementation.
+The plates are placed $1$ m apart vertically, where the fluid is driven due to
+a pressure gradient, a form of body force. The flow is towards positive x
+direction. The schematic is shown in \cref{fig:poiseuille_schematic}.  In this
+exact conditions, the Navier-Stokes equations admit the time dependent
+solution given in \cref{eq:poiseuille_exact_soln}, as given by
+\citet{morris1997modeling}
 \begin{equation}
-  \label{eq:sph-discretization-continuity}
+  \label{eq:poiseuille_exact_soln}
   v_x(y, t) = \frac{F}{2 \nu}y(y - L) + \sum_{n=0}^{\infty}\frac{4FL^2}{\nu \pi^3 (2n + 1)^3} \sin\bigg(\frac{\pi y}{L} (2 n + 1) \bigg) \exp\bigg(\frac{ (2 n + 1)^2 \pi^2 \nu}{L^2} t\bigg)
 \end{equation}
+$\nu$ is kinematic viscosity ($\frac{\mu}{\rho_0}$). This test case serves to
+validate the no-slip boundary condition of our developed scheme. We use
+numerical parameters such as a viscosity of $0.01$, a particle spacing of
+$\frac{1}{60}$, and set the speed of sound to ten times the maximum velocity
+the fluid can attain. The simulation runs for a total duration of $50$
+seconds.
 
-$\nu$ is kinematic viscosity ($\frac{\mu}{\rho_0}$)
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/fluid_01_benchmark_poisuelle/poiseuille_schematic}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
-\end{figure}
-
+\Cref{fig:poiseuille_soln_graph} depicts the variation of the u-velocity in
+y-direction, compared to the analytical formula given in
+\cref{eq:poiseuille_exact_soln}.  By observing
+\cref{fig:poiseuille_soln_graph}, we notice a close resemblance between the
+SPH simulation results and the analytical solution in
+\cref{eq:poiseuille_exact_soln}, thus validating our solver.
 \begin{figure}[!htpb]
@@
   \includegraphics[width=0.4\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.png}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
+  \caption{Velocity profile of the Poiseuille flow compared against the
+    analytical solution at time $t=50$ seconds.}
+  \label{fig:poiseuille_soln_graph}
 \end{figure}
+
+% \FloatBarrier%
+% \subsection{Rigid body validation: Dzhanibekov effect on a T-shaped rigid
+% body}
+% \label{sec:rb_1}
+% % https://doi.org/10.1063/5.0190167
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/results_dem_1_validation_particle_particle_impact/dem_01_head_on_schematic}
-  \caption{Body frame and local frame description of rigid body}
+  \includegraphics[width=0.6\textwidth]{images/results_dem_1_validation_particle_particle_impact/dem_01_head_on_schematic}
+  \caption{Schematic of two spherical particles of equal radius in a
+    head-on collision with equal magnitude of velocity but opposite direction.}
   \label{fig:result:dem_1_schematic}
 \end{figure}
-For the initial validation of the Discrete Element Method (DEM), we examine
-the head-on collision of two spherical particles. In
+To validate the Discrete Element Method (DEM) solver, we analyze the direct
+collision between two spherical particles.  In
 \cref{fig:result:dem_1_schematic}, the initial setup depicts both particles
@@
 kg\,m\textsuperscript{-3}.  For the current scenario, we assume there is no
-friction or gravity acting on the particles.
+friction among the particles and no gravity acting on the particles.
 \Cref{fig:result:dem_1_force_vs_overlap} depicts the variation of the normal
 force and the amount of overlap, compared to the analytical findings presented
-in \citet{xxxx}. The force curve generated by our current implementation
-closely matches the analytical result, confirming the validation of our DEM
-solver's normal contact force model.
+in \cite{chung2011benchmark}. The force curve generated by our current
+implementation closely matches the analytical result, hereby confirming the
+validation of our DEM solver's model for normal contact force.
 \begin{figure}[!htpb]
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
-  \caption{Body frame and local frame description of rigid body}
+  \includegraphics[width=0.6\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
+  \caption{Variation of the normal impact force with overlap of the impacting
+    particles, compared to the analytical result.}
   \label{fig:result:dem_1_force_vs_overlap}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/results_dem_2_validation_particle_wall_impact/schematic}
-  \caption{}
+  \includegraphics[width=0.6\textwidth]{images/results_dem_2_validation_particle_wall_impact/schematic}
+  \caption{Schematic of a spherical particle impacting a wall
+    with same magnitude of velocity but different impact angles.}
   \label{fig:result:dem_sw_contact_schematic}
@@
 particle with wall with different incident angles and a constant velocity in
-magnitude. This test case is helpful in testing the tangential part of our DEM
-implementation. The schematic of the body and wall is shown in
-\cref{fig:result:dem_sw_contact_schematic}. The radius of the impacting particle is
-$0.0025$ m and is made of aluminium oxide. The particle has a Young's modulus
-of $3.8 \times 10^{11}$ N\,m\textsuperscript{-2}, a Poisson ratio of $0.23$, and a
-density of $4000$ kg\,m\textsuperscript{-3}. The impact velocity has a
-magnitude of $3.9$ m\,s\textsuperscript{-1}. The friction coefficient among
-the wall and the particle is $0.092$.
+magnitude. This test case is useful in testing the tangential interaction
+modeling of our DEM solver.  The current problem was experimentally
+investigated by \citet{kharaz2001experimental}, and is commonly employed by
+various DEM solvers to validate their codes, as seen in the work of
+\cite{di2004comparison} and \cite{golshan2023lethe}.  The schematic of the
+body and wall is shown in \cref{fig:result:dem_sw_contact_schematic}.
+The dimensions and material properties of both the particle and the wall are
+set based on the study by \cite{di2004comparison,kharaz2001experimental}. The
+radius of the impacting particle is $0.0025$ m and is made of aluminium
+oxide. The particle has a Young's modulus of $3.8 \times 10^{11}$
+N\,m\textsuperscript{-2}, a Poisson's ratio of $0.23$, and a density of $4000$
+kg\,m\textsuperscript{-3}. The wall's Young's modulus is $70\times 10^{9}$
+N\,m\textsuperscript{-2}, with a Poisson ratio of $0.25$.  The impact velocity
+has a magnitude of $3.9$ m\,s\textsuperscript{-1}. The coefficient of friction
+between the wall and the particle is $0.092$.
 
-In \cref{fig:result:dem_sw_contact_omega_vs_theta}, we plot the variation of
-the rebound angular velocity with the incident impact angle, compared against
-the experimental result given in \citet{xxxx}. The variation of the angular
-velocity produced by our current implementation matches with the experimental
-result, confirming the validation of our DEM solver's tangential part of the
-contact force model.
+In \cref{fig:result:dem_sw_contact_omega_vs_theta}, we show variation of the
+rebound angular velocity with the incident impact angle, compared to
+experimental data from \citet{kharaz2001experimental}.  The angular velocity
+variation generated by our present implementation closely aligns with the
+experimental data, thereby validating the tangential
+contact model.
 \begin{figure}[!htpb]
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/benchmark_4_sw_colliding_oblique/angle_vs_ang_vel.pdf}
-  \caption{Body frame and local frame description of rigid body}
+  \includegraphics[width=0.6\textwidth]{figures/benchmark_4_sw_colliding_oblique/angle_vs_ang_vel.pdf}
+  \caption{Variation of the rebound angular velocity of the impacting particle
+    with the incidence angle, compared to the experimental result and Lethe
+    DEM solver by \cite{golshan2023lethe}.}
   \label{fig:result:dem_sw_contact_omega_vs_theta}
@@
   \includegraphics[width=0.4\textwidth]{images/rfc_01_skillen_2013_particle_entry_in_hs_tank/Skillen_2013_particle_entry_in_hs_tank}
-  \caption{Half Buoyant}
+  \caption{A circular cylinder entering into a calm water tank under the
+    influence of the gravity.}
   \label{fig:results_rfc_01_skillen_2013}
 \end{figure}
-To validate the rigid fluid coupling solver, we study the motion of a circular
-cylinder dropping into a steady tank. This problem has been studied
-experimentally by Greenhow and Lin
-\citet{xxxx}. \Cref{fig:results_rfc_01_skillen_2013} shows the initial
-configuration of the cylinder placed at $0.5$ m from the free surface. The
-radius of the disc is taken as $0.11$ m, while we consider two cases with the
-density of $500$ and $1000$ kg\,m\textsuperscript{-1}. The cylinder falls
-under the gravity into the tank.
 
-\todoin{Initial spacing, viscosity, gravity, h value, speed of sound, number of
-  particles, resolution write in a table}
+To validate the rigid-fluid coupling solver, we examine the motion of a
+circular disc descending into a steady hydrostatic tank, considering two
+different densities for the disc. This scenario has been investigated
+experimentally by
+\citet{greenhow1983nonlinear} and
+numerically by various studies, including
+\citet{sun2006water} using the Boundary Element Method
+and \cite{sun2018accurate} employing the $\delta^+$-SPH technique.
+\Cref{fig:results_rfc_01_skillen_2013}
+illustrates the initial setup, with the cylinder positioned $0.5$ meters from
+the free surface. The cylinder's radius is $0.11$ meters, and we investigate
+cases with densities of $500$ and $1000$ kg,m\textsuperscript{-3}.
+The cylinder descends due to gravity into the tank. We perform tests using
+three different spacings to assess convergence: resolving the cylinder
+diameter into 20, 50, and 80 particles, resulting in spacings of $5.5 \times 10^{-3}$ m,
+$2.2 \times 10^{-3}$ m, and $1.375 \times 10^{-3}$ m respectively. We employ a kinematic viscosity of
+$1 \times 10^{-6}$ m\textsuperscript{2}/s for water and do not utilize artificial
+viscosity in this case. The simulation runs for a total time of $0.16$
+seconds, utilizing a smoothing length (h) equal to the particle spacing in
+each scenario. The speed of sound is set to ten times the maximum fluid
+velocity attainable.
 
-\cref{fig:result_rfc_01_result_displacement}, depicts the evolution of the
+\Cref{fig:result_rfc_01_result_displacement}, depicts the evolution of the
 depth of penetration of the cylinder, compared against the experimental result
-by \citet{xxxx}, numerical techniques of boundary element method
-(BEM)(\cite{xxx}) and delta-plus SPH (\cite{xxx}). From
-\cref{fig:result_rfc_01_result_displacement}, we find that the current solver
-matches well with the experimental result and also converges while increasing
-the resolution.
+by \citet{greenhow1983nonlinear}, numerical techniques of boundary element
+method (BEM)(\cite{sun2006water}) and delta-plus SPH
+(\cite{sun2018accurate}). From \cref{fig:result_rfc_01_result_displacement},
+we find that the current numerical results matches well with the experimental result as
+well as the numerical studies and also converges while increasing the
+resolution.
 \begin{figure}[!htpb]
@@
     \includegraphics[width=1.0\textwidth]{figures/skillen_2013_water_entry_half_buoyant/penetration_vs_t}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-0}
+    \subcaption{Half buoyant cylinder}%\label{fig:rings:ipst-nu-0.47-0}
   \end{subfigure}
@@
     \includegraphics[width=1.0\textwidth]{figures/skillen_2013_water_entry_neutrally_buoyant/penetration_vs_t}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-1}
+    \subcaption{Neutrally buoyant cylinder}%\label{fig:rings:ipst-nu-0.47-1}
   \end{subfigure}
-  \caption{}
+  \caption{Variation of the penetration depth of the cylinder with time,
+    compared to BEM model \cite{sun2006water} and $\delta$+SPH model\cite{sun2018accurate}.}
 \label{fig:result_rfc_01_result_displacement}
@@
 \FloatBarrier%
-\subsection{RFC validation 2: Two tandem particles entering into a tank}
-\label{sec:rfc_validation_2_single_particle_entry}
+\subsection{RFC validation 2: A 3D cube falling in water}
+\label{sec:rfc_validation_2_falling_solid_in_water}
+
+The current test case involves falling of a solid cube in a calm water
+tank. The position of the cube is compared with the
+experimental\cite{wu2014two} result for the validation of the current SPH-DEM
+solver. This problem has been used as a standard benchmark in validating
+several other numberical techniques, such as in VOF-DEM solver
+\cite{nan2022cfd} and other SPH-DEM solvers \cite{qiu20173d}. The cube has a
+side length of $20$ mm. While the dimentions of the water tank is 150 mm
+$\times$ 140 mm $\times$ 140 mm. While the water depth is taken as $131$ mm. The density
+of the water is taken as $1000$ kg,m\textsuperscript{-3}, and the density of
+the cube is $2,120$ kg,m\textsuperscript{-3}. The schemtic of the initial
+configuration is shown in \cref{fig:results_rfc_02_falling}. We show that the
+current solver can handle 3D problems with this test case.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/rfc_02_falling_solid_in_water/schematic}
+  \caption{Schematic of a cube of density $2120 kg,m\textsuperscript{-3}$
+    immersed half way in a steady hydrostatic tank is allowed to settle under
+    gravity.}
+  \label{fig:results_rfc_02_falling}
+\end{figure}
+
+\Cref{fig:results_rfc_02_y_vs_t} shows the evolution of the y-position of
+center of mass of the cube, compared against the experimental result by
+\citet{wu2014two}. From \cref{fig:results_rfc_02_y_vs_t}, the comparison
+reveals a close correspondence between the results obtained by our solver and
+the experimental findings, affirming its capability to handle fluid-solid
+coupling problems efficiently.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.6\textwidth]{figures/wu_2014_falling_solid_3d/z_vs_t}
+  \caption{Vertical position variation of the center of mass of the cube with
+    time, compared against the experimental result by \citet{wu2014two}.}
+  \label{fig:results_rfc_02_y_vs_t}
+\end{figure}
+
+% \FloatBarrier%
+% \subsection{RFC validation 3: Falling solid in water}
+% \label{sec:rfc_validation_3_falling_solid_in_water}
+
+% zhang2009simulation
+% \cite{wu2014two} experimental.
+% \cite{qiu20173d} SPH-DEM
+% \cite{nan2022cfd} using VOF-DEM
+
+% \FloatBarrier%
+% \subsection{RFC validation 3: Force acting on particle in a shear flow}
+% \label{sec:rfc_validation_3_single_particle_in_shear_flow}
+
+% \FloatBarrier%
+% \subsection{RFC testing 1: Falling circular body in water}
+% \label{sec:rfc_testing_1_falling_circular_body_in_water}
+
+% We take a circular body and change the viscosity of the fluid and check the
 
@@
 \label{sec:mixing-spherical-particles-in-fluid-tank}
+
+% \FloatBarrier%
+% \subsection{Mixing of spherical particles in a fluid tank with turbine impeller}
+% \label{sec:mixing-spherical-particles-in-tank}
+
+% Study of free-surface and solids suspension in top-sealed tanks stirred by
+% pitched blade turbine impellers through DEM-VOF method
+% This paper has an example of mixing problem.
 

### 2024-04-27 automate.py

@@ -39,8 +39,8 @@ rc('axes', prop_cycle=(
 ))
 
 
-# n_core = 32
-n_core = 6
+# n_core = 6
+n_core = 16
 n_thread = n_core * 2
 backend = ' --openmp '
 
@@ -448,6 +448,275 @@ class ParticleDispersion3D(Problem):
                     shutil.copy(os.path.join(source, file_name), target_dir)
 
 
+class Wu2014FallingSolid3D(Problem):
+    """We will allow a circular particle to settle in a tank with different
+    viscosity coefficients and check the deviatioinn in the settling time
+    """
+    def get_name(self):
+        return 'wu_2014_falling_solid_3d'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/wu_2014_falling_solid_3d.py' + backend
+
+        # kinetic viscosity
+        # Base case info
+        self.case_info = {
+            'N_8': (dict(
+                N=8,
+                nu=1e-6,
+                ), 'N=8'),
+
+            'N_10': (dict(
+                N=10,
+                nu=1e-6,
+                ), 'N=10'),
+
+            'N_12': (dict(
+                N=12,
+                nu=1e-6,
+                ), 'N=12'),
+        }
+
+        self.cases = [
+            Simulation(get_path(name), cmd,
+                       job_info=dict(n_core=n_core,
+                                     n_thread=n_thread), cache_nnps=None,
+                       **scheme_opts(self.case_info[name][0]))
+            for name in self.case_info
+        ]
+
+    def run(self):
+        self.make_output_dir()
+        self.move_figures()
+        self.plot_displacement()
+
+    def plot_displacement(self):
+        data = {}
+        for name in self.case_info:
+            data[name] = np.load(self.input_path(name, 'results.npz'))
+
+        rand_case = (list(data.keys())[0])
+
+        t_exp = data[rand_case]['t_exp']
+        z_position_exp = data[rand_case]['z_position_exp']
+
+        # ==================================
+        # Plot x amplitude
+        # ==================================
+        plt.plot(t_exp, z_position_exp, "o", label='Experiment')
+        for name in self.case_info:
+            t_current = data[name]['t_current']
+            z_current = data[name]['z_position_current']
+
+            plt.plot(t_current, z_current, label=self.case_info[name][1])
+
+        plt.xlabel('time')
+        plt.ylabel('z - amplitude')
+        plt.legend()
+        # plt.tight_layout(pad=0)
[…]

### 2024-04-27 code/dinesh_2024_mixing_with_stirrer_2d.py

@@ -85,7 +85,7 @@ class MakeForcesZeroOnRigidBody(Equation):
 class Problem(Application):
     def add_user_options(self, group):
         group.add_argument("--fluid-length-ratio", action="store", type=float,
-                           dest="fluid_length_ratio", default=40,
+                           dest="fluid_length_ratio", default=20,
                            help="Ratio between the fluid length and rigid body diameter")
 
         group.add_argument("--fluid-height-ratio", action="store", type=float,
@@ -97,7 +97,7 @@ class Problem(Application):
                            help="Ratio between the tank length and fluid length")
 
         group.add_argument("--tank-height-ratio", action="store", type=float,
-                           dest="tank_height_ratio", default=4.,
+                           dest="tank_height_ratio", default=3.,
                            help="Ratio between the tank height and fluid height")
 
         group.add_argument("--N", action="store", type=int, dest="N",
@@ -111,6 +111,10 @@ class Problem(Application):
         group.add_argument("--rigid-body-diameter", action="store", type=float,
                            dest="rigid_body_diameter", default=1e-3,
                            help="Diameter of each particle")
+
+        group.add_argument("--stirrer-velocity", action="store", type=float,
+                           dest="stirrer_velocity", default=3,
+                           help="Stirrer velocity")
 
         add_bool_argument(
             group,
@@ -139,7 +143,7 @@ class Problem(Application):
         self.rigid_body_diameter = 0.11
         self.rigid_body_velocity = 0.
         self.no_of_layers = self.options.no_of_layers
-        self.no_of_bodies = 3 * 6 * self.options.no_of_layers
+        self.no_of_bodies = 18 * 2
 
         # x - axis
         self.fluid_length = self.options.fluid_length_ratio * self.rigid_body_diameter
@@ -158,12 +162,14 @@ class Problem(Application):
         self.tank_layers = 3
 
         # x - axis
-        self.stirrer_length = self.fluid_length * 0.1
+        self.stirrer_length = self.rigid_body_diameter
         # y - axis
         self.stirrer_height = self.fluid_height * 0.5
         # z - axis
         self.stirrer_depth = self.fluid_depth * 0.5
[…]

### 2024-04-27 code/hashemi_2012_dkt.py

@@ -9,16 +9,9 @@ python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1
 
 TODO:
 
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
+1. Close the tank
+2. Remove the stirrer
+3. Get the dimentions of the tank right
 """
 import numpy as np
 import sys
@@ -101,7 +94,7 @@ class Problem(Application):
                            help="Ratio between the tank height and fluid height")
 
         group.add_argument("--N", action="store", type=int, dest="N",
-                           default=6,
+                           default=12,
                            help="Number of particles in diamter of a rigid cylinder")
 
         group.add_argument("--rigid-body-rho", action="store", type=float,
@@ -136,15 +129,15 @@ class Problem(Application):
         # ======================
         # dimensions rigid body dimensions
         # All the particles are in circular or spherical shape
-        self.rigid_body_diameter = 0.11
+        self.rigid_body_diameter = 0.00125 * 2.
         self.rigid_body_velocity = 0.
         self.no_of_layers = self.options.no_of_layers
         self.no_of_bodies = 3 * 6 * self.options.no_of_layers
 
         # x - axis
-        self.fluid_length = self.options.fluid_length_ratio * self.rigid_body_diameter
+        self.fluid_length = 0.02
         # y - axis
-        self.fluid_height = self.options.fluid_height_ratio * self.rigid_body_diameter
+        self.fluid_height = 0.06
         # z - axis
         self.fluid_depth = 0.
 
@@ -193,12 +186,15 @@ class Problem(Application):
         self.hdx = 1.
         self.N = self.options.N
         self.dx = self.rigid_body_diameter / self.N
+        print("With N", self.N, "the dx value is", self.dx)
+        print("With delta as in hashemi 2012 paper", 1 / 10000., "the dx value is same.")
+        print("With delta as in hashemi 2012 paper", 1 / 15000., "the dx value is same.")
         self.h = self.hdx * self.dx
[…]

### 2024-04-27 code/hashemi_2012_falling_of_circular_cylinder_in_a_closed_channel.py

@@ -9,16 +9,9 @@ python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1
 
 TODO:
 
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
+1. Close the tank
+2. Remove the stirrer
+3. Get the dimentions of the tank right
 """
 import numpy as np
 import sys
@@ -101,7 +94,7 @@ class Problem(Application):
                            help="Ratio between the tank height and fluid height")
 
         group.add_argument("--N", action="store", type=int, dest="N",
-                           default=6,
+                           default=12,
                            help="Number of particles in diamter of a rigid cylinder")
 
         group.add_argument("--rigid-body-rho", action="store", type=float,
@@ -136,15 +129,16 @@ class Problem(Application):
         # ======================
         # dimensions rigid body dimensions
         # All the particles are in circular or spherical shape
-        self.rigid_body_diameter = 0.11
+        self.rigid_body_diameter = 0.00125
         self.rigid_body_velocity = 0.
         self.no_of_layers = self.options.no_of_layers
         self.no_of_bodies = 3 * 6 * self.options.no_of_layers
 
         # x - axis
-        self.fluid_length = self.options.fluid_length_ratio * self.rigid_body_diameter
+        self.fluid_length = 0.02
+        self.fluid_length = 0.01
         # y - axis
-        self.fluid_height = self.options.fluid_height_ratio * self.rigid_body_diameter
+        self.fluid_height = 0.06
         # z - axis
         self.fluid_depth = 0.
 
@@ -193,12 +187,16 @@ class Problem(Application):
         self.hdx = 1.
         self.N = self.options.N
         self.dx = self.rigid_body_diameter / self.N
+        print("With N", self.N, "the dx value is", self.dx)
+        print("With delta as in hashemi 2012 paper 1 / 6000.", 1 / 6000., "the dx value is same.")
+        print("With delta as in hashemi 2012 paper 1 / 10000.", 1 / 10000., "the dx value is same.")
[…]

### 2024-04-27 code/hashemi_2012_neutrally_buoyant_circular_cylinder_in_shear_flow.py

@@ -1,0 +1,583 @@
+"""A neutrally buoyand circular cylinder in a shear flow
+
+Section 7.1 in Hashemi 2012 paper
+
+python hashemi_2012_neutrally_buoyant_circular_cylinder_in_shear_flow.py --openmp --no-use-edac --nu 1e-6 --alpha 0.02 --artificial-viscosity-with-boundary --pfreq 300 --internal-flow --pst
+
+"""
+import os
+
+# numpy
+import numpy as np
+
+# PySPH imports
+from pysph.base.nnps import DomainManager
+from pysph.base.utils import get_particle_array
+from pysph.solver.application import Application
+from pysph.solver.utils import load
+import pysph.tools.geometry as G
+import sys
+sys.path.insert(0, "./../")
+from pysph_rfc_new.fluids import (get_particle_array_fluid, get_particle_array_boundary)
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Group, MultiStageEquations
+
+from pysph.sph.equation import Equation, Group
+from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, translate_system_with_left_corner_as_origin
+
+from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
+                                              set_linear_velocity,
+                                              set_angular_velocity,
+                                              get_master_and_slave_rb,
+                                              add_contact_properties_body_master)
+
+from sph_dem.rigid_fluid_coupling import (
+    ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
+from pysph_dem.dem_simple import (setup_wall_dem)
+
+
+def check_time_make_zero(t, dt):
+    if t < 5.0:
+        return True
+    else:
+        return False
+
+
+def get_center_of_mass(x, y, z, m):
+    # loop over all the bodies
+    xcm = [0., 0., 0.]
+    total_mass = np.sum(m)
+    xcm[0] = np.sum(m[:] * x[:]) / total_mass
+    xcm[1] = np.sum(m[:] * y[:]) / total_mass
+    xcm[2] = np.sum(m[:] * z[:]) / total_mass
+    return xcm
+
+
+def move_body_to_new_center(xcm, x, y, z, center):
+    x_trans = center[0] - xcm[0]
+    y_trans = center[1] - xcm[1]
[…]

### 2024-04-27 code/single_particle_dispersion_cylindrical_tank_3d.py

@@ -2,29 +2,14 @@
 
 Run it using:
 
-python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme combined -d rb_falling_in_hs_tank_combined_output
-
-python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme master -d rb_falling_in_hs_tank_master_output
 
 
-TODO:
-
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
 """
 import numpy as np
 import sys
 
 from pysph.examples import dam_break_2d as DB
-from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.tools.geometry import (get_2d_tank, get_2d_block, get_3d_block)
 from pysph.tools.geometry import get_3d_sphere
 import pysph.tools.geometry as G
 from pysph.base.utils import get_particle_array
@@ -48,6 +33,7 @@ from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, transla
 
 from sph_dem.rigid_fluid_coupling import (
     ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
+from sph_dem.geometry import (get_cylindrical_fluid_tank_3d)
 
 from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
                                               set_linear_velocity,
@@ -85,11 +71,11 @@ class MakeForcesZeroOnRigidBody(Equation):
 class Problem(Application):
     def add_user_options(self, group):
         group.add_argument("--fluid-length-ratio", action="store", type=float,
-                           dest="fluid_length_ratio", default=40,
+                           dest="fluid_length_ratio", default=8,
                            help="Ratio between the fluid length and rigid body diameter")
 
[…]

### 2024-04-27 code/test_01_rfc_single_particle_settling_2d.py

@@ -9,16 +9,9 @@ python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1
 
 TODO:
 
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
+1. Close the tank
+2. Remove the stirrer
+3. Get the dimentions of the tank right
 """
 import numpy as np
 import sys
@@ -101,7 +94,7 @@ class Problem(Application):
                            help="Ratio between the tank height and fluid height")
 
         group.add_argument("--N", action="store", type=int, dest="N",
-                           default=6,
+                           default=8,
                            help="Number of particles in diamter of a rigid cylinder")
 
         group.add_argument("--rigid-body-rho", action="store", type=float,
@@ -136,15 +129,15 @@ class Problem(Application):
         # ======================
         # dimensions rigid body dimensions
         # All the particles are in circular or spherical shape
-        self.rigid_body_diameter = 0.11
+        self.rigid_body_diameter = 0.125
         self.rigid_body_velocity = 0.
         self.no_of_layers = self.options.no_of_layers
         self.no_of_bodies = 3 * 6 * self.options.no_of_layers
 
         # x - axis
-        self.fluid_length = self.options.fluid_length_ratio * self.rigid_body_diameter
+        self.fluid_length = 5 * self.rigid_body_diameter
         # y - axis
-        self.fluid_height = self.options.fluid_height_ratio * self.rigid_body_diameter
+        self.fluid_height = 20. * self.rigid_body_diameter
         # z - axis
         self.fluid_depth = 0.
 
@@ -193,12 +186,16 @@ class Problem(Application):
         self.hdx = 1.
         self.N = self.options.N
         self.dx = self.rigid_body_diameter / self.N
+        print("With N", self.N, "the dx value is", self.dx)
+        print("With delta as in hashemi 2012 paper 1 / 6000.", 1 / 6000., "the dx value is same.")
+        print("With delta as in hashemi 2012 paper 1 / 10000.", 1 / 10000., "the dx value is same.")
[…]

### 2024-04-27 code/wu_2014_falling_solid_2d.py

@@ -9,16 +9,9 @@ python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1
 
 TODO:
 
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
+1. Close the tank
+2. Remove the stirrer
+3. Get the dimentions of the tank right
 """
 import numpy as np
 import sys
@@ -47,7 +40,7 @@ from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, transla
 # from geometry import hydrostatic_tank_2d, create_circle_1
 
 from sph_dem.rigid_fluid_coupling import (
-    ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
+    ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body, RBStirrerForce)
 
 from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
                                               set_linear_velocity,
@@ -82,6 +75,52 @@ class MakeForcesZeroOnRigidBody(Equation):
         trq[:] = 0
 
 
+class RBTankForce(Equation):
+    def __init__(self, dest, sources, kn, en, fric_coeff):
+        self.kn = kn
+        self.en = en
+        self.fric_coeff = fric_coeff
+        super(RBTankForce, self).__init__(dest, sources)
+
+    def loop(self, d_idx, d_fx, d_fy, d_fz, d_h, d_total_mass, d_rad_s,
+             s_idx, s_rad_s, d_dem_id, s_dem_id,
+             d_nu, s_nu, d_E, s_E, d_G, s_G,
+             d_m, s_m,
+             d_body_id,
+             XIJ, RIJ, R2IJ, VIJ):
+        overlap = 0
+        if RIJ > 1e-9:
+            overlap = d_rad_s[d_idx] + s_rad_s[s_idx] - RIJ
+
+        if overlap > 1e-12:
+            # normal vector passing from particle i to j
+            nij_x = -XIJ[0] / RIJ
+            nij_y = -XIJ[1] / RIJ
+            nij_z = -XIJ[2] / RIJ
+
+            # overlap speed: a scalar
[…]

### 2024-04-27 code/wu_2014_falling_solid_3d.py

@@ -1,33 +1,21 @@
-"""Rigid body falling in tank but 2D
+"""
+Numerical modeling of floating bodies transport for flooding analysis in nuclear
+reactor building
 
-Run it using:
+3.1. Validation of the PMS model for solid-fluid interaction
 
-python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme combined -d rb_falling_in_hs_tank_combined_output
+https://www.sciencedirect.com/science/article/pii/S0029549318307350#b0140
 
-python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme master -d rb_falling_in_hs_tank_master_output
-
-
-TODO:
-
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
 """
 import numpy as np
 import sys
 
 from pysph.examples import dam_break_2d as DB
-from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.tools.geometry import (get_2d_tank, get_2d_block, get_3d_block)
 from pysph.tools.geometry import get_3d_sphere
 import pysph.tools.geometry as G
 from pysph.base.utils import get_particle_array
+from pysph.examples.solid_mech.impact import add_properties
 
 from pysph.examples import cavity as LDC
 from pysph.sph.equation import Equation, Group
@@ -48,6 +36,7 @@ from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, transla
 
 from sph_dem.rigid_fluid_coupling import (
     ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
+from sph_dem.geometry import (get_fluid_tank_new_rfc_3d, get_3d_block_rfc)
 
[…]

### 2024-04-27 code/wu_2014_floating_solid_2d.py

@@ -9,16 +9,9 @@ python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1
 
 TODO:
 
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
+1. Close the tank
+2. Remove the stirrer
+3. Get the dimentions of the tank right
 """
 import numpy as np
 import sys
@@ -47,7 +40,7 @@ from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, transla
 # from geometry import hydrostatic_tank_2d, create_circle_1
 
 from sph_dem.rigid_fluid_coupling import (
-    ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
+    ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body, RBStirrerForce)
 
 from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
                                               set_linear_velocity,
@@ -82,6 +75,52 @@ class MakeForcesZeroOnRigidBody(Equation):
         trq[:] = 0
 
 
+class RBTankForce(Equation):
+    def __init__(self, dest, sources, kn, en, fric_coeff):
+        self.kn = kn
+        self.en = en
+        self.fric_coeff = fric_coeff
+        super(RBTankForce, self).__init__(dest, sources)
+
+    def loop(self, d_idx, d_fx, d_fy, d_fz, d_h, d_total_mass, d_rad_s,
+             s_idx, s_rad_s, d_dem_id, s_dem_id,
+             d_nu, s_nu, d_E, s_E, d_G, s_G,
+             d_m, s_m,
+             d_body_id,
+             XIJ, RIJ, R2IJ, VIJ):
+        overlap = 0
+        if RIJ > 1e-9:
+            overlap = d_rad_s[d_idx] + s_rad_s[s_idx] - RIJ
+
+        if overlap > 1e-12:
+            # normal vector passing from particle i to j
+            nij_x = -XIJ[0] / RIJ
+            nij_y = -XIJ[1] / RIJ
+            nij_z = -XIJ[2] / RIJ
+
+            # overlap speed: a scalar
[…]

### 2024-04-27 code/wu_2014_floating_solid_3d.py

@@ -1,30 +1,17 @@
-"""Rigid body falling in tank but 2D
+"""
+Numerical modeling of floating bodies transport for flooding analysis in nuclear
+reactor building
 
-Run it using:
+3.1. Validation of the PMS model for solid-fluid interaction
 
-python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme combined -d rb_falling_in_hs_tank_combined_output
+https://www.sciencedirect.com/science/article/pii/S0029549318307350#b0140
 
-python rb_falling_in_hs_tank.py --openmp --pfreq 100 --timestep 1e-4 --alpha 0.1 --fric-coeff 0.05 --en 0.05 --N 5 --no-of-bodies 1 --fluid-length-ratio 5 --fluid-height-ratio 10 --rigid-body-rho 2000 --tf 3 --scheme master -d rb_falling_in_hs_tank_master_output
-
-
-TODO:
-
-1. Create many particles
-2. Run it on HPC
-3. Change the speed
-4. Change the dimensions
-5. Commit SPH-DEM and current repository
-6. Validate 1 spherical particle settled in hs tank
-7. Validate 2 spherical particles settled in hs tank
-8. Complete the manuscript
-9. Different particle diameter
-10. Different density
 """
 import numpy as np
 import sys
 
 from pysph.examples import dam_break_2d as DB
-from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.tools.geometry import (get_2d_tank, get_2d_block, get_3d_block)
 from pysph.tools.geometry import get_3d_sphere
 import pysph.tools.geometry as G
 from pysph.base.utils import get_particle_array
@@ -48,6 +35,7 @@ from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, transla
 
 from sph_dem.rigid_fluid_coupling import (
     ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
+from sph_dem.geometry import (get_fluid_tank_new_rfc_3d, get_3d_block_rfc)
 
 from sph_dem.rigid_body.rigid_body_3d import (setup_rigid_body,
                                               set_linear_velocity,
[…]

### 2024-04-27 code/zhang_2009_solid_fluid_mixture_verification_2d.py

@@ -45,6 +45,7 @@ from pysph_dem.rigid_body.boundary_particles import (add_boundary_identification
                                 get_boundary_identification_etvf_equations)
 from pysph_rfc_new.geometry import hydrostatic_tank_2d, create_circle_1, translate_system_with_left_corner_as_origin
 # from geometry import hydrostatic_tank_2d, create_circle_1
+from sph_dem.geometry import (create_tank_2d_from_block_2d)
 
 from sph_dem.rigid_fluid_coupling import (
     ParticlesFluidScheme, add_rigid_fluid_properties_to_rigid_body)
@@ -80,6 +81,27 @@ class MakeForcesZeroOnRigidBody(Equation):
 
         frc[:] = 0
         trq[:] = 0
+
+
+def get_files_at_given_times_from_log(files, times, logfile):
+    import re
+    result = []
+    time_pattern = r"output at time\ (\d+(?:\.\d+)?)"
+    file_count, time_count = 0, 0
+    with open(logfile, 'r') as f:
+        for line in f:
+            if time_count >= len(times):
+                break
+            t = re.findall(time_pattern, line)
+            if t:
+                if float(t[0]) in times:
+                    result.append(files[file_count])
+                    time_count += 1
+                elif float(t[0]) > times[time_count]:
+                    result.append(files[file_count])
+                    time_count += 1
+                file_count += 1
+    return result
 
 
 class Problem(Application):
@@ -136,22 +158,22 @@ class Problem(Application):
         # ======================
         # dimensions rigid body dimensions
         # All the particles are in circular or spherical shape
-        self.rigid_body_diameter = 0.11
+        self.rigid_body_diameter = 1. * 1e-2
         self.rigid_body_velocity = 0.
         self.no_of_layers = self.options.no_of_layers
         self.no_of_bodies = 3 * 6 * self.options.no_of_layers
 
         # x - axis
-        self.fluid_length = self.options.fluid_length_ratio * self.rigid_body_diameter
+        self.fluid_length = 7.1 * 1e-2
         # y - axis
-        self.fluid_height = self.options.fluid_height_ratio * self.rigid_body_diameter
+        self.fluid_height = 12.1 * 1e-2
         # z - axis
[…]

### 2024-05-30 manuscript/paper.tex
Correct the draft

@@
 \documentclass[preprint,12pt]{elsarticle}
+% \documentclass[preprint,12pt,draft]{elsarticle}
 % \documentclass[draft,12pt]{elsarticle}
@@
 
-  \title{Study of mixing behaviour of spherical particles in fluid using stirrer}
-  \author[XXX]{Dinesh Adepu\corref{cor1}}
+  \title{{DEM}-{SPH} study of particles dispersion in fluid}
+  \author[xxx]{Dinesh Adepu\corref{cor1}}
   \ead{d.dinesh@surrey.ac.uk}
-  \author[University of Surrey]{Chuan Yu Wu}
-  \ead{XXX}
-\address[xxx]{xxx}
+  \author[xxx]{Chuan Yu Wu}
+  % \ead{XXX}
+\address[xxx]{School of Chemistry and Chemical Engineering, University of Surrey}
 
@@
 \begin{abstract}
-
+  Mixing powdered substances in tanks using a stirrer is a common occurrence
+  across various industries. Typically, this phenomenon is studied numerically
+  due to the complex nonlinear physics involved. In our current study, we have
+  developed a solver combining Smoothed Particle Hydrodynamics (SPH) and
+  Discrete Element Method (DEM) to investigate the mixing behavior of rigid
+  circular particles within a tank under the influence of a stirrer operating
+  at different speeds.  The SPH method governs the fluid phase, while the
+  dynamics and interactions of particles are captured by the DEM. We achieve a
+  fully resolved coupling between solid particles and fluid particles by
+  discretizing solid particles into dummy SPH particles. Our validation
+  process includes verifying the fluid solver's accuracy through a Poiseuille
+  problem and validating the DEM solver by benchmarking interactions between
+  two particles and particle-wall impacts.  The coupled model's is validated
+  by simulating single-particle entry in a 2D steady tank and a cube settling
+  in a tank, which is a 3D case. Following validation, we proceed with the
+  mixing study. We conduct two simulations: one with spherical particles of
+  uniform radius and another with particles having two different radius.  Our
+  findings reveal that as for lower stirrer speeds, particles tend to
+  aggregate initially and remain in the center. However, with further increase
+  in stirrer speed, particles tend to accumulate near the tank corners due to
+  the circulation induced in the fluid due to the stirrer motion. We use an
+  open-source software, PySPH, adapting and integrating the coupled model to
+  conduct the current study.
 \end{abstract}
@@
 various industries where powder and fluid interactions are pivotal.  Petroleum
-industry \cite{wang2023developments}, The transport of bodies in internal
+industry \cite{wang2023developments}, the transport of bodies in internal
 systems \cite{Dai2021}, debris flow \cite{Qingyun2022}, the food processing
 industry \cite{Karunasena2014}, and ice-sea modeling \cite{Mintu2018} are a
-few areas to mention.  Particularly, processes involving the mixing of powder
-with fluid using a stirrer are commonplace \cite{li2022study}. While
-experimental investigation of such processes is often impractical due to their
-highly nonlinear nature, numerical methods offer a viable alternative. These
-systems are studied as part of two-way coupling models. The two-way coupling
-phenomena are nonlinear, and an analytical study is not feasible. A numerical
-study is preferable while handling such a phenomenon. A mesh-based or meshless
-technique can be utilized to study rigid fluid coupling (RFC) numerically.
-\Cref{fig:gloabl_body_frame_rb} illustrates a sample particle dispersion
-problem studied in the current work.
+few areas to mention.  In many processes the mixing of powder with fluid using
+a stirrer are commonplace \cite{li2022study}.  \Cref{fig:gloabl_body_frame_rb}
+illustrates a sample particle dispersion problem studied in the current work.
+While experimental investigation of such processes is often impractical due to
+their highly nonlinear nature, numerical methods offer a viable alternative.
+While these systems are studied with numerical methods, they are a part of
+two-way coupling models. In numerical method approach, one can employ either a
+mesh-based or meshless technique to study the current phenomena.
+
 \begin{figure}[!htpb]
@@
 is a classic approach in handling particulate flow problem. In
-mesh-based CFD-DEM modeling, lattice Boltzmann method (LBM)
+mesh-based modeling, lattice Boltzmann method (LBM)
 \cite{xiong2014lbm} and finite volume method (FVM) \cite{kloss2012models} are
@@
 Method (PFEM) \cite{li2019modeling, franci2020pfem}, handles the fluid
-dynamics.  While handling the interaction between the fluid and solid
-particles, the interaction can be categorized into a resolved and unresolved
-coupling. In unresolved coupling, simplified models compute forces acting on
-solid particles within fluid flow, while fully resolved coupling computes
-forces comprehensively. Both strategies are applicable in both meshless
-\cite{cleary2015prediction, trujillo2020smooth} and mesh-based
-\cite{van2008numerical, ma2022review} CFD-DEM techniques. Research such as
+dynamics.
+
+While handling the interaction between the fluid and solid particles, the
+interaction can be categorized into a resolved and unresolved coupling.  In
+unresolved coupling, simplified models are utilized to calculate the forces
+exerted on solid particles within the fluid flow. In contrast, in the fully
+resolved coupling approach, the fluid forces are directly computed on the
+solid particles without the need for empirical drag force models.  Both
+strategies are applicable in both meshless \cite{cleary2015prediction,
+  trujillo2020smooth} and mesh-based \cite{van2008numerical, ma2022review}
+CFD-DEM techniques.  In addition to the study mono-sized particle behaviour in
+a fluid \cite{trujillo2020smooth}, research such as
 \cite{brosh2014accelerating} and \cite{peng2021fully} explore wide particle
 size distributions with CFD-DEM and SPH-DEM respectively.  Regarding
-non-Newtonian fluid modeling in mesh-based schemes, works like
+non-Newtonian fluid modelling in mesh-based schemes, works like
 \cite{li2018dam} are notable and in meshless schemes, \cite{peng2021fully} is
-notable. \citet{zhu2008discrete} and \citet{ma2022review}
-delve into investigations on spherical and non-spherical particles
-respectively within CFD-DEM frameworks.  Meshless CFD-DEM, though fruitful,
-encounters challenges in handling problems with free surfaces and becomes
-computationally demanding with a large number of solid particles, especially
-in fully resolved coupling. In contrast, SPH offers advantages in such
-scenarios due to its inherent capability in handling free surfaces and
-adeptness in modeling large mesh deformation problems, facilitating the
-incorporation of novel physics.
+notable. \citet{zhu2008discrete} and \citet{ma2022review} delve into
+investigations on spherical and non-spherical particles respectively within
+CFD-DEM frameworks.  Meshless CFD-DEM, though fruitful, encounters challenges
+in handling problems with free surfaces and becomes computationally demanding
+with a large number of solid particles, especially in fully resolved
+coupling. In contrast, SPH offers advantages in such scenarios due to its
+inherent capability in handling free surfaces and adeptness in modeling large
+mesh deformation problems, facilitating the incorporation of novel physics.
 
@@
 simple spherical particles mixing using unresolved coupling
-\cite{cleary2015prediction, markauskas2019coupled} and with debris
-flow \cite{canelas2016sph} with fully resolved coupling approach has been
-solved using SPH-DEM framework.  Handling particles of arbitrary shape in
-fluid flow is addressed in various works, including those by
-\citet{peng2021fully, canelas2016sph, amicarelli2015smoothed}.  Several
-variants of SPH, such as WCSPH \cite{peng2021fully, cleary2015}, and ISPH
+\cite{cleary2015prediction, markauskas2019coupled} and with debris flow
+\cite{canelas2016sph} with fully resolved coupling approach were analysed
+using SPH-DEM.  Handling particles of arbitrary shape in fluid flow is
+addressed in various works, including those by \citet{peng2021fully,
+  canelas2016sph, amicarelli2015smoothed}.  Several variants of SPH, such as
+WCSPH \cite{peng2021fully, cleary2015prediction}, and ISPH
 \cite{asai2021fluid}, are utilized for modeling fluid flow with particulate
@@
 \cite{monaghan2009sph}. Coupling between SPH fluid particles and solid
-structures discretized as vertex edges is proposed by
-\cite{park2023new}. Particle settling with variable sizes is studied by
+structures discretized as vertex edges is also proposed by
+\citet{park2023new}. Particle settling with variable sizes is studied by
 \citet{zou2022study}.  Elastic behavior of spherical particles and dispersion
@@
 bodies of arbitrary sizes is addressed using various techniques, such as those
-discussed in papers by \citet{asai2021fluid}, citet{peng2021fully},
+discussed in papers by \citet{asai2021fluid}, \citet{peng2021fully},
 \citet{canelas2016sph}.
 
-In the current work we cosider the particle dispersion within a large-scale
+In the current work we consider the particle dispersion within a large-scale
 under stirrer mixing phenomenon. We employ Smoothed Particle Hydrodynamics
@@
 the dynamics and contact interactions among spherical particles. The
-interaction between solids and fluids is managed using a fixed ghost particle
+interaction between solids and fluids is modelled using a fixed ghost particle
 approach, ensuring a fully resolved simulation. We validate the fluid solver
@@
 fidelity of the solver, we proceed with analyzing the mixing behavior of
-various spherical particles influenced by a stirrer in a water tank. We
-investigate scenarios involving particles of different densities, stirrer
-velocities, and variable sizes as part of our case study. The development work
-is conducted using PySPH\cite{ramachandran2021pysph}, an open-source code
-available at \url{https://github.com/pypr/pysph} . To ensure reproducibility,
-we utilize the automan package \cite{ramachandran2018automan} to automate all
-results generated in the current manuscript, aiming for a reproducible
-research approach.
+various spherical particles influenced by a stirrer in a tank. We investigate
+scenarios involving particles of different densities, stirrer velocities, and
+variable sizes as part of our case study. The development work is conducted
+using PySPH\cite{ramachandran2021pysph}, an open-source code available at
+\url{https://github.com/pypr/pysph}.  We modify the current codebase to
+integrate implementations of the Discrete Element Method (DEM) and the
+Smoothed Particle Hydrodynamics (SPH) coupled with DEM model for our ongoing
+research. To ensure reproducibility, we utilize the automan package
+\cite{ramachandran2018automan} to automate all results generated in the
+current manuscript, aiming for a reproducible research approach.
 
@@
 In the current work, we follow a weakly-compressible SPH approach to model the
-fluid. Smoothed particle hydrodynamics is initially developed by Lucy
-\cite{lucy1977numerical} and Gingold and Monaghan \cite{gingold1977smoothed}
-to model astrophysical problems. The continuum in SPH is modeled using
-particles, which has physical properties such as mass, velocity, and the
-particles interact based on the governing equations using a Guassian-like
-kernel \cite{SPH_papers}.
+fluid. The continuum in SPH is modeled using particles, which has physical
+properties such as mass, velocity, and these particles interact based on the
+governing equations using a Guassian-like kernel
+\cite{monaghan-review:2005,morris1997modeling}.
 
@@
 \label{sec:fluid--governing-equations}
-Equations governing the fluid motion are, conservation of mass
+The fluid motion is governed by the conservation of mass and the conservation
+of linear momentum, which can be expressed by the following equations:
 \begin{equation}
@@
 \end{equation}
-and conservation of linear momentum,
 \begin{equation}
@@
 
-The stress tensor is split into a pressure and viscous parts,
+The stress tensor is split into pressure and viscous parts,
 \begin{equation}
@@
 domain is discretized into N particles with mass $m_i$ and volume
-$\Delta v_i$, We have
+$V_i$, We have
 \begin{equation}
   \label{eq:mass_repr}
-  m_j = \Delta v_i \> \rho_i.
+  m_i = V_i \> \rho_i.
 \end{equation}
@@
 The SPH discretization of the continuity
-equation~\cref{eq:sph-discretization-continuity} and the momentum equation
-~\cref{eq:sph-momentum-fluid} respectively are,
+equation~\cref{eq:sph-discretization-continuity} is given as,
 \begin{equation}
@@
 %
-Similarly, the discretized momentum equation for fluids is written as,
+Similarly, the discretized momentum equation is written as,
 \begin{multline}
@@
 where $\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
-fluid and \cite{morris1997modeling} formulation is used to discretize the
-viscosity term.
+fluid. The viscous term in \Cref{eq:me} is discretized according to the
+formulation introduced in \cite{morris1997modeling}.
 
@@
 
-The ghost particle approach of \cite{Adami2012} is used to model the
+The ghost particle approach proposed by \citet{Adami2012} is used to model the
 boundaries. We use three layers of ghost particles to model the solid wall.
@@
 \end{equation}
-where $\ten{u}_b$, is the momentum velocity
-of the fluid and $W_{ab}$ is the kernel value between the fluid
-particle and the ghost particle.
+where $\ten{u}_b$, is the velocity of the fluid particle $b$ and $W_{ab}$ is the kernel
+value between the fluid particle and the ghost particle.
 
@@
 \FloatBarrier%
-\subsection{Contact resolution}
+\subsection{Contact models}
 \label{sec:dem}
@@
 
-We resolve the contact among the spherical particles using discrete element
-method. In the current work we have utilized a non-linear contact force
-model. In DEM, the force acting on a particle $a$ due to the interaction with
-the particle $b$ is resolved into a normal and tangential component. The
-normal force component is utilised to make sure that the particle do not
-penetrate into each other, while the tangential component is used to model the
-friction between the interacting particles.  The normal force
-($\teng{F}_a^{n}$) on particle $a$ due to the interaction with the particles
-$b$ is given by a non-linear, Hetzian model \citet{brilliantov1996model},
+We resolve the contact among the spherical particles using the discrete
+element method \cite{luding_dem_2008}. In the current work we have utilized a
+non-linear contact force model. In DEM, the force acting on a particle $a$ due
+to the interaction with the particle $b$ is resolved into a normal and
+tangential component. The normal force component represents a repulsive force,
+while the tangential component is used to model the friction between the
+interacting particles.  The normal force ($\teng{F}_a^{n}$) on particle $a$
+due to the interaction with the particles $b$ is given by a non-linear,
+Hetzian model \cite{brilliantov1996model}, including damping is given as,
 \begin{equation}
   \label{eq:contact-algorithm-normal}
-  \ten{F}_a^n = k_r \delta_{n} \ten{n}.
-\end{equation}
-Here, the overlap $\delta_{n}$ is computed using
+  \ten{F}_a^n = k_n \delta_{n} \ten{n} - \eta_n (\ten{v}_{ab} \cdot \ten{n}) \ten{n}.
+\end{equation}
+Here, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is the relative velocity of
+particle $a$ with respect to the contacting particle $b$,
+$\ten{n}$ normal unit vector passing from particle $b$ to $a$, and the overlap $\delta_{n}$ is computed
+using the radius of particle $a$ ($R_a$) and particle $b$ ($R_b$) as
 \begin{equation}
@@
 \end{equation}
-$k_r$ is the normal spring stiffness coefficient, which is computed using the
-material properties of the bodies in contact \cite{golshan2023lethe}.
+$k_n$ and $\eta_n$ are the normal spring stiffness and damping coefficient, which
+are computed using the material properties of the bodies in contact and the
+coefficient of restitution among the interacting bodies, given by:
+\begin{equation}
+  \label{eq:kf-stiffness}
+  k_n = \frac{4}{3} \; E^{*} \; \sqrt{R^{*} \delta_n},
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \eta_n = -2 \sqrt{\frac{5}{6}} \beta \; \sqrt{S_n m^*}.
+\end{equation}
+Where the other parameters are given as:
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \frac{1}{E^{*}} = \frac{1 -\nu_a^2}{E_a} + \frac{1 -\nu_b^2}{E_b}
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \beta = \frac{\ln{e}}{\ln{e}^2 + \pi},
+\end{equation}
+here, $e$ is the coefficient of restitution.
+\begin{equation}
+  \label{eq:kf-stiffness}
+  R^{*} = \frac{R_a R_b}{R_a + R_b}
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  m^{*} = \frac{m_a m_b}{m_a + m_b}
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  S_n = 2 E^{*} \sqrt{R^{*} \delta_n}
+\end{equation}
 
@@
 tangential force is history-dependent. The contact friction force is
-proportional to the tangential spring displacement, which is integrated over
+proportional to the tangential displacement, which is integrated over
 the contact time as
@@
   \ten{F}_{a}^{t^{n+1}} =
-  -k_f \Delta \textit{\textbf{l}}_a^{\,n + 1} =
-  -k_f \big[\big(\Delta {\textit{\textbf{l}}}_a^{\,n} \
+  -k_t \Delta \textit{\textbf{l}}_a^{\,n + 1} - \eta_t \ten{v}_t =
+  -k_t \big[\big(\Delta {\textit{\textbf{l}}}_a^{\,n} \
   + \ten{v}_{ab}^{n + 1} \Delta t\big) \cdot \ten{t}_a^{n + 1} \big] \
-  \ten{t}_a^{n + 1},
-\end{equation}
-where $\Delta t$ is the time step, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is the
-relative velocity of particle $a$ with respect to the contacting particle $b$,
-and $k_f$ is the tangential spring stiffness coefficient. The tangential
-spring stiffness is computed similar to the normal spring
-stiffness\cite{golshan2023lethe}.  The tangential unit vector is computed by,
+  \ten{t}_a^{n + 1} - \eta_t \ten{v}_t,
+\end{equation}
+where $\Delta t$ is the time step,
+and $k_t$ is the tangential spring stiffness coefficient. The tangential unit
+vector is computed by,
 \begin{equation}
@@
 \end{equation}
+The tangential spring stiffness ($k_t$) and the tangential damping coefficient
+$\eta_t$ are given as:
+\begin{equation}
+  \label{eq:kf-stiffness}
+  k_t = 8 \; G^{*} \; \sqrt{R^{*} \delta_n},
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \eta_t = -2 \sqrt{\frac{5}{6}} \beta \; \sqrt{S_t m^*},
+\end{equation}
+with $G^*$ and $S_t$ are given as,
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \frac{1}{G^{*}} = \frac{2 (2 - \nu_a) (1 + \nu_a)}{E_a} +  \frac{2 (2 - \nu_b) (1 + \nu_b)}{E_b},
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  S_t = 8 G^{*} \sqrt{R^{*} \delta_n},
+\end{equation}
+where, $G$ is the shear modulus of the particles, $\nu$ is the Poisson's ratio.
 
@@
   \end{subfigure}
-  \caption{}
+  \caption{A rigid particle being discretized into several dummy SPH
+    particles, to handle the interaction with surrounding fluid.}
 \label{fig:real_particle_sph_sampling}
 \end{figure}
-To calculate the force exerted on the spherical particle by the surrounding
+To calculate the force exerted on the rigid particle due to the surrounding
 fluid, we employ a method involving the sampling of the spherical particle
@@
 distributed and remain stationary, moving in tandem with the velocity of the
-rigid particle at any given location. To establish the pressure of these SPH
-particles, we utilize the fixed ghost particle boundary technique outlined in
-\cref{sec:boundary_conditions}.
-
-With spherical particles being discretized into SPH particles and immersed in
+rigid particle at any given location.  They serve as SPH boundary particles
+and contribute to the computation of fluid particle density and acceleration
+according to \Cref{eq:sph-discretization-continuity,eq:sph-momentum-fluid}.
+To establish the pressure of these SPH particles, we utilize the fixed ghost
+particle boundary technique outlined in \cref{sec:boundary_conditions}.
+
+With rigid particles being discretized into SPH particles and immersed in
 fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
@@
   \caption{A rigid spherical particle sampled with dummy SPH particles being
-    immersed in a fluid tank. An SPH particle representation}
+    immersed in a fluid tank. An SPH particle representation.}
   \label{fig:many_rb_in_fluid_sph_particles}
@@
   \ten{F}_{\text{rfc}}^a = -m_a \sum_{f} m_f \bigg(\frac{p_f}{\rho_{f}^2} +
-  \frac{p_a}{\rho_{a}^2}\bigg) \nabla_{a} W(x_{af}).
-\end{equation}
-Here, $m_a$ signifies the hydrodynamic mass of the sampled dummy SPH particle,
+  \frac{p_a}{\rho_{a}^2}\bigg) \nabla_{a} W(x_{af}) +
+  m_a \sum_{f} m_f \frac{4 \eta \nabla_a W_{af}\cdot
+    \ten{r}_{af}}{(\rho_a + \rho_f) (r_{af}^2 + 0.01 h_{af}^2)} \ten{u}_{af}
+\end{equation}
+where, $m_a$ signifies the hydrodynamic mass of the sampled dummy SPH particle,
 and $\rho_a$ represents its hydrodynamic density. While $m_f$, $p_f$ and
@@
 
-We use the kick-drift-kick scheme for the time integration. We move the
+We use the kick-drift-kick scheme \cite{monaghan-review:2005} for the time integration. We move the
 velocities of the fluid and the solid particles to half time step,
@@
   \label{eq:velocity-update-stage-1}
-  \ten{u}_a^{n+\frac{1}{2}} = \ten{u}_a^{n} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^n,
-\end{equation}
-Then the time derivative of density is calculated using the
-\cref{eq:sph-discretization-continuity} using the velocities at half time
-step. The new time step density and particle position is updated by,
+  \ten{u}_a^{t+\frac{1}{2} \Delta t} = \ten{u}_a^{t} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^t,
+\end{equation}
+here, $()_a^t$ represents the properties of particle $a$ at time $t$ and
+$()_a^{t+\frac{1}{2} \Delta t}$ corresponds to the halfway point between time
+$t$ and $t + \Delta t$. Then the time derivative of density is calculated using the
+\cref{eq:sph-discretization-continuity}, with velocities at half time step
+employed for the calculation.  The updated density and particle position for
+the new time step are determined by,
 \begin{equation}
   \label{eq:density-update-stage-2}
-  \rho_{a}^{n+1} = \rho_{a}^{n} + \Delta t \; \bigg(\frac{d\rho_{a}}{dt}\bigg)^{n+\frac{1}{2}},
+  \rho_{a}^{t+\Delta t} = \rho_{a}^{t} + \Delta t \; \bigg(\frac{d\rho_{a}}{dt}\bigg)^{t+\frac{1}{2} \Delta t},
 \end{equation}
@@
   \label{eq:position-update-stage-2}
-  \ten{r}_{a}^{n+1} = \ten{r}_{a}^{n} + \Delta t \; \ten{u}_{a}^{n+1}.
+  \ten{r}_{a}^{t+\Delta t} = \ten{r}_{a}^{t} + \Delta t \; \ten{u}_{a}^{t+\Delta t}.
 \end{equation}
@@
   \label{eq:velocity-update-stage-3}
-  \ten{u}_a^{n+1} = \ten{u}_a^{n+\frac{1}{2}} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^{n+1}.
-\end{equation}
-
-The modeling of rigid-rigid interaction requires lower time step than the
-fluid. We choose the minimum of both the timesteps to move the system forward
+  \ten{u}_a^{t+\Delta t} = \ten{u}_a^{t+\frac{1}{2}\Delta t} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^{t+\Delta t}.
+\end{equation}
+
+The modeling of rigid-rigid interaction requires a smaller time step than the
+fluid. We choose the minimum of these two timesteps to move the system forward
 in time. For the numerical stability of fluid, the time step depends on the
-CFL condition as,
+Courant–Friedrichs–Lewy (CFL) condition \cite{monaghan-review:2005} as,
 \begin{equation}
@@
 typically chosen as $10 |U|$ for fluids in this work. For rigid body, the time
-step is constrained as,
+step is constrained \cite{cundall_discrete_1979} as,
 \begin{equation}
@@
 particles and addressing a particle-wall impact scenario.  We validate the
-coupled Smoothed Particle Hydrodynamics (SPH)-DEM solver is confirmed through
-simulations involving a spherical particle entering a steady tank and a
-falling solid in a water tank and a floating solid. Lastly, we investigate the
-mixing behavior of spherical particles under a stirrer, examining cases with
-varying densities and diameters.
+coupled SPH-DEM solver with simulations involved like a circular particle
+entering a steady tank, a cube settling in a water tank.  Lastly, we
+investigate the mixing behavior of spherical particles under a stirrer,
+examining cases with varying particle diameters and stirrer speeds.
 
@@
 $\frac{1}{60}$, and set the speed of sound to ten times the maximum velocity
-the fluid can attain. The simulation runs for a total duration of $50$
+that the fluid can attain. The simulation runs for a total duration of $50$
 seconds.
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.png}
+  \includegraphics[width=0.7\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.png}
   \caption{Velocity profile of the Poiseuille flow compared against the
@@
 \end{figure}
-To validate the Discrete Element Method (DEM) solver, we analyze the direct
+To validate the Discrete Element Method (DEM) solver, we analyze the normal
 collision between two spherical particles.  In
@@
 moving towards each other with an initial velocity of $10$
-m\,s\textsuperscript{-1}.  Each disk has a radius of $0.01$ m and is composed
+m\,s\textsuperscript{-1}.  Each particle has a radius of $0.01$ m and is composed
 of glass. The glass material has a Young's modulus of $4.8 \times 10^{10}$
-N\,m\textsuperscript{-2}, a Poisson ratio of $0.2$, and a density of $2800$
+N\,m\textsuperscript{-2}, a Poisson's ratio of $0.2$, and a density of $2,800$
 kg\,m\textsuperscript{-3}.  For the current scenario, we assume there is no
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
+  \includegraphics[width=0.8\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
   \caption{Variation of the normal impact force with overlap of the impacting
@@
 The dimensions and material properties of both the particle and the wall are
-set based on the study by \cite{di2004comparison,kharaz2001experimental}. The
-radius of the impacting particle is $0.0025$ m and is made of aluminium
+set based on the study of \cite{di2004comparison,kharaz2001experimental}. The
+radius of the impacting particle is $2.5 \times 10^{-3}$ m and is made of aluminium
 oxide. The particle has a Young's modulus of $3.8 \times 10^{11}$
-N\,m\textsuperscript{-2}, a Poisson's ratio of $0.23$, and a density of $4000$
+N\,m\textsuperscript{-2}, a Poisson's ratio of $0.23$, and a density of $4,000$
 kg\,m\textsuperscript{-3}. The wall's Young's modulus is $70\times 10^{9}$
-N\,m\textsuperscript{-2}, with a Poisson ratio of $0.25$.  The impact velocity
+N\,m\textsuperscript{-2}, with a Poisson's ratio of $0.25$.  The impact velocity
 has a magnitude of $3.9$ m\,s\textsuperscript{-1}. The coefficient of friction
@@
 the free surface. The cylinder's radius is $0.11$ meters, and we investigate
-cases with densities of $500$ and $1000$ kg,m\textsuperscript{-3}.
+cases with densities of $500$ and $1000$ kg\,m\textsuperscript{-3}.
 The cylinder descends due to gravity into the tank. We perform tests using
@@
 $\times$ 140 mm $\times$ 140 mm. While the water depth is taken as $131$ mm. The density
-of the water is taken as $1000$ kg,m\textsuperscript{-3}, and the density of
-the cube is $2,120$ kg,m\textsuperscript{-3}. The schemtic of the initial
+of the water is taken as $1000$ kg\,m\textsuperscript{-3}, and the density of
+the cube is $2,120$ kg\,m\textsuperscript{-3}. The schemtic of the initial
 configuration is shown in \cref{fig:results_rfc_02_falling}. We show that the
@@
   \includegraphics[width=0.4\textwidth]{images/rfc_02_falling_solid_in_water/schematic}
-  \caption{Schematic of a cube of density $2120 kg,m\textsuperscript{-3}$
+  \caption{Schematic of a cube of density $2,120 kg\,m\textsuperscript{-3}$
     immersed half way in a steady hydrostatic tank is allowed to settle under
@@
 \subsection{Mixing of spherical particles in a fluid tank}
-\label{sec:mixing-spherical-particles-in-fluid-tank}
+\label{sec:mixing-spherical-particles-in-fluid-tank-homogeneous}
+
+In this section, we investigate particle dispersion within a tank under
+various stirrer velocities. Each circular particle has a radius of $0.055$ m,
+with a total of $54$ particles. The fluid's dimensions in the tank are set to
+a length of $3.3$ m and a height of $1.65$ m. The stirrer, positioned on the left
+side, has a height of $0.75$ m, half of which is submerged into the fluid, and
+a length of $0.11$ m. After allowing the particles to settle for $1$ second,
+the stirrer oscillates throughout the fluid length. We examine three stirrer
+speeds: $1$, $3$ m\,s\textsuperscript{-1}.  The schematic of the figure is
+given in \Cref{fig:schematic-Dinesh-mixer-homogeneous}. The solid particles
+have a Young's modulus of $10^{9}$ N\,m\textsuperscript{-2}, a Poisson's ratio
+of $0.23$ and a density of $1050$ kg\,m\textsuperscript{-3} is considered.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time0}
+  \caption{ Initial configuration of particles in a fluid tank including the
+    stirrer.}
+  \label{fig:schematic-Dinesh-mixer-homogeneous}
+\end{figure}
+
+\Cref{fig:1-mixing-1,fig:1-mixing-2,fig:1-mixing-3}, illustrate the
+distribution of particles within a fluid tanker under the influence of a
+stirrer.  In \Cref{fig:1-mixing-1}, particles tend to aggregate and settle
+gradually into a clump at the center. Additionally, their motion aligns with
+the surrounding fluid motion. Conversely, \Cref{fig:1-mixing-2,fig:1-mixing-3}
+depict a scenario where the high speed of the stirrer causes fluid to
+circulate heavily at the tank's corners, resulting in particle
+settlement at the tank's corners without efficient mixing.
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time1}
+    \subcaption{t = $3$ s}\label{fig:1-mixing-1-a}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time2}
+    \subcaption{t = $6$ s}\label{fig:1-mixing-1-b}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time3}
+    \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-c}
+  \end{subfigure}
+  % \begin{subfigure}{0.45\textwidth}
+  %   \centering
+  %   \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time0}
+  %   \subcaption{t = $7.38$ ms}\label{fig:1-mixing-1-d}
+  % \end{subfigure}
+  \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+    three time steps, where the stirrer is oscillating at a velocity of $1$
+    m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+    represents the velocity magnitude.}
+\label{fig:1-mixing-1}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_2/time1}
+    \subcaption{t = $3$ s}\label{fig:1-mixing-1-a}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_2/time2}
+    \subcaption{t = $6$ s}\label{fig:1-mixing-1-b}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_2/time3}
+    \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-c}
+  \end{subfigure}
+  \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+    three time steps, where the stirrer is oscillating at a velocity of $3$
+    m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+    represents the velocity magnitude.}
+\label{fig:1-mixing-2}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_3/time1}
+    \subcaption{t = $3$ s}\label{fig:1-mixing-1-a}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_3/time2}
+    \subcaption{t = $6$ s}\label{fig:1-mixing-1-b}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_3/time3}
+    \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-c}
+  \end{subfigure}
+  % \begin{subfigure}{0.45\textwidth}
+  %   \centering
+  %   \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time0}
+  %   \subcaption{t = $7.38$ ms}\label{fig:1-mixing-1-d}
+  % \end{subfigure}
+  \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+    three time steps, where the stirrer is oscillating at a velocity of $5$
+    m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+    represents the velocity magnitude.}
+\label{fig:1-mixing-3}
+\end{figure}
 
@@
 \subsection{Mixing of spherical particles of variable size in a fluid tank}
-\label{sec:mixing-spherical-particles-in-fluid-tank}
+\label{sec:mixing-spherical-particles-in-fluid-tank-inhomogeneous}
+In this section, similar to the case discussed in
+\Cref{sec:mixing-spherical-particles-in-fluid-tank-homogeneous}, we analyze circular
+particles with two different radii. These particles have a ratio of $1.2$
+between the larger and smaller particle, with the smaller particle having a
+radius of $0.11$ m. The schematic of the figure is provided in
+\Cref{fig:schematic-Dinesh-mixer-inhomogeneous}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_1/time0}
+  \caption{Schematic of mixer with two different radius in a fluid
+    tank.}\label{fig:schematic-Dinesh-mixer-inhomogeneous}
+\end{figure}
+
+\Cref{fig:2-mixing-1,fig:2-mixing-2} shows the distribution of particles in a
+fluid tank under the influence of a stirrer, with two stirrer speeds at three
+different time steps. Similar to
+\Cref{sec:mixing-spherical-particles-in-fluid-tank-homogeneous}, from
+\Cref{fig:2-mixing-1}, we see that with a lower stirrer speed, particles tend
+to aggregate and settle gradually into a clump at the center and at higher
+speeds due to the generated circulation near the tank corners, the particles
+settle at the corner and do not involve in the mixing, as can be seen from
+\Cref{fig:2-mixing-2}.
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_1/time1}
+    \subcaption{t = $3$ s}\label{fig:1-mixing-1-b}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_1/time2}
+    \subcaption{t = $6$ s}\label{fig:1-mixing-1-c}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_1/time3}
+    \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-d}
+  \end{subfigure}
+  \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+    three time steps, where the stirrer is oscillating at a velocity of $1$
+    m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+    represents the velocity magnitude.}
+\label{fig:2-mixing-1}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_2/time1}
+    \subcaption{t = $3$ s}\label{fig:1-mixing-1-b}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_2/time2}
+    \subcaption{t = $6$ s}\label{fig:1-mixing-1-c}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_inhomogeneous_2d/case_2/time3}
+    \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-d}
+  \end{subfigure}
+  \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+    three time steps, where the stirrer is oscillating at a velocity of $3$
+    m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+    represents the velocity magnitude.}
+\label{fig:2-mixing-2}
+\end{figure}
 
@@
 \label{sec:conclusions}
+In this study, mixing efficiency in a two-dimensional tank is examined using a
+similar stirrer type, employing a fully resolved SPH-DEM solver. The fluid
+phase is represented using a weakly compressible SPH formulation, while the
+interaction and dynamics of spherical particles are modeled using the Discrete
+Element Method (DEM). The interaction between the fluid and discrete particles
+is managed by associating the spherical particles with surrogate SPH
+particles. The coupled SPH-DEM solver is developed within the PySPH software
+framework \cite{ramachandran2021pysph}. Validation of the weakly compressible
+SPH method is performed using the Poiseuille flow problem, while the DEM
+solver is validated against particle-level benchmarks including head-on
+collisions between two spherical particles and particle-wall collisions. The
+validation of the coupled solver includes scenarios such as a circular
+particle entering a tank and a cube settling in a three-dimensional tank.  The
+influence of stirrer speed on particle dispersion in a 2D tank was thoroughly
+investigated. Different stirrer speeds were examined, revealing distinct
+behaviors. At lower stirrer speeds, particles tended to aggregate and remain
+in center within the tank, influenced due to the surrounding fluid
+velocity. While, higher stirrer speeds generated fluid circulation, causing
+some particles to settle at the tank corners, thus hindering their
+participation in mixing. The same behaviour was found even in scenarios involving
+particles with varying radii.
+
+Due to the current solver's capability in handling the free surfaces, we can
+extend the current to study the particle dispersion in a 3D cylindrical tank
+featuring an impeller. Further, we can explore how the speed and placement of
+the impeller affect mixing efficiency. Additionally, influence of particle
+cohesion on the inter-particle mixing behavior can be examined.
 

### 2024-05-30 automate.py

@@ -644,6 +644,10 @@ class Dinesh2024MixingWithStirrerHomogeneous2d(Problem):
             'case_3': (dict(
                 stirrer_velocity=5.
                 ), 'Case 3'),
+
+            'main_case': (dict(
+                stirrer_velocity=0.3
+                ), 'Main case'),
         }
 
         self.cases = [
@@ -703,6 +707,10 @@ class Dinesh2024MixingWithStirrerInHomogeneous2d(Problem):
                 stirrer_velocity=3.,
                 radius_ratio=1.2,
                 ), 'Case 2'),
+
+            'main_case': (dict(
+                stirrer_velocity=0.3
+                ), 'Main case'),
 
             # 'case_3': (dict(
             #     stirrer_velocity=5.,
@@ -955,6 +963,298 @@ class Hashemi2012FallingCircularCylinder(Problem):
                     shutil.copy(os.path.join(source, file_name), target_dir)
 
 
+class Hashemi2012DKT(Problem):
+    """
+    """
+    def get_name(self):
+        return 'hashemi_2012_DKT'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/hashemi_2012_dkt.py' + backend
+
+        # kinetic viscosity
+        # Base case info
+        self.case_info = {
+            'N_10': (dict(
+                N=10,
+                nu=1e-2,
+                ), 'N=10'),
+
+            'N_8': (dict(
+                N=8,
+                nu=1e-2,
+                ), 'N=8'),
+        }
+
+        self.cases = [
+            Simulation(get_path(name), cmd,
+                       job_info=dict(n_core=n_core,
+                                     n_thread=n_thread), cache_nnps=None,
+                       **scheme_opts(self.case_info[name][0]))
+            for name in self.case_info
+        ]
+
+    def run(self):
+        self.make_output_dir()
+        self.move_figures()
+        self.plot_displacement()
+
+    def plot_displacement(self):
+        data = {}
+        for name in self.case_info:
+            data[name] = np.load(self.input_path(name, 'results.npz'))
+
+        rand_case = (list(data.keys())[0])
+
+        t_zhang_FPM_PST = data[rand_case]['t_zhang_FPM_PST']
+        vertical_position_zhang_FPM_PST = data[rand_case]['vertical_position_zhang_FPM_PST']
+        t_hashemi_sph = data[rand_case]['t_hashemi_sph']
[…]

### 2024-05-30 code/dinesh_2024_mixing_with_stirrer_2d.py

@@ -114,7 +114,7 @@ class Problem(Application):
                            help="Diameter of each particle")
 
         group.add_argument("--stirrer-velocity", action="store", type=float,
-                           dest="stirrer_velocity", default=1,
+                           dest="stirrer_velocity", default=0.319,
                            help="Stirrer velocity")
 
         group.add_argument("--radius-ratio", action="store", type=float,
@@ -249,15 +249,23 @@ class Problem(Application):
         xf, yf, xt, yt = hydrostatic_tank_2d(self.fluid_length, self.fluid_height,
                                              self.tank_height, self.tank_layers,
                                              self.dx, self.dx, False)
-
-        zt = np.zeros_like(xt)
         zf = np.zeros_like(xf)
-
         # move fluid such that the left corner is at the origin of the
         # co-ordinate system
         translation = translate_system_with_left_corner_as_origin(xf, yf, zf)
         xt[:] = xt[:] - translation[0]
         yt[:] = yt[:] - translation[1]
+
+        xt_1, yt_1 = get_2d_block(dx=self.dx,
+                                  length=self.fluid_length,
+                                  height=self.stirrer_length)
+        xt_1 += min(xf) - min(xt_1)
+        yt_1 += max(yt) - max(yt_1)
+        xt = np.concatenate([xt, xt_1])
+        yt = np.concatenate([yt, yt_1])
+
+        zt = np.zeros_like(xt)
+
         zt[:] = zt[:] - translation[2]
 
         # xf, yf, zf = np.array([0.02]), np.array([self.fluid_height]), np.array([0.])
@@ -634,7 +642,7 @@ class Problem(Application):
             axs.scatter(stirrer.x, stirrer.y, s=s, c="k")
             axs.scatter(rigid_body.x, rigid_body.y, s=s, c="r")
             tmp = axs.scatter(fluid.x, fluid.y, s=s, c=vmag, vmin=c_min,
-                              vmax=c_max, cmap="jet")
+                              vmax=c_max, cmap="jet", rasterized=True)
             # tmp = axs.scatter(fluid.x, fluid.y, s=s, c=fluid.p, vmin=c_min,
             #                   vmax=c_max, cmap="hot")
 
@@ -653,7 +661,7 @@ class Problem(Application):
 
             # save the figure
             figname = os.path.join(os.path.dirname(fname), "time" + str(i) + ".pdf")
-            fig.savefig(figname, dpi=300)
[…]

### 2024-05-30 code/hashemi_2012_dkt.py

@@ -106,6 +106,24 @@ class Problem(Application):
                            dest="rigid_body_diameter", default=1e-3,
                            help="Diameter of each particle")
 
+        group.add_argument("--radius-ratio", action="store", type=float,
+                           dest="radius_ratio", default=1.0,
+                           help="Diameter of each particle")
+
+        add_bool_argument(
+            group,
+            'top',
+            dest='top_particle',
+            default=True,
+            help='Make top particle radius bigger')
+
+        add_bool_argument(
+            group,
+            'parallel-arrangement',
+            dest='parallel_arrangement',
+            default=False,
+            help='Make particles next to each other (parallel arrangement)')
+
         add_bool_argument(
             group,
             'follow-combined-rb-solver',
@@ -131,6 +149,9 @@ class Problem(Application):
         # dimensions rigid body dimensions
         # All the particles are in circular or spherical shape
         self.rigid_body_diameter = 0.00125 * 2.
+        self.radius_ratio = self.options.radius_ratio
+        self.top = self.options.top_particle
+        self.parallel = self.options.parallel_arrangement
         self.rigid_body_velocity = 0.
         self.no_of_layers = self.options.no_of_layers
         self.no_of_bodies = 3 * 6 * self.options.no_of_layers
@@ -200,7 +221,7 @@ class Problem(Application):
         print("sound speed c0 is", self.c0)
         self.mach_no = self.vref / self.c0
         self.nu = 0.0
-        self.wall_time = 0.3
+        self.wall_time = 0.0
         self.tf = 0.8 + self.wall_time
         # self.tf = 0.56 - 0.3192
         self.p0 = self.fluid_rho*self.c0**2
@@ -289,13 +310,34 @@ class Problem(Application):
         return rigid_body_combined
 
     def create_rb_geometry_particle_array(self):
-        x1, y1 = create_circle_1(self.rigid_body_diameter, self.dx)
 
-        x2, y2 = create_circle_1(self.rigid_body_diameter, self.dx)
-        y2[:] += self.rigid_body_diameter * 1.5
+        if self.top == True:
+            x1, y1 = create_circle_1(2. * (self.rigid_body_diameter / 2.), self.dx)
[…]

### 2024-05-30 code/hashemi_2012_falling_of_circular_cylinder_in_a_closed_channel.py

@@ -576,7 +576,7 @@ class Problem(Application):
             # v.append(rigid_body.vcm[1])
                 y.append(rigid_body.y[0])
                 v.append(rigid_body.v[0])
-                t.append(_t)
+                t.append(_t - self.wall_time)
 
                 force_p_magn.append(np.sum(rb_slave.fx_p[:]**2. + rb_slave.fy_p[:]**2. + rb_slave.fz_p[:]**2.)**0.5)
                 force_v_magn.append(np.sum(rb_slave.fx_v[:]**2. + rb_slave.fy_v[:]**2. + rb_slave.fz_v[:]**2.)**0.5)

### 2024-05-31 manuscript/extended_abstract.tex
Add an extended abstract

--- 2024-03-01 manuscript/paper.tex
@@
-\documentclass[preprint,12pt]{elsarticle}
-% \documentclass[draft,12pt]{elsarticle}
+\documentclass[a4paper,11pt]{book}
 
+% TEMPLATE
+% ----------------------------------------------------------------------
+\usepackage[utf8]{inputenc}
+\usepackage{geometry}
+\geometry{
+	a4paper,
+	left=20mm,
+	top=30mm,
+	bottom=30mm,
+}
+\usepackage[hidelinks]{hyperref}
+\usepackage{titlesec}
+\usepackage{etoolbox}
+\usepackage{chngcntr}
+\usepackage{graphicx}
+\usepackage{lipsum}
+\usepackage{xcolor}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{fancyhdr}
+\usepackage{booktabs}
+
+\counterwithout{figure}{chapter}
+\renewcommand\thesection{\arabic{section}}
+\patchcmd{\thebibliography}{\chapter*}{\section*}{}{}
+\renewcommand{\bibname}{References}
+\bibliographystyle{plainnat}
+\pagestyle{empty}
+\titleformat{\chapter}[frame]{\normalfont}{}{10pt}{\LARGE\bfseries\filcenter}
+\pagestyle{fancy}
+\fancyhf{}
+\pagestyle{fancy}
+% \fancyhead[LE,RO]{}
+% \fancyhead[RE,LO]{Modelling for Engineering \& Human Behaviour 2024}
+% \fancyfoot[C]{\thepage}
+
+\renewcommand{\theequation}{\arabic{equation}}
+\renewcommand{\thefigure}{\arabic{figure}}
+\renewcommand{\thetable}{\arabic{table}}
+% ----------------------------------------------------------------------
+
+% ==============================
+% Imports from my paper
+% ==============================
 \usepackage{hyperref}
@@
 \usepackage{lineno}
-% \linenumbers
-
-\journal{}
+\usepackage{natbib}
+% ==============================
+% Imports from my paper ends
+% ==============================
 
@@
 
-\begin{frontmatter}
+\chapter{{DEM}-{SPH} study of particles dispersion in fluid}
 
-  \title{Study of mixing behaviour of spherical particles in fluid using stirrer}
-  \author[XXX]{Dinesh Adepu\corref{cor1}}
-  \ead{d.dinesh@surrey.ac.uk}
-  \author[University of Surrey]{Chuan Yu Wu}
-  \ead{XXX}
-\address[xxx]{xxx}
+\thispagestyle{empty}
+\vspace{-0.5cm}
+\begin{center}
+\begin{large}
+  \underline{Dinesh Adepu}$^\flat$\footnote{d.adepu@surrey.ac.uk}
+  and Chuan-Yu Wu$^\flat$\\
+  % and C. Author$^\flat$\\
+  \vspace{0.25cm}
+  \normalsize ($\flat$)\; School of Chemistry and Chemical Engineering, University of Surrey\\
+  \normalsize  Guildford, Surrey, United Kingdom.\\
+  % \vspace{0.1cm}
+  % \normalsize ($\natural$)\;  Second Author Affiliation,\\
+  % \normalsize Second Author Address.\\
+\end{large}
+\end{center}
+\vspace{-0.5cm}
 
-\cortext[cor1]{Corresponding author}
-
-\begin{abstract}
-  Particle dispersion is a fundamental physical phenomenon encountered in
-  various industries where powder and fluid interactions are
-  pivotal. Particularly, processes involving the mixing of powder with fluid
-  using a stirrer are commonplace. While experimental investigation of such
-  processes is often impractical due to their highly nonlinear nature,
-  numerical methods offer a viable alternative. Among these, Smoothed Particle
-  Hydrodynamics coupled with Discrete Element Method (SPH-DEM) stands out for
-  its ability to handle free surface fluid dynamics and model the complex
-  physics inherent in dispersion processes.
-
-  In this study, we initially develop and validate both the DEM and SPH
-  solvers. Validation includes testing against fundamental benchmarks such as
-  two-particle head-on collisions and particle-wall impacts for the DEM
-  solver, and Poiseuille flow for the fluid solver. Additionally, we validate
-  the rigid-fluid model through simulations of a single cylindrical body
-  entering a steady tank and the settling of two tandem cylinders in a
-  fluid-filled tank.
-
-  With confidence in the fidelity of our solver established, we delve into
-  investigating the mixing behavior of spherical particles dispersed in
-  water. Our study encompasses various scenarios, including particles with
-  densities higher or lower than the surrounding fluid, as well as particles
-  with varying radii. We also examine combinations of these factors.
-  \todoin{What factor have you considered to quantify the mixing
-    behaviour.}
-
-  \todoin{Write the findings}
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-{xxx}, {xxx}, {xxx}
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-% \linenumbers
-
-\FloatBarrier%
 \section{Introduction}
 
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/hs_tank_fluid_with_particles}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
-\end{figure}
+Particle dispersion is crucial in various industries from food processing to
+ice-sea modeling where powder and fluids interact.  Studying particle dispersion
+through experiments can be difficult due to the complex interactions involved.
+Numerical methods, however, offer a powerful alternative, allowing researchers
+to explore these systems using mesh-based or meshless techniques.  Computational
+Fluid Dynamics and Discrete Element Method (CFD-DEM) is a common approach for
+simulating particle flow.  Mesh-based methods like lattice Boltzmann and finite
+volume methods handle the fluid, while meshless methods like Smoothed Particle
+Hydrodynamics (SPH) handle it without a mesh. Mesh based methods struggle with
+free surfaces and large particle numbers, while meshless methods excels in these
+areas. Among many meshless techniques, SPH has been used for various particulate
+flows, including mixing of simple spheres and debris flow with complex shapes.
 
-\begin{itemize}
-\item Fluid modeling using smoothed particle hydrodynamics
-  (\cref{sec:fluid--modeling})
-\item Interaction among the discrete spherical rigid particle units by
-  discrete element method (\cref{sec:rbd})
-\end{itemize}
+This work simulates particle dispersion in a stirred tank using SPH for fluids
+and DEM for particles.  The interaction between particles and fluids is fully
+resolved.  We validate both the SPH and DEM solvers individually, followed by
+validation of the combined SPH-DEM solver.  Then we analyze how different
+particle properties and stirrer velocities affect mixing behavior. We use an
+open-source code called PySPH and modify it. We use an automation package to
+ensure our results are reproducible.
 
-While the interaction among the rigid spherical particle and fluid particles
-are modeled by sampling the spherical particles into dummy SPH particles. This
-is explained in \cref{sec:rfc}.
+\section{Modeling}
+\subsection{Fluid modeling}
 
-% \FloatBarrier%
-% \section{Fluid modeling}
-
-% \FloatBarrier%
-% \subsection{Boundary conditions}
-
-% \FloatBarrier%
-% \section{Solid phase modeling}
-
-% \FloatBarrier%
-% \subsection{Discrete element method}
-
-% \FloatBarrier%
-% \subsection{Rigid body equations}
-
-% \FloatBarrier%
-% \section{Rigid fluid coupling}
-
-% \FloatBarrier%
-% \section{Results}
-
-\FloatBarrier%
-\subsection{Fluid modeling}
-\label{sec:fluid--modeling}
-
+% \subsection{Discretized fluid governing equations}
 In the current work, we follow a weakly-compressible SPH approach to model the
-fluid. The SPH discretization of the continuity
-equation~\cref{eq:sph-discretization-continuity} and the momentum equation
-~\cref{eq:sph-momentum-fluid} respectively are,
+fluid. The continuum in SPH is modeled using particles, which has physical
+properties such as mass, velocity, and these particles interact based on the
+governing equations using a Guassian-like kernel. The SPH discretized governing
+equations for the continuity equation and the momentum equation of a fluid are
+given as:
 \begin{equation}
@@
 \end{equation}
-
-%
-Similarly, the discretized momentum equation for fluids is written as,
 \begin{multline}
@@
   \frac{{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg)
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2} + \Pi_{ab}\bigg)
   \nabla_{a} W_{ab}
@@
     \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}  \;+\;
-  \ten{g}_{a} + \text{force due to rb},
+  \ten{g}_{a},
 \end{multline}
-where $\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
-% fluid and \textcite{morris1997modeling} formulation is used to discretize the
-viscosity term.
-
-We add to the momentum equation an additional artificial viscosity term
-% $\Pi_{ab}$~\parencite{monaghan-review:2005} to maintain the stability of the
-numerical scheme, given as,
+where $\rho$ is the density, $\ten{u}$ is the velocity, $g$ is the component of
+body force per unit mass, where $\eta$ is the kinematic viscosity of the fluid,
+$p$ is the pressure.  Artificial viscosity term $\Pi_{ab}$, given as,
 \begin{align}
@@
 \FloatBarrier%
-\subsection{Boundary conditions}
-\label{sec:boundary_conditions}
-
-\FloatBarrier%
-\section{Rigid body dynamics}
+\subsection{Rigid body dynamics}
 \label{sec:rbd}
@@
 
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.7\textwidth]{images/rigid_body/rigid_body}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
-\end{figure}
-We use two coordinate frames to capture the dynamics of the rigid body, a
-global frame and a body frame as shown in
-\cref{fig:gloabl_body_frame_rb}. The body fixed frame, which moves with
-rigid body is always located at the center of mass ($\ten{x}_{cm}$). The
-state of the rigid body at a given time ($t$) can be described using position
-($\ten{x}_{cm}$) and velocity ($\ten{v}_{cm}$) of the center of mass, a
-rotation matrix($\ten{R}$) to represent the orientation of the rigid body with
-respect to the global frame, and angular velocity($\teng{\omega}$). The center
-of mass is computed as
-\begin{equation}
-  \label{eq:rfc:center_of_mass}
-  \ten{x}_{cm} = \frac{\sum_i m_i \; \ten{x}_{i} }{\sum_i m_i }.
-\end{equation}
-The position of the discretized particle ($i$) in
-\cref{fig:gloabl_body_frame_rb} belonging to the rigid body at time $t$ can be
-computed as,
-\begin{equation}
-  \label{eq:rfc:rb_particle_pos_update}
-  \ten{x}_i = \ten{x}_{cm} + \ten{r}_{i},
-\end{equation}
-with
-\begin{equation}
-  \label{eq:rfc:rb_particle_pos_update}
-  \ten{r}_i = \ten{R} \overline{\ten{r}}_{i}.
-\end{equation}
-Here $\overline{\ten{r}}_{i}$ is the position of the particle $i$ about the body
-frame axis and remains constant through out the simulation. The rotation matrix
-$\ten{R}$ is used to bring the body frame position vector to the global frame
-$\ten{O}$. Similarly the velocity vector is computed as,
-\begin{equation}
-  \label{eq:rfc:rb_particle_vel_update}
-  \ten{v}_i = \ten{v}_{cm} + \teng{\omega} \times \ten{r}_{i}.
-\end{equation}
-
-We evolve the state of the rigid body through the integration of the
-\cref{eq:rfc:balance_linear_mom,eq:rfc:balance_angular_mom}. The linear velocity of the
-center of mass ($\ten{v}_{cm}$) and angular momentum ($\ten{L}$) at the next
-timestep are computed as,
-\begin{equation}
-  \label{eq:rfc:lin_vel_cm_update}
-  \ten{v}_{cm}^{n+1} = \ten{v}_{cm}^{n} + \frac{\ten{F}_{cm}}{M} \; \Delta t,
-\end{equation}
-\begin{equation}
-  \label{eq:rfc:ang_mom_update}
-  \ten{L}^{n+1} = \ten{L}^{n} + \teng{\tau}_{cm} \; \Delta t.
-\end{equation}
-Here, $\ten{F}_{cm} = \sum_i \ten{F}_i$.
-
-The position of the center of mass and the rotation matrix ($\ten{R}$) are updated
-by,
-\begin{equation}
-  \label{eq:rfc:lin_pos_cm_update}
-  \ten{x}_{cm}^{n+1} = \ten{x}_{cm}^{n} + \ten{v}_{cm}^{n} \; \Delta t,\\
-  \ten{R}^{n+1} = \ten{R}^{n} + \tilde{\teng{\omega}}^{n} \, \ten{R}^{n} \; \Delta t,
-\end{equation}
-where $\tilde{\teng{\omega}}^{n}$ is matrix formulation of angular velocity
-$\omega$. The angular velocity at the new time step is computed with
-\begin{equation}
-  \label{eq:rfc:ang_velocity_update}
-  \teng{\omega}^{n+1} = (\textit{\teng{I}}^{-1})^{n+1} \; \ten{L}^{n+1}.
-\end{equation}
-Here, moment of inertia at the new time step is computed as,
-\begin{equation}
-  \label{eq:rfc:moi_update}
-  (\textit{\teng{I}}^{-1})^{n+1} = \ten{R}^{n+1} \textit{\teng{\overline{I}}}^{-1} (\ten{R}^{n+1})^T.
-\end{equation}
-where moment of inertia ($\textit{\teng{\overline{I}}}^{-1}$) in body frame is
-used to compute in global frame at every time instant for faster computations.
-The moment of inertia ($\textit{\teng{\overline{I}}}$) is computed as,
-\begin{equation*}
-\textit{\teng{\overline{I}}} =
-\begin{bmatrix}
-\sum_i m_i (y_i^2 + z_i^2) & -\sum_i m_i x_iy_i & -\sum_i m_i x_iz_i\\
--\sum_i m_i x_iy_i & \sum_i m_i (x_i^2 + z_i^2) &  -\sum_i m_i y_iz_i\\
--\sum_i m_i  x_iz_i & -\sum_i m_i y_iz_i & \sum_i m_i (x_i^2 + y_i^2)
-\end{bmatrix}.
-\end{equation*}
-
-The position and velocity of the particles of the rigid body are updated by
-\begin{eqnarray}
-  \label{eq:rfc:rb_particle_pos_update}
-  \ten{r}_i = \ten{R} \cdot \overline{\ten{r}}_{i},\\
-  \ten{x}_i = \ten{x}_{cm} + \ten{r}_{i},\\
-  \ten{v}_i = \ten{v}_{cm} + \teng{\omega} \times \ten{r}_{i}.
-\end{eqnarray}
-
 The force acting on particle $i$ is composed of interaction with the other rigid
@@
 \end{eqnarray}
-We follow \cref{sec:contact-algorithm} to compute force
-$\ten{F}_{\text{cont}}^a$ acting on particle $i$ due to the interaction with
-the rigid bodies. The force $\ten{F}_{\text{Fl}}^i$ acting due to the
-interaction with the fluid particles follows \cref{subsec:fsi}.
+We follow DEM to compute force $\ten{F}_{\text{cont}}^a$ acting on particle $i$
+due to the interaction with the rigid bodies. The force $\ten{F}_{\text{rfc}}^i$
+acting due to the interaction with the fluid particles is computed by resolving
+the rigid body into dummy SPH particles.  These SPH particles are evenly
+distributed and remain stationary, moving in tandem with the velocity of the
+rigid particle at any given location.  They serve as SPH boundary particles and
+contribute to the computation of fluid particle density and acceleration.  The
+force acting on the sampled dummy SPH particle due to the interaction with the
+fluid is given by,
+\begin{equation}
+  \label{eq:rfc-force}
+  \ten{F}_{\text{rfc}}^a = -m_a \sum_{f} m_f \bigg(\frac{p_f}{\rho_{f}^2} +
+  \frac{p_a}{\rho_{a}^2}\bigg) \nabla_{a} W(x_{af}) +
+  m_a \sum_{f} m_f \frac{4 \eta \nabla_a W_{af}\cdot
+    \ten{r}_{af}}{(\rho_a + \rho_f) (r_{af}^2 + 0.01 h_{af}^2)} \ten{u}_{af}
+\end{equation}
+where, $m_a$ signifies the hydrodynamic mass of the sampled dummy SPH particle,
+and $\rho_a$ represents its hydrodynamic density. While $m_f$, $p_f$ and
+$\rho_f$ are mass, pressure and density of the fluid particle.
+
+\section{Results}
+
+We validate the Discrete Element Method solver by simulating a particle-wall
+impact scenario.  We validate the coupled SPH-DEM solver with simulations
+involved like a circular particle entering a steady tank.  Lastly, we
+investigate the mixing behavior of spherical particles under a stirrer,
+examining cases with varying particle diameters and stirrer speeds.
 
 \FloatBarrier%
-\subsection{Contact resolution}
-\label{sec:dem}
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.7\textwidth]{images/spherical_particles_dem_representation}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
-\end{figure}
-
-We resolve the contact among the spherical particles using discrete element
-method. In the current work we have utilized the contact force model proposed
-by \citet{mohseni2021particle}. The force acting on a particle $a$ due to the
-interaction with the particle $b$ can be resolved into a normal and tangential
-component. The normal force component is utilised to make sure that the
-particle do not penetrate into each other, while the tangential component is
-used to model the friction between the interacting solids.  The normal force
-($\teng{F}_a^{n}$) on particle $a$ due to the interaction with the particles
-$b$ is given as,
-\begin{equation}
-  \label{eq:contact-algorithm-normal}
-  \ten{F}_a^n = k_r \delta_{n^{c}}^{a} \ten{n}_a^{c}.
-\end{equation}
-Here, the overlap $\delta_{n^{c}}^{a}$ is computed using
-\begin{equation}
-  \label{eq:cf-overlap}
-  \delta_{n^{c}}^{a} = \Delta x - d_a,
-\end{equation}
-where the normal contact vector $\ten{n}_a^{c}$ is computed using
-\begin{equation}
-  \label{eq:cf-normal-vector}
-  \ten{\hat{n}}_a^{c} = \frac{
-    \displaystyle\sum\limits_{b = 1}^{\text{NP}^{b}} \;
-    \frac{\ten{r}_{ab}}{r_{ab}}  \frac{m_b}{\rho_b} W_{ab}}
-  {
-    \displaystyle\sum\limits_{b = 1}^{\text{NP}^{b}} \;
-    \frac{m_b}{\rho_b} W_{ab}},
-\end{equation}
-\begin{equation}
-  \label{eq:cf-normal-vector}
-  \ten{n}_a^{c} = \frac{\teng{\hat{n}}_a^{c}}{||\teng{\hat{n}}_a^{c}||}.
-\end{equation}
-With $\Delta x$ being the initial spacing between the particles, $k_r$ is the normal
-spring stiffness coefficient. Note that while computing the overlap of
-particle $a$ with the body $B$ we have computed an effective overlap, rather
-than per particle interaction. This effectively is able to model the
-interaction between non smooth surfaces in contrast with particle-particle
-force computation.
-
-\subsection{Tangential force computation}
-\label{sec:tangential-force-computation}
-We associate a tangential spring attached to particle $i$ and body $B$ to
-compute the tangential force, which initially has a magnitude of zero
-($|\Delta \textit{\textbf{l}}_a|=0$). And the tangential spring is activated
-when the particle comes into contact with body $B$. The tangential force is
-history-dependent. The contact friction force is proportional to the
-tangential spring displacement, which is integrated over the contact time as
-\begin{equation}
-  \label{eq:tangential-force}
-  \ten{F}_{a}^{t^{n+1}} =
-  -k_f \Delta \textit{\textbf{l}}_a^{\,n + 1} =
-  -k_f \big[\big(\Delta {\textit{\textbf{l}}}_a^{\,n} \
-  + \ten{v}_{ab}^{n + 1} \Delta t\big) \cdot \ten{t}_a^{n + 1} \big] \
-  \ten{t}_a^{n + 1},
-\end{equation}
-where $\Delta t$ is the time step, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is
-the relative velocity of the primary particle $a$ with respect to the
-closest secondary particle $b$, and $k_f$ is the tangential spring stiffness
-coefficient. The tangential unit vector is computed by,
-\begin{equation}
-  \label{eq:tangential-vect}
-  \ten{t}_a = \frac{\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}_a^{c}) \ten{n}_a^{c}}{|\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}_a^{c}) \ten{n}_a^{c}|}.
-\end{equation}
-
-The tangential force is coupled to the normal force through the Coulomb's law,
-\begin{equation}
-  \label{eq:Coulomb-law}
-  \ten{F}_{a}^{t} = \min(\mu |\ten{F}_{a}^{n}|, |\ten{F}_{a}^{t}|) \
-  \frac{\ten{F}_{a}^{t}}{|\ten{F}_{a}^{t}|}.
-\end{equation}
-This allows us to impose the sliding friction condition between the
-interacting solids. Finally, the total force acting on the particle $a$ due to
-the interaction with body $B$ is:
-\begin{equation}
-  \label{eq:contact-force}
-  \ten{F}_{a}^{\text{cont}} = \ten{F}_{a}^{n} + \ten{F}_{a}^{t}
-\end{equation}
-
-% \begin{figure}[!htpb]
-%   \centering
-%   \includegraphics[width=0.3\textwidth]{images/contact_force/contact_force_description_3}
-%   \caption{Force transfer to the secondary particles $b$ from the primary body particle $a$}
-% \label{fig:secondary_particle_contact_foce_transfer}
-% \end{figure}
-An equal and opposite force of the same magnitude is applied to the closest
-secondary particle $b$ of $a$ as shown in
-\cref{fig:secondary_particle_contact_foce_transfer},
-\begin{equation}
-  \label{eq:contact-force}
-  \ten{F}_{b}^{\text{cont}} = - \ten{F}_{a}^{\text{cont}}.
-\end{equation}
-
-% =========================================== %
-% ------ Results start ---------------------- %
-% =========================================== %
-
-\FloatBarrier%
-\subsection{Rigid fluid coupling}
-\label{sec:rfc}
-
-\begin{figure}[!htpb]
-  \centering
-  \begin{subfigure}{0.22\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/real_spherical_particles}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-0}
-  \end{subfigure}\hspace{15mm}%
-  \begin{subfigure}{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/sph_sampled_spherical_particles}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-1}
-  \end{subfigure}
-  \caption{}
-\label{fig:real_particle_sph_sampling}
-\end{figure}
-In order to compute the force acting on the spherical particle due to the
-interacting fluid we sample the spherical particle with dummy SPH particles,
-as shown in \cref{fig:real_particle_sph_sampling}. Here the spherical particle
-is sampled using dummy SPH particles, while SPH particles are being placed
-equispaced. With spherical particles being discretized into SPH particles and
-immersed in fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.7\textwidth]{images/rfc_zoomed_combined}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:many_rb_in_fluid_sph_particles}
-\end{figure}
-
-Force on each sampled SPH particles consisting of the rigid body due to the
-interaction with the fluid particle is given as. The mass of each dummy
-particle being sampled in the spherical particle is considered as
-hydrodynamics mass. The force on the fluid particle due to the interaction
-with the sampled dummy SPH particles is considered in the momentum and the
-continuity equation. The force acting on the sampled dummy SPH particle due to
-the interaction with the fluid is given by,
-\begin{equation}
-  \label{eq:sph-discretization-continuity}
-  \frac{{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \;
-  \rho_{a} \; {\ten{u}}_{ab} \; \cdot \nabla_{a} W_{ab},
-\end{equation}
-The force here is composed of two components, one is due to the pressure and
-due to viscosity.
-
-\FloatBarrier%
-\subsection{Time Integration}
-
-Rigid body and the fluid follow the kick-drift-kick time integration scheme. The
-modeling of rigid-rigid interaction requires lower time step than the fluid. We
-choose the minimum of both the timesteps to move the system forward in time. For
-the numerical stability of fluid, the time step depends on the CFL condition as,
-\begin{equation}
-  \label{eq:rfc:time-step-cfl}
-  \Delta t_{\text{fluid}} = \mathrm{min} \bigg( 0.25 \; \frac{h}{c + |U|} ,  0.25 \; \frac{h^2}{\nu},  0.25 \; \frac{h^2}{g} \bigg),
-\end{equation}
-where $|U|$ is the maximum velocity magnitude, $c$ is the speed of sound
-typically chosen as $10 |U|$ for fluids in this work. For rigid body, the time
-step is constrained as,
-\begin{equation}
-  \label{eq:rfc:time-step-body-force}
-  \Delta t_{\text{rb}} \leq \frac{\pi}{50} \sqrt{\frac{m}{K_r}}.
-\end{equation}
-A minimum timestep is chosen as
-\begin{equation}
-  \label{eq:rfc:time-step-body-force}
-  \Delta t = min(\Delta t_{\text{fluid}}, \Delta t_{\text{rb}}).
-\end{equation}
-
-\FloatBarrier%
-\section{Results}
-\label{sec:results}
-
-\FloatBarrier%
-\subsection{Poiseuille's flow}
-\label{sec:poiseuille_flow}
-% https://onlinelibrary.wiley.com/doi/epdf/10.1002/nag.898
-
-\begin{itemize}
-\item Unsteady flow between two infinite, parallel paltes at rest in presence
-  of pressure gradient.
-\item Write about the location of the plates.
-\item Which way the flow is going (positive x or negative x)
-\item In this exact conditions, the Navier-Stokes equations admit the time
-  dependent solution (Write solution (equation 19))
-\item Periodic boundary conditions
-\item The accuracy of the results presented here validate the developed
-  no-slip boundary method inthe presence of straight boundaries.  The
-  remainder of this section addresses the more complexcase of non-straight
-  boundaries.
-\item Write about the schematic
-\item Write the resulting velocity profile
-\item Numerical parameters are important
-\item A body force of 1e-5
-\item Viscosity 0.01
-\item Time of 50 seconds
-\item spacing of 1 / 60
-\item Length in y is 2 * self.d=0.5
-\item Length in x 0.4 * self.Ly
-\item self.re = self.options.re
-\item self.Vmax = self.nu*self.re/(2*self.d)
-\item self.c0 = 10*self.Vmax
-\item self.p0 = self.c0**2*self.rho0
-\item self.fx = self.Vmax * 2*self.nu/(self.d**2)
-\end{itemize}
-
-The analytical solution from Morris is given as
-
-\begin{equation}
-  \label{eq:sph-discretization-continuity}
-  v_x(y, t) = \frac{F}{2 \nu}y(y - L) + \sum_{n=0}^{\infty}\frac{4FL^2}{\nu \pi^3 (2n + 1)^3} \sin\bigg(\frac{\pi y}{L} (2 n + 1) \bigg) \exp\bigg(\frac{ (2 n + 1)^2 \pi^2 \nu}{L^2} t\bigg)
-\end{equation}
-
-$\nu$ is kinematic viscosity ($\frac{\mu}{\rho_0}$)
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/fluid_01_benchmark_poisuelle/poiseuille_schematic}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
-\end{figure}
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.png}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:gloabl_body_frame_rb}
-\end{figure}
-
-\FloatBarrier%
-\subsection{DEM validation 1: Normal impact of spherical particle}
-\label{sec:DEM_validation_1_normal_impact}
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/results_dem_1_validation_particle_particle_impact/dem_01_head_on_schematic}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:result:dem_1_schematic}
-\end{figure}
-For the initial validation of the Discrete Element Method (DEM), we examine
-the head-on collision of two spherical particles. In
-\cref{fig:result:dem_1_schematic}, the initial setup depicts both particles
-moving towards each other with an initial velocity of $10$
-m\,s\textsuperscript{-1}.  Each disk has a radius of $0.01$ m and is composed
-of glass. The glass material has a Young's modulus of $4.8 \times 10^{10}$
-N\,m\textsuperscript{-2}, a Poisson ratio of $0.2$, and a density of $2800$
-kg\,m\textsuperscript{-3}.  For the current scenario, we assume there is no
-friction or gravity acting on the particles.
-\Cref{fig:result:dem_1_force_vs_overlap} depicts the variation of the normal
-force and the amount of overlap, compared to the analytical findings presented
-in \citet{xxxx}. The force curve generated by our current implementation
-closely matches the analytical result, confirming the validation of our DEM
-solver's normal contact force model.
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:result:dem_1_force_vs_overlap}
-\end{figure}
-
-\FloatBarrier%
-\subsection{DEM validation 2: Particle wall impact}
+\subsection{DEM validation: Particle wall impact}
 \label{sec:DEM_validation_2_particle_wall_impact}
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/results_dem_2_validation_particle_wall_impact/schematic}
-  \caption{}
-  \label{fig:result:dem_sw_contact_schematic}
-\end{figure}
-As part of our validation test cases, we consider the collision of a spherical
-particle with wall with different incident angles and a constant velocity in
-magnitude. This test case is helpful in testing the tangential part of our DEM
-implementation. The schematic of the body and wall is shown in
-\cref{fig:result:dem_sw_contact_schematic}. The radius of the impacting particle is
-$0.0025$ m and is made of aluminium oxide. The particle has a Young's modulus
-of $3.8 \times 10^{11}$ N\,m\textsuperscript{-2}, a Poisson ratio of $0.23$, and a
-density of $4000$ kg\,m\textsuperscript{-3}. The impact velocity has a
-magnitude of $3.9$ m\,s\textsuperscript{-1}. The friction coefficient among
-the wall and the particle is $0.092$.
-
-In \cref{fig:result:dem_sw_contact_omega_vs_theta}, we plot the variation of
-the rebound angular velocity with the incident impact angle, compared against
-the experimental result given in \citet{xxxx}. The variation of the angular
-velocity produced by our current implementation matches with the experimental
-result, confirming the validation of our DEM solver's tangential part of the
-contact force model.
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/benchmark_4_sw_colliding_oblique/angle_vs_ang_vel.pdf}
-  \caption{Body frame and local frame description of rigid body}
-  \label{fig:result:dem_sw_contact_omega_vs_theta}
-\end{figure}
-
-\FloatBarrier%
-\subsection{RFC validation 1: Single particle entering into a tank}
-\label{sec:rfc_validation_1_single_particle_entry}
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/rfc_01_skillen_2013_particle_entry_in_hs_tank/Skillen_2013_particle_entry_in_hs_tank}
-  \caption{Half Buoyant}
-  \label{fig:results_rfc_01_skillen_2013}
-\end{figure}
-To validate the rigid fluid coupling solver, we study the motion of a circular
-cylinder dropping into a steady tank. This problem has been studied
-experimentally by Greenhow and Lin
-\citet{xxxx}. \Cref{fig:results_rfc_01_skillen_2013} shows the initial
-configuration of the cylinder placed at $0.5$ m from the free surface. The
-radius of the disc is taken as $0.11$ m, while we consider two cases with the
-density of $500$ and $1000$ kg\,m\textsuperscript{-1}. The cylinder falls
-under the gravity into the tank.
-
-\todoin{Initial spacing, viscosity, gravity, h value, speed of sound, number of
-  particles, resolution write in a table}
-
-\cref{fig:result_rfc_01_result_displacement}, depicts the evolution of the
-depth of penetration of the cylinder, compared against the experimental result
-by \citet{xxxx}, numerical techniques of boundary element method
-(BEM)(\cite{xxx}) and delta-plus SPH (\cite{xxx}). From
-\cref{fig:result_rfc_01_result_displacement}, we find that the current solver
-matches well with the experimental result and also converges while increasing
-the resolution.
 \begin{figure}[!htpb]
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{figures/skillen_2013_water_entry_half_buoyant/penetration_vs_t}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-0}
+    \includegraphics[width=0.6\textwidth]{images/results_dem_2_validation_particle_wall_impact/schematic}
+    \subcaption{
+    }\label{fig:result:dem-1a}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{figures/skillen_2013_water_entry_neutrally_buoyant/penetration_vs_t}
-    \subcaption{}%\label{fig:rings:ipst-nu-0.47-1}
+    \includegraphics[width=0.6\textwidth]{figures/benchmark_4_sw_colliding_oblique/angle_vs_ang_vel.pdf}
+    \subcaption{
+    }\label{fig:result:dem-1b}
   \end{subfigure}
-  \caption{}
-\label{fig:result_rfc_01_result_displacement}
+  \caption{(a) Schematic of particle-wall impact.  (b)
+ Variation of Angular velocity with impact angle.}
+\label{fig:result-dem-1}
 \end{figure}
+We consider the collision of a spherical particle with wall with different
+incident angles and a constant velocity in magnitude. This test case is useful
+in testing the tangential interaction modeling of our DEM solver.  The schematic
+of the body and wall is shown in \cref{fig:result:dem-1a}.  The radius of the
+impacting particle is $2.5 \times 10^{-3}$ m and is made of aluminium oxide. The
+particle has a Young's modulus of $3.8 \times 10^{11}$ N\,m\textsuperscript{-2}, a
+Poisson's ratio of $0.23$, and a density of $4,000$
+kg\,m\textsuperscript{-3}. The wall's Young's modulus is $70\times 10^{9}$
+N\,m\textsuperscript{-2}, with a Poisson's ratio of $0.25$.  The impact velocity
+has a magnitude of $3.9$ m\,s\textsuperscript{-1}. The coefficient of friction
+between the wall and the particle is $0.092$.  In
+\cref{fig:result:dem-1b}, we show variation of the
+rebound angular velocity with the incident impact angle, compared to
+experimental data.
 
 \FloatBarrier%
-\subsection{RFC validation 2: Two tandem particles entering into a tank}
-\label{sec:rfc_validation_2_single_particle_entry}
+\subsection{Single particle entering into a tank}
+\label{sec:rfc_validation_1_single_particle_entry}
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=0.6\textwidth]{
+      images/rfc_01_skillen_2013_particle_entry_in_hs_tank/Skillen_2013_particle_entry_in_hs_tank}
+    \subcaption{}\label{fig:result:rfc-1a}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/skillen_2013_water_entry_half_buoyant/penetration_vs_t}
+    \subcaption{}\label{fig:result:rfc-1b}
+  \end{subfigure}
+  \caption{(a) Schematic of cylinder disc entering a 2D tank.  (b) Evolution of
+    the penetration depth of the cylinder disc with time. }
+\label{fig:result-rfc-1}
+\end{figure}
+In this example we examine the motion of a circular disc descending into a
+steady hydrostatic tank. \Cref{fig:result:rfc-1a} illustrates the initial setup,
+with the cylinder positioned $0.5$ meters from the free surface. The cylinder's
+radius is $0.11$ meters, and density of $500$ kg\,m\textsuperscript{-3}.
+\Cref{fig:result:rfc-1b}, depicts the evolution of the depth of penetration of
+the cylinder compared to experimental results and other numerical techniques.
 
-\FloatBarrier%
+% \FloatBarrier%
 \subsection{Mixing of spherical particles in a fluid tank}
-\label{sec:mixing-spherical-particles-in-fluid-tank}
+\label{sec:mixing-spherical-particles-in-fluid-tank-homogeneous}
+In this section, we investigate particle dispersion within a tank under various
+stirrer velocities. Each circular particle has a radius of $0.055$ m, with a
+total of $54$ particles.  The density of the particles is taken as $1050$
+kg\,m\textsuperscript{-3}.  After allowing the particles to settle for $1$
+second, the stirrer oscillates throughout the fluid length. We examine three
+stirrer speeds.  The schematic of the figure is given in
+\Cref{fig:1-mixing-1-a}.  \Cref{fig:1-mixing-1-b,fig:1-mixing-1-c,fig:1-mixing-1-d},
+illustrate the distribution of particles within a fluid tanker under the
+influence of a stirrer at different instants. From \Cref{fig:1-mixing-1},
+particles tend to aggregate and settle gradually into a clump at the center.
 
-\FloatBarrier%
-\subsection{Mixing of spherical particles of variable size in a fluid tank}
-\label{sec:mixing-spherical-particles-in-fluid-tank}
+\section{Conclusions}
+This study uses a fully resolved SPH-DEM solver to analyze mixing in a 2D tank
+with a stirrer.  SPH simulates the fluid, while DEM handles the
+spherical particles and their interactions.  We validated the SPH and DEM
+solvers independently and then validated the combined solver with specific test
+cases. Finally, we investigated how stirrer speed affects particle dispersion,
+finding that both low and high speeds affect the mixing of particles due to the
+recirculation and clump formation.
 
-\FloatBarrier%
-\section{Conclusions}
-\label{sec:conclusions}
+% [!htpb]
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time0}
+    \subcaption{t = $0$ s}\label{fig:1-mixing-1-a}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time1}
+    \subcaption{t = $3$ s}\label{fig:1-mixing-1-b}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time2}
+    \subcaption{t = $6$ s}\label{fig:1-mixing-1-c}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time3}
+    \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-d}
+  \end{subfigure}
+  \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+    three time steps, where the stirrer is oscillating at a velocity of $1$
+    m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+    represents the velocity magnitude.}
+\label{fig:1-mixing-1}
+\end{figure}
+% \begin{figure}[!htpb]
+%   \centering
+%   \begin{subfigure}{0.48\textwidth}
+%     \centering
+%     \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_2/time1}
+%     \subcaption{t = $3$ s}\label{fig:1-mixing-1-a}
+%   \end{subfigure}
+%   \begin{subfigure}{0.48\textwidth}
+%     \centering
+%     \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_2/time2}
+%     \subcaption{t = $6$ s}\label{fig:1-mixing-1-b}
+%   \end{subfigure}
 
-% \section*{References}
+%   \begin{subfigure}{0.48\textwidth}
+%     \centering
+%     \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_2/time3}
+%     \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-c}
+%   \end{subfigure}
+%   \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+%     three time steps, where the stirrer is oscillating at a velocity of $3$
+%     m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+%     represents the velocity magnitude.}
+% \label{fig:1-mixing-2}
+% \end{figure}
+% \begin{figure}[!htpb]
+%   \centering
+%   \begin{subfigure}{0.48\textwidth}
+%     \centering
+%     \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_3/time1}
+%     \subcaption{t = $3$ s}\label{fig:1-mixing-1-a}
+%   \end{subfigure}
+%   \begin{subfigure}{0.48\textwidth}
+%     \centering
+%     \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_3/time2}
+%     \subcaption{t = $6$ s}\label{fig:1-mixing-1-b}
+%   \end{subfigure}
+
+%   \begin{subfigure}{0.48\textwidth}
+%     \centering
+%     \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_3/time3}
+%     \subcaption{t = $9.9$ s}\label{fig:1-mixing-1-c}
+%   \end{subfigure}
+%   % \begin{subfigure}{0.45\textwidth}
+%   %   \centering
+%   %   \includegraphics[width=1.0\textwidth]{figures/dinesh_2024_mixing_with_stirrer_homogeneous_2d/case_1/time0}
+%   %   \subcaption{t = $7.38$ ms}\label{fig:1-mixing-1-d}
+%   % \end{subfigure}
+%   \caption{Snapshots of fluid, stirrer and the rigid circular particles at
+%     three time steps, where the stirrer is oscillating at a velocity of $5$
+%     m\,s\textsuperscript{-1}. The colour contour of the fluid particles
+%     represents the velocity magnitude.}
+% \label{fig:1-mixing-3}
+% \end{figure}
+
+% \section*{Acknowledgments}
+
+% Acknowledgments of your work.
+%
+% \begin{thebibliography}{99}
+% 	\bibitem{Paper}
+% 	AutorA, A., AutorB, B., Title of the paper
+% 	{\em Name of the Journal}, Volume(Number):Initial Page--Final Page, Year.
+
+% 	\bibitem{Book} BookAuthor, A., Title of the Book. City, Editorial, Year.
+% \end{thebibliography}
 
 \bibliographystyle{model6-num-names}
-\bibliography{references}
+% \bibliography{references}
+
 \end{document}
-
-% ============================
-% Table template for reference
-% ============================
-% \begin{table}[!ht]
-%   \centering
-%   \begin{tabular}[!ht]{ll}
-%     \toprule
-%     Quantity & Values\\
-%     \midrule
-%     $L$, length of the domain & 1 m \\
-%     Time of simulation & 2.5 s \\
-%     $c_s$ & 10 m/s \\
-%     $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
-%     Reynolds number & 200 \& 1000 \\
-%     Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
-%     Smoothing length factor, $h/\Delta x$ & 1.0\\
-%     \bottomrule
-%   \end{tabular}
-%   \caption{Parameters used for the Taylor-Green vortex problem.}%
-%   \label{tab:tgv-params}
-% \end{table}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% fill-column: 78
-%%% End:

### 2024-08-13 manuscript/paper.tex
Update manuscript

@@
 
-  \title{{DEM}-{SPH} study of particles dispersion in fluid}
+  \title{{DEM}-{SPH} study of particle dispersion in fluid}
   \author[xxx]{Dinesh Adepu\corref{cor1}}
-  \ead{d.dinesh@surrey.ac.uk}
+  \ead{d.adepu@surrey.ac.uk}
   \author[xxx]{Chuan Yu Wu}
   % \ead{XXX}
-\address[xxx]{School of Chemistry and Chemical Engineering, University of Surrey}
+\address[xxx]{School of Chemistry and Chemical Engineering, University of Surrey, Guildford, GU2 7XH, UK}
 
@@
 \begin{abstract}
-  Mixing powdered substances in tanks using a stirrer is a common occurrence
-  across various industries. Typically, this phenomenon is studied numerically
-  due to the complex nonlinear physics involved. In our current study, we have
-  developed a solver combining Smoothed Particle Hydrodynamics (SPH) and
-  Discrete Element Method (DEM) to investigate the mixing behavior of rigid
-  circular particles within a tank under the influence of a stirrer operating
-  at different speeds.  The SPH method governs the fluid phase, while the
-  dynamics and interactions of particles are captured by the DEM. We achieve a
-  fully resolved coupling between solid particles and fluid particles by
-  discretizing solid particles into dummy SPH particles. Our validation
-  process includes verifying the fluid solver's accuracy through a Poiseuille
-  problem and validating the DEM solver by benchmarking interactions between
-  two particles and particle-wall impacts.  The coupled model's is validated
-  by simulating single-particle entry in a 2D steady tank and a cube settling
-  in a tank, which is a 3D case. Following validation, we proceed with the
-  mixing study. We conduct two simulations: one with spherical particles of
-  uniform radius and another with particles having two different radius.  Our
-  findings reveal that as for lower stirrer speeds, particles tend to
-  aggregate initially and remain in the center. However, with further increase
-  in stirrer speed, particles tend to accumulate near the tank corners due to
-  the circulation induced in the fluid due to the stirrer motion. We use an
-  open-source software, PySPH, adapting and integrating the coupled model to
-  conduct the current study.
+  Mixing powdered substances in stirring tanks is a common occurrence across
+  various industries. In our current study, we developed a solver combining
+  Smoothed Particle Hydrodynamics (SPH) and Discrete Element Method (DEM) to
+  investigate the mixing behavior of particles in a tank under the influence
+  of a stirrer operating at different speeds.  The SPH method governs the
+  fluid phase, while the dynamics and interactions of particles are captured
+  by DEM. We achieve a fully resolved coupling between solid particles and
+  fluid particles by discretizing solid particles into dummy SPH
+  particles. Validation was performed, including verifying the fluid solver's
+  accuracy through a Poiseuille problem and validating the DEM solver by
+  benchmarking interactions between two particles and particle-wall impacts.
+  The coupled model is validated by simulating single-particle entry in a
+  steady tank in 2D and a cube settling in a tank in 3D. Using the validated
+  model, we conduct two simulations: one with spherical particles of uniform
+  radius and another with particles having two different radius.  Our results
+  reveal that at lower stirrer speeds, particles tend to aggregate
+  initially and remain in the center. However, with the increase in
+  stirrer speed, particles tend to accumulate near the tank corners due to the
+  circulation induced in the fluid due to the stirrer motion.
 \end{abstract}
@@
 Particle dispersion is a fundamental physical phenomenon encountered in
-various industries where powder and fluid interactions are pivotal.  Petroleum
-industry \cite{wang2023developments}, the transport of bodies in internal
-systems \cite{Dai2021}, debris flow \cite{Qingyun2022}, the food processing
-industry \cite{Karunasena2014}, and ice-sea modeling \cite{Mintu2018} are a
-few areas to mention.  In many processes the mixing of powder with fluid using
-a stirrer are commonplace \cite{li2022study}.  \Cref{fig:gloabl_body_frame_rb}
-illustrates a sample particle dispersion problem studied in the current work.
-While experimental investigation of such processes is often impractical due to
-their highly nonlinear nature, numerical methods offer a viable alternative.
-While these systems are studied with numerical methods, they are a part of
-two-way coupling models. In numerical method approach, one can employ either a
-mesh-based or meshless technique to study the current phenomena.
+various industries where powder and fluid interactions are pivotal.  Control
+of water flooding in petroleum industry \cite{wang2023developments}, the
+transport of bodies in internal systems \cite{Dai2021}, debris flow
+\cite{Qingyun2022}, the food processing industry \cite{Karunasena2014}, and
+ice-sea modeling \cite{Mintu2018} are a few examples to mention.  In many
+processes, the mixing of powder with fluid using a stirrer are commonplace
+\cite{li2022study}.  \Cref{intro:schematic} illustrates a sample particle
+dispersion problem.  While experimental investigation of such processes is
+often impractical due to their highly nonlinear nature, numerical methods
+offer a viable alternative.  While these systems are studied with numerical
+methods, they are generally treated as a two-way coupling problem. In
+numerical method approach, one can employ either a mesh-based or meshless
+technique to study these phenomena.
 
@@
 The combination of Discrete Element Method (DEM) for solid particle
-interactions and Computational Fluid Dynamics (CFD) for fluid modeling
-is a classic approach in handling particulate flow problem. In
-mesh-based modeling, lattice Boltzmann method (LBM)
-\cite{xiong2014lbm} and finite volume method (FVM) \cite{kloss2012models} are
-utilized to handle the fluid dynamics. Similarly, in meshless schemes like
-Smoothed Particle Hydrodynamics (SPH) \cite{peng2021fully},
-Moving Particle Semi-implicit (MPS), and Particle Finite Element
-Method (PFEM) \cite{li2019modeling, franci2020pfem}, handles the fluid
-dynamics.
+interactions and Computational Fluid Dynamics (CFD) for fluid modeling is a
+classic approach in handling particulate flow problem. In mesh-based modeling,
+lattice Boltzmann method (LBM) \cite{xiong2014lbm} and finite volume method
+(FVM) \cite{kloss2012models} are utilized to handle the fluid
+dynamics. Similarly, in meshless schemes, Smoothed Particle Hydrodynamics
+(SPH) \cite{peng2021fully}, Moving Particle Semi-implicit (MPS), and Particle
+Finite Element Method (PFEM) \cite{li2019modeling, franci2020pfem}, are
+adopted to handle the fluid dynamics.
 
@@
   trujillo2020smooth} and mesh-based \cite{van2008numerical, ma2022review}
-CFD-DEM techniques.  In addition to the study mono-sized particle behaviour in
-a fluid \cite{trujillo2020smooth}, research such as
-\cite{brosh2014accelerating} and \cite{peng2021fully} explore wide particle
-size distributions with CFD-DEM and SPH-DEM respectively.  Regarding
-non-Newtonian fluid modelling in mesh-based schemes, works like
-\cite{li2018dam} are notable and in meshless schemes, \cite{peng2021fully} is
-notable. \citet{zhu2008discrete} and \citet{ma2022review} delve into
-investigations on spherical and non-spherical particles respectively within
-CFD-DEM frameworks.  Meshless CFD-DEM, though fruitful, encounters challenges
-in handling problems with free surfaces and becomes computationally demanding
-with a large number of solid particles, especially in fully resolved
-coupling. In contrast, SPH offers advantages in such scenarios due to its
-inherent capability in handling free surfaces and adeptness in modeling large
-mesh deformation problems, facilitating the incorporation of novel physics.
+techniques.  In addition to study mono-sized particle behaviour in a fluid
+\cite{trujillo2020smooth}, research, such as \cite{brosh2014accelerating} and
+\cite{peng2021fully}, also explore wide particle size distributions with
+CFD-DEM and SPH-DEM respectively.  Regarding non-Newtonian fluid modelling in
+mesh-based schemes, works like \cite{li2018dam} are notable and in meshless
+schemes, \cite{peng2021fully} is notable. \citet{zhu2008discrete} and
+\citet{ma2022review} delve into investigations on spherical and non-spherical
+particles respectively within CFD-DEM frameworks.  Mesh based CFD-DEM, though
+fruitful, encounters challenges in handling problems with free surfaces and
+becomes computationally demanding with a large number of solid particles,
+especially in fully resolved coupling. In contrast, SPH offers advantages in
+such scenarios due to its inherent capability in handling free surfaces and
+adeptness in modeling large mesh deformation problems, facilitating the
+incorporation of novel physics.
 
@@
 physics, non-Newtonian fluid flows \cite{peng2021fully} among other areas
-\cite{monaghan2012smoothed}.  Various kind of particulate flows, involving,
+\cite{monaghan2012smoothed}.  Various kind of particulate flows, including,
 simple spherical particles mixing using unresolved coupling
 \cite{cleary2015prediction, markauskas2019coupled} and with debris flow
-\cite{canelas2016sph} with fully resolved coupling approach were analysed
+\cite{canelas2016sph} with fully resolved coupling approach, were analysed
 using SPH-DEM.  Handling particles of arbitrary shape in fluid flow is
 addressed in various works, including those by \citet{peng2021fully,
-  canelas2016sph, amicarelli2015smoothed}.  Several variants of SPH, such as
-WCSPH \cite{peng2021fully, cleary2015prediction}, and ISPH
-\cite{asai2021fluid}, are utilized for modeling fluid flow with particulate
-flows. The coupling between fluid and rigid bodies in the fully resolved
-category employs techniques such as the fixed ghost particle technique
-\cite{canelas2016sph, asai2021fluid}, single layers of dummy SPH particles
-\cite{peng2021fully}, and simple repulsive forces
-\cite{monaghan2009sph}. Coupling between SPH fluid particles and solid
+  canelas2016sph}, and \citet{amicarelli2015smoothed}.  Several variants of
+SPH, such as weakly compressible SPH (WCSPH) \cite{peng2021fully,
+  cleary2015prediction}, and ISPH \cite{asai2021fluid}, are utilized for
+modeling fluid flow with particulate flows. The coupling between fluid and
+rigid bodies in the fully resolved category employs techniques such as the
+fixed ghost particle technique \cite{canelas2016sph, asai2021fluid}, single
+layers of dummy SPH particles \cite{peng2021fully}, and simple repulsive
+forces \cite{monaghan2009sph}. Coupling between SPH fluid particles and solid
 structures discretized as vertex edges is also proposed by
@@
 studies are conducted by \citet{ng2021numerical}. Interaction between rigid
-bodies of arbitrary sizes is addressed using various techniques, such as those
-discussed in papers by \citet{asai2021fluid}, \citet{peng2021fully},
-\citet{canelas2016sph}.
-
-In the current work we consider the particle dispersion within a large-scale
-under stirrer mixing phenomenon. We employ Smoothed Particle Hydrodynamics
-(SPH) to model fluid dynamics and the Discrete Element Method (DEM) to handle
-the dynamics and contact interactions among spherical particles. The
-interaction between solids and fluids is modelled using a fixed ghost particle
-approach, ensuring a fully resolved simulation. We validate the fluid solver
+bodies of arbitrary sizes is addressed using various techniques. For example,
+\citet{asai2021fluid} utilize an energy-tracking impulse method, while
+\citet{peng2021fully} apply a surface mesh-based Discrete Element Method
+(SMR-DEM) to handle collisions.
+
+Mixing of particles in a tank with stirrer is modelled with an unresolved
+SPH-DEM model by \citet{zhu2021virtual}. While the interaction between two
+solid particles is handled using a linear model. A similar study is carried
+out to study the mixing of particles in a rotating drum by \citet{he2018gpu}
+using unresolved SPH-DEM model. Here, the authors use non-linear contact force
+model, which captures the force model accurately.  While using a fully
+resolved SPH-DEM coupling solver, particle dispersion has been studied in
+\cite{ng2021numerical,canelas2016sph,canelas2017resolved,peng2021fully}, where
+the interaction between the solid particle and the fluid is handled using
+ghost particles placed on the solid particle. In works of unresolved coupling,
+the interaction among the solid particles is handled using the discretized
+ghost points with a modified DEM model. However, fully resolved coupled works
+have only been applied to works with arbitrary shaped bodies, and to mainly
+ocean engineering problems \cite{canelas2016sph,canelas2017resolved} but not
+for particle mixing in tank.  In the current work, we study the circular
+particle mixing in stirring tanks.  We employ a fully resolved coupled SPH-DEM
+model, however, unlike previous fully resolved approaches
+\cite{ng2021numerical,canelas2016sph,canelas2017resolved,peng2021fully}, we
+only utilize the discretized ghost particles placed on the circular solid
+particle for interaction with the fluid, but not for solid solid
+interaction. The solid-solid interaction is carried out using the traditional
+DEM methodology \cite{cundall_discrete_1979}. We validate the fluid solver
 independently using Poiseuille flow and the DEM solver separately using
 fundamental benchmarks such as particle-particle and particle-wall
-impacts. Subsequently, the fully resolved coupled SPH-DEM solver is validated
-using three benchmarks: a single particle entering, two particles settling,
-and a forced wedge entry into a steady hydrostatic tank. Upon confirming the
-fidelity of the solver, we proceed with analyzing the mixing behavior of
-various spherical particles influenced by a stirrer in a tank. We investigate
-scenarios involving particles of different densities, stirrer velocities, and
-variable sizes as part of our case study. The development work is conducted
-using PySPH\cite{ramachandran2021pysph}, an open-source code available at
-\url{https://github.com/pypr/pysph}.  We modify the current codebase to
-integrate implementations of the Discrete Element Method (DEM) and the
-Smoothed Particle Hydrodynamics (SPH) coupled with DEM model for our ongoing
-research. To ensure reproducibility, we utilize the automan package
-\cite{ramachandran2018automan} to automate all results generated in the
-current manuscript, aiming for a reproducible research approach.
-
-The structure of this paper is as follows: In
-\cref{sec:fluid-modeling}, we explain the numerical method used to model fluid
-dynamics. \Cref{sec:rbd} outlines the equations governing the dynamics
-of rigid bodies and the contact force model employed to resolve collisions
-among them. The coupling between rigid spherical particles and the fluid is
-detailed in \cref{sec:rfc}. Our results are presented in
-\cref{sec:results}, where various problems from the literature are simulated to
-validate the current solver, and particle dispersion is examined.
+impacts. Subsequently, the fully resolved coupled SPH-DEM solver is validated.
+
+Upon confirming the fidelity of the solver, we proceed with analyzing the
+mixing behavior of various spherical particles influenced by a stirrer in a
+tank. We investigate scenarios involving particles of different densities,
+stirrer velocities, and variable sizes as part of our case study. The
+development work is conducted using PySPH\cite{ramachandran2021pysph}, an
+open-source code available at \url{https://github.com/pypr/pysph}.  We modify
+the current codebase to integrate implementations of the DEM and the SPH
+coupled with DEM model for our ongoing research. To ensure reproducibility, we
+utilize the automan package \cite{ramachandran2018automan} to automate all
+results generated in the current manuscript, aiming for a reproducible
+research approach.
+
+% \begin{itemize}
+% \item
+% \item \cite{zhu2021virtual} uses unresolved coupling, with contact between the
+%   particles being a linear model. Mixing in a tank with stirrer.
+% \item \cite{he2018gpu} uses unresolved coupling, with contact between the
+%   particles being a Hertz model, considering the real material properties of
+%   the interacting particles. Rotating drum mixing.
+% \item tong2018scale uses unresolved coupling, with contact between the
+%   particles being a linear model. Studies mixing in tank.
+% \item Circular particle dispersion study SPH-DEM-VCPM studies
+%   \citet{ng2021numerical}, Fully resolved coupling, with particles interacting
+%   among themselves using a linear force model, the interaction between two
+%   solid particles is handled using the dummy points of VCPM.
+% \item Circular particle dispersion study SPH-DEM-VCPM studies
+%   \citet{ng2021numerical}, Fully resolved coupling, with particles interacting
+%   among themselves using a linear force model, the interaction between two
+%   solid particles is handled using the dummy points of VCPM.
+% \item canelas2016sph, canelas2017resolved, peng2021fully model transport of
+%   rigid body of circular and arbitrary shape in a fluid flow, mainly applied to
+%   areas of ocean engineering and not anything related to spherical particle
+%   mixing.  \citet{ng2021numerical} assumes the particles to be elastic and
+%   models it with VCPM method, and those discretized VCPM notes also acts as
+%   SPH dummy particles and rigid fluid coupling is carried out using that.
+% \item Though fully resolved coupling works have been existing in the
+%   literature the interaction among the solid particles are handled through the
+%   dummy particles being discretized. Using the ghost particles, the contact
+%   force between the solid particles has been handled, where both linear and
+%   nonlinear contact force models are studied. While the contact force
+%   coefficients are calibrated for the distributed contact (DCDEM).
+% \item In the current work, we develop a coupled SPH-DEM solver, to model the
+%   particle dispersion within a large-scale under stirrer mixing phenomenon.
+% \item We adopt a fully coupled approach to model the interaction between the
+%   solid particles and the fluid unlike the unresolved studies.
+% \item The interaction between the solid particles is handled using the DEM
+%   model, however, we will use the center of the solid bodies to handle the
+%   contact, and not the dummy particles as used in \cite{}canelas2016sph,
+%   \cite{canelas2017resolved}, \cite{peng2021fully}. This provides us with more accurate
+%   contact force modeling, with a nonlinear force model.
+% \end{itemize}
+
+% In the current work we consider the particle dispersion within a large-scale
+% under stirrer mixing phenomenon. We employ Smoothed Particle Hydrodynamics
+% (SPH) to model fluid dynamics and the Discrete Element Method (DEM) to handle
+% the dynamics and contact interactions among spherical particles. The
+% interaction between solids and fluids is modelled using a fixed ghost particle
+% approach, ensuring a fully resolved simulation. We validate the fluid solver
+% independently using Poiseuille flow and the DEM solver separately using
+% fundamental benchmarks such as particle-particle and particle-wall
+% impacts. Subsequently, the fully resolved coupled SPH-DEM solver is validated
+% using three benchmarks: a single particle entering, two particles settling,
+% and a forced wedge entry into a steady hydrostatic tank. Upon confirming the
+% fidelity of the solver, we proceed with analyzing the mixing behavior of
+% various spherical particles influenced by a stirrer in a tank. We investigate
+% scenarios involving particles of different densities, stirrer velocities, and
+% variable sizes as part of our case study. The development work is conducted
+% using PySPH\cite{ramachandran2021pysph}, an open-source code available at
+% \url{https://github.com/pypr/pysph}.  We modify the current codebase to
+% integrate implementations of the Discrete Element Method (DEM) and the
+% Smoothed Particle Hydrodynamics (SPH) coupled with DEM model for our ongoing
+% research. To ensure reproducibility, we utilize the automan package
+% \cite{ramachandran2018automan} to automate all results generated in the
+% current manuscript, aiming for a reproducible research approach.
+
+The structure of this paper is as follows: In \cref{sec:fluid-modeling}, we
+explain the numerical method used to model fluid dynamics. \Cref{sec:rbd}
+outlines the equations governing the dynamics of rigid bodies and the contact
+force model employed to resolve collisions among them. The coupling between
+rigid spherical particles and the fluid is detailed in
+\cref{sec:rfc}. \cref{sec:integration} discusses the time integration scheme
+employed in the current work.  \cref{sec:validation}, where various problems
+from the literature are simulated to validate the current solver.  Mixing
+behaviour of spherical particles in a stirring tank is examined in
+\Cref{sec:results}.
 
@@
 In the current work, we follow a weakly-compressible SPH approach to model the
-fluid. The continuum in SPH is modeled using particles, which has physical
+fluid. The continuum in SPH is modeled using particles, which have physical
 properties such as mass, velocity, and these particles interact based on the
@@
 \end{equation}
-where $\eta$ is the kinematic viscosity of the fluid, $p$ is the pressure,
+where $\eta$ is the dynamic viscosity of the fluid, $p$ is the pressure,
 $\delta_{ij}$ is the Kronecker delta function.
@@
 mass and the kernel values of the discretized particles. Assume that the
-domain is discretized into N particles with mass $m_i$ and volume
-$V_i$, We have
+domain is discretized into N particles with mass $m_a$ and volume
+$V_a$, We have
 \begin{equation}
   \label{eq:mass_repr}
-  m_i = V_i \> \rho_i.
+  m_a = V_a \> \rho_a.
 \end{equation}
@@
   \label{eq:discrete_form}
-  A_i = \sum_{j \in \text{Neigh}(i)}\> \frac{m_j}{\rho_j} A_j\> W(\ten{x}_i - \ten{x}_j, h),
-\end{equation}
-where $A(\boldsymbol{x}_i) = A_i$ is the value of the field property of
-particle i, similarly for $A_j$. Here, $\text{Neigh}(i)$ is the neighbours of
-particle $i$.  A symmetric derivative approximation~\cite{Violeau16} is given
-as,
-\begin{equation}
-  \nabla A(\ten{x}_i) = \rho_i \sum_{j} m_j \left(\frac{A_i}{\rho_i^2} + \frac{A_j}{\rho_j^2}\right) \nabla W_{ij}.
+  A_a = \sum_{b \in \text{Neigh}(a)}\> \frac{m_b}{\rho_b} A_b\> W(\ten{x}_a - \ten{x}_b, h),
+\end{equation}
+where $A(\boldsymbol{x}_a) = A_a$ is the value of the field property of
+particle $a$, similarly for $A_b$. $\text{Neigh}(a)$ is the neighbours of
+particle $a$ and $W(\ten{x}_a - \ten{x}_b, h)$ is the kernel value, with $h$
+being the smoothing length. In the current work we used Quintic
+spline~\cite{Violeau16} in all our simulation cases.  A symmetric derivative
+approximation~\cite{Violeau16} is given as,
+\begin{equation}
+  \nabla A(\ten{x}_a) = \rho_a \sum_{b \in \text{Neigh}(a)} m_b \left(\frac{A_a}{\rho_a^2} + \frac{A_b}{\rho_b^2}\right) \nabla W_{ab}.
 \end{equation}
@@
 
-An approximation of the divergence operator is used to discretize the
-\cref{eq:ce}.  It is given as,
-\begin{equation}
-  \label{intro:eq:sph-continu-div-final}
-  \nabla \cdot \ten{v}(\ten{x}_i) = \frac{1}{\rho_i} \sum_{j} m_j \left(\ten{v}_j - \ten{v}_i\right) \cdot \nabla W_{ij}.
-\end{equation}
-
 % \subsection{Discretized fluid governing equations}
 The SPH discretization of the continuity
-equation~\cref{eq:sph-discretization-continuity} is given as,
+equation~\cref{eq:ce} is given as,
 \begin{equation}
@@
 \end{equation}
+where $\ten{u}_{ab} = \ten{u}_a - \ten{u}_b$.
 
@@
   \frac{{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg)
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2} + \Pi_{ab}\bigg) \ten{I} \cdot
   \nabla_{a} W_{ab}
@@
 \end{multline}
-where $\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
-fluid. The viscous term in \Cref{eq:me} is discretized according to the
-formulation introduced in \cite{morris1997modeling}.
-
-We add to the momentum equation an additional artificial viscosity term
-$\Pi_{ab}$~\cite{monaghan-review:2005} to maintain the stability of the
-numerical scheme, given as,
+where $\ten{I}$ is the identity matrix. The viscous term in \Cref{eq:me} is discretized according to the
+formulation introduced in
+\cite{morris1997modeling}. $\Pi_{ab}$~\cite{monaghan-review:2005} is an
+artificial viscosity item to maintain the stability of the numerical scheme,
+given as,
 \begin{align}
@@
 $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$, $\bar{c}_{ab} = (c_a + c_b) / 2$, and
-$\alpha$ is the artificial viscosity parameter.  The pressure $p_a$ is evaluated
-using an equation of state:
+$\alpha$ is the artificial viscosity parameter, is taken to be $0.1$ in the current
+work. The pressure $p_a$ is evaluated using an equation of state:
 \begin{equation}
 \label{eqn:sph-eos}
-  p_a = K \bigg(\frac{\rho_a}{\rho_{0}} - 1 \bigg).
-\end{equation}
-Where, $K=\rho_0 \, c_0^2$ is bulk modulus of the body, with
-$c_0=10 \times V_{\text{max}}$ is speed of sound, while $\rho_0$ as the
+  p_a = \rho_0 \, c_0^2 \bigg(\frac{\rho_a}{\rho_{0}} - 1 \bigg).
+\end{equation}
+where, $c_0=10 \times V_{\text{max}}$ is speed of sound, while $\rho_0$ as the
 initial density of the particles.
@@
 The ghost particle approach proposed by \citet{Adami2012} is used to model the
-boundaries. We use three layers of ghost particles to model the solid wall.
-The properties of the solid wall are interpolated from the fluid particles.
+boundaries. To ensure kernel completion of the fluid particle near the
+boundary, we use three layers of ghost particles to model the solid wall.  The
+properties of the solid wall are interpolated from the fluid particles.
 
 When the viscous force is computed, the no slip boundary condition is used,
-where the velocity on the boundary set as,
+where the velocity ($\ten{u}_{\text{Ga}}$) on the boundary set as,
 \begin{equation}
@@
   \label{eq:rfc:balance_linear_mom}
-  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i,
+  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i + \ten{F}_{\text{contact}},
 \end{equation}
@@
 \end{equation}
-where $M$, $\ten{v}_{cm}$ are the mass and velocity of the center of mass of the rigid body.
-$\ten{F}_i, \teng{\tau}_{cm}, \ten{L} $ are force acting at point $i$, torque and
-angular momentum about the center of mass of the rigid body. In the current
-case, force acting on the particle $i$, $\ten{F}_i$, is due to the interaction
-with the other bodies and with the fluid particles, and any other body forces.
+where $M$, $\ten{v}_{cm}$ are the mass and velocity of the center of mass of
+the rigid body.  $\ten{F}_i, \teng{\tau}_{cm}, \ten{L} $ are the force acting at
+point $i$, torque and angular momentum about the center of mass of the rigid
+body. Where the rigid body is being sampled using ghost SPH particles. In the
+current case, force acting on the particle $i$, $\ten{F}_i$, is due to the
+interaction with the fluid particles and $\ten{F}_{\text{contact}}$ is the
+force acting on the solid body due to interaction with other solid bodies.
 The torque $\teng{\tau}_{cm}$ and angular momentum $\ten{L}$ are computed as,
@@
   \label{eq:rfc:torque}
- \teng{\tau}_{cm} = \sum_i \ten{F}_i \times (\ten{x}_{cm} - \ten{x}_{i}),
+  \teng{\tau}_{cm} = \sum_i \ten{F}_i \times (\ten{x}_{cm} - \ten{x}_{i}) + \ten{F}_{\text{contact}} \times (\ten{x}_{cm} - \ten{x}_{\text{contact}}),
 \end{equation}
@@
   \sum_i \; \ten{r}_i \times \; (\teng{\omega} \times \ten{r}_i)
-  = \sum_i \; m_i \; [(\ten{r}_i \cdot \ten{r}_i) \ten{I} - \ten{r}_i \otimes \ten{r}_i].
-\end{equation}
-Here $\ten{x}_{cm}$ and $\omega$ are the position of the center of mass and
-angular velocity of the rigid body. $m_i$, $\ten{x}_{i}$, $\ten{r}_i$ are the
-mass, position of particle, and position of particle $i$ with respect to vector
-center of mass.
+  = \sum_i \; m_i \; [(\ten{r}_i \cdot \ten{r}_i) \ten{I} - \ten{r}_i \otimes \ten{r}_i],
+\end{equation}
+where $\ten{x}_{cm}$ and $\omega$ are the position of the center of mass and
+angular velocity of the rigid body. $m_i$, $\ten{x}_{i}$, $\ten{r}_i$,
+$\ten{x}_{\text{contact}}$ are the mass, position of ghost particle, position
+of ghost particle $i$ with respect to vector center of mass, and point of
+contact of two solid bodies interacting.
 
@@
 We use two coordinate frames to capture the dynamics of the rigid body, a
-global frame and a body frame as shown in
-\cref{fig:gloabl_body_frame_rb}. The body fixed frame, which moves with
+global frame and a local frame as shown in
+\cref{fig:gloabl_body_frame_rb}. The local fixed frame, which moves with
 rigid body is always located at the center of mass ($\ten{x}_{cm}$). The
@@
 \end{equation}
-The position of the discretized particle ($i$) in
+The position of the ghost particle ($i$) in
 \cref{fig:gloabl_body_frame_rb} belonging to the rigid body at time $t$ can be
@@
   \label{eq:rfc:rb_particle_pos_update}
-  \ten{r}_i = \ten{R} \overline{\ten{r}}_{i}.
-\end{equation}
-Here $\overline{\ten{r}}_{i}$ is the position of the particle $i$ about the body
-frame axis and remains constant through out the simulation. The rotation matrix
-$\ten{R}$ is used to bring the body frame position vector to the global frame
-$\ten{O}$. Similarly the velocity vector is computed as,
+  \ten{r}_i = \ten{R} \overline{\ten{r}}_{i},
+\end{equation}
+where $\overline{\ten{r}}_{i}$ is the position of the ghost particle $i$ about
+the body frame axis and remains constant through out the simulation. The
+rotation matrix $\ten{R}$ is used to bring the body frame position vector to
+the global frame $\ten{O}$. Similarly the velocity vector of the ghost
+particle is computed as,
 \begin{equation}
@@
 
+The total force ($\ten{F}$) acting on a solid body can be divided into the
+force acting on the ghost particle $i$ due to the interaction with the fluid,
+and the force acting on the solid body due to the interaction with the other
+solid body, given as
+\begin{eqnarray}
+  \label{eq:rfc:rb_particle_pos_update}
+  \ten{F} = \sum_i \ten{F}_{\text{rfc}}^i + \ten{F}_{\text{contact}}
+\end{eqnarray}
+\cref{sec:dem} explains the approach to compute force
+$\ten{F}_{\text{contact}}$ acting on the solid particle due to the interaction
+with the rigid bodies. The force $\ten{F}_{\text{rfc}}^i$ acting due to the
+interaction with the fluid particles follows \cref{sec:rfc}.
+
+\FloatBarrier%
+\subsection{Contact models}
+\label{sec:dem}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{images/spherical_particles_dem_representation}
+  \caption{Illustration of contact modelling between two rigid spherical
+    particles immersed in a fluid tank.}
+  \label{fig:spherical-particles-in-tank-dem}
+\end{figure}
+
+We resolve the contact among the spherical particles using the discrete
+element method \cite{luding_dem_2008}. In the current work we utilized a
+non-linear contact force model. In DEM, the force acting on a particle $a$ due
+to the interaction with the particle $b$ is resolved into a normal and
+tangential component. The normal force component represents a repulsive force,
+while the tangential component is used to model the friction between the
+interacting particles.  The normal force ($\teng{F}_a^{n}$) on particle $a$
+due to the interaction with the particles $b$ is given by a non-linear,
+Hetzian model \cite{brilliantov1996model}, including damping, is given as,
+\begin{equation}
+  \label{eq:contact-algorithm-normal}
+  \ten{F}_a^n = k_n \delta_{n} \ten{n} - \eta_n (\ten{v}_{ab} \cdot \ten{n}) \ten{n}.
+\end{equation}
+Here, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is the relative velocity of
+particle $a$ with respect to the contacting particle $b$,
+$\ten{n}$ normal unit vector passing from particle $b$ to $a$, and the overlap $\delta_{n}$ is computed
+using the radius of particle $a$ ($R_a$) and particle $b$ ($R_b$) as
+\begin{equation}
+  \label{eq:cf-overlap}
+  \delta_{n} = R_{a} + R_{b} - r_{ab},
+\end{equation}
+$k_n$ and $\eta_n$ are the normal spring stiffness and damping coefficient, which
+are computed using the material properties of the bodies in contact and the
+coefficient of restitution among the interacting bodies, given by:
+\begin{equation}
+  \label{eq:kf-stiffness}
+  k_n = \frac{4}{3} \; E^{*} \; \sqrt{R^{*} \delta_n},
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \eta_n = -2 \sqrt{\frac{5}{6}} \beta \; \sqrt{S_n m^*},
+\end{equation}
+where
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \frac{1}{E^{*}} = \frac{1 -\nu_a^2}{E_a} + \frac{1 -\nu_b^2}{E_b}
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \beta = \frac{\ln{e}}{\ln{e}^2 + \pi},
+\end{equation}
+here, $e$ is the coefficient of restitution.
+\begin{equation}
+  \label{eq:kf-stiffness}
+  R^{*} = \frac{R_a R_b}{R_a + R_b}
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  m^{*} = \frac{m_a m_b}{m_a + m_b}
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  S_n = 2 E^{*} \sqrt{R^{*} \delta_n}
+\end{equation}
+
+\subsection{Tangential force computation}
+\label{sec:tangential-force-computation}
+To handle the frictional contact, we associate a tangential spring attached to
+particle $a$ and particle $b$ to compute the tangential force, which initially has
+a magnitude of zero ($|\Delta \textit{\textbf{l}}_a|=0$). The tangential spring
+is activated when the particle comes into contact with particle $b$. The
+tangential force is history-dependent. The contact friction force is
+proportional to the tangential displacement, which is integrated over
+the contact time as
+\begin{equation}
+  \label{eq:tangential-force}
+  \ten{F}_{a}^{t^{n+1}} =
+  -k_t \Delta \textit{\textbf{l}}_a^{\,n + 1} - \eta_t \ten{v}_t =
+  -k_t \big[\big(\Delta {\textit{\textbf{l}}}_a^{\,n} \
+  + \ten{v}_{ab}^{n + 1} \Delta t\big) \cdot \ten{t}_a^{n + 1} \big] \
+  \ten{t}_a^{n + 1} - \eta_t \ten{v}_t,
+\end{equation}
+where $\Delta t$ is the time step,
+and $k_t$ is the tangential spring stiffness coefficient. The tangential unit
+vector is computed by,
+\begin{equation}
+  \label{eq:tangential-vect}
+  \ten{t}_a = \frac{\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}) \ten{n}}{|\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}) \ten{n}|}.
+\end{equation}
+The tangential spring stiffness ($k_t$) and the tangential damping coefficient
+$\eta_t$ are given as:
+\begin{equation}
+  \label{eq:kf-stiffness}
+  k_t = 8 \; G^{*} \; \sqrt{R^{*} \delta_n},
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \eta_t = -2 \sqrt{\frac{5}{6}} \beta \; \sqrt{S_t m^*},
+\end{equation}
+with $G^*$ and $S_t$ are given as,
+\begin{equation}
+  \label{eq:kf-stiffness}
+  \frac{1}{G^{*}} = \frac{2 (2 - \nu_a) (1 + \nu_a)}{E_a} +  \frac{2 (2 - \nu_b) (1 + \nu_b)}{E_b},
+\end{equation}
+\begin{equation}
+  \label{eq:kf-stiffness}
+  S_t = 8 G^{*} \sqrt{R^{*} \delta_n},
+\end{equation}
+where, $G$ is the shear modulus of the particles, $\nu$ is the Poisson's ratio.
+
+The tangential force is coupled to the normal force through the Coulomb's law,
+\begin{equation}
+  \label{eq:Coulomb-law}
+  \ten{F}_{a}^{t} = \min(\mu |\ten{F}_{a}^{n}|, |\ten{F}_{a}^{t}|) \
+  \frac{\ten{F}_{a}^{t}}{|\ten{F}_{a}^{t}|}.
+\end{equation}
+This allows us to impose the sliding friction condition between the
+interacting solids. Finally, the total force acting on the particle $a$ due to
+the interaction with particle $b$ is:
+\begin{equation}
+  \label{eq:contact-force}
+  \ten{F}_{a}^{\text{contact}} = \ten{F}_{a}^{n} + \ten{F}_{a}^{t}
+\end{equation}
+
+An equal and opposite force of the same magnitude is applied to
+particle $b$, given as
+\begin{equation}
+  \label{eq:contact-force}
+  \ten{F}_{b}^{\text{contact}} = - \ten{F}_{a}^{\text{contact}}.
+\end{equation}
+
+\FloatBarrier%
+\section{Solid fluid coupling}
+\label{sec:rfc}
+
+% Coupling equation with single particles he2017coupled
+% Coupling with dummy particles \cite{guan2024numerical}
+% A different coupling equation meng2022hydroelastic
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.22\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/real_spherical_particles}
+    \subcaption{A rigid spherical particle}%\label{fig:rings:ipst-nu-0.47-0}
+  \end{subfigure}\hspace{15mm}%
+  \begin{subfigure}{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/sph_sampled_spherical_particles}
+    \subcaption{A rigid spherical particle sampled with dummy SPH particles}%\label{fig:rings:ipst-nu-0.47-1}
+  \end{subfigure}
+  \caption{A rigid particle being discretized into a number of dummy SPH
+    particles, to handle the interaction with surrounding fluid.}
+\label{fig:real_particle_sph_sampling}
+\end{figure}
+To calculate the force exerted on the rigid particle due to the surrounding
+fluid, we employ a method involving the sampling of the spherical particle
+using dummy SPH particles, depicted in
+\cref{fig:real_particle_sph_sampling}. These SPH particles are evenly
+distributed and remain fixed, moving in tandem with the velocity of the
+solid particle at any given location.  They serve as SPH boundary particles
+and contribute to the computation of fluid particle density and acceleration
+according to \Cref{eq:sph-discretization-continuity,eq:sph-momentum-fluid}.
+To establish the pressure of these SPH particles, we utilize the fixed ghost
+particle boundary technique outlined in \cref{sec:boundary_conditions}.
+
+With solid particles being discretized into SPH particles and immersed in
+fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{images/rfc_zoomed_combined}
+  \caption{Solid spherical particles sampled with dummy SPH particles being
+    immersed in a fluid tank.}
+  \label{fig:many_rb_in_fluid_sph_particles}
+\end{figure}
+The force on the fluid particle due to the
+interaction with the sampled dummy SPH particles is considered in the momentum
+\cref{eq:sph-momentum-fluid} and the continuity
+\cref{eq:sph-discretization-continuity}. The force acting on the sampled dummy
+SPH particle due to the interaction with the fluid is given by,
+\begin{equation}
+  \label{eq:rfc-force}
+  \ten{F}_{\text{rfc}}^i = -m_i \sum_{f} m_f \bigg(\frac{p_f}{\rho_{f}^2} +
+  \frac{p_i}{\rho_{i}^2}\bigg) \nabla_{i} W(x_{if}) +
+  m_i \sum_{f} m_f \frac{4 \eta \nabla_i W_{if}\cdot
+    \ten{r}_{if}}{(\rho_i + \rho_f) (r_{if}^2 + 0.01 h_{if}^2)} \ten{u}_{if}
+\end{equation}
+where, $m_i$ signifies the hydrodynamic mass of the sampled dummy SPH particle,
+and $\rho_i$ represents its hydrodynamic density. $m_f$, $p_f$ and
+$\rho_f$ are mass, pressure and density of the fluid particle.
+
+\FloatBarrier%
+\section{Time Integration}
+\label{sec:integration}
+
+The modeling of solid-solid interaction requires a smaller time step than the
+fluid. We choose the minimum of these two timesteps to move the system forward
+in time. For the numerical stability of fluid, the time step depends on the
+Courant–Friedrichs–Lewy (CFL) condition \cite{monaghan-review:2005} as,
+\begin{equation}
+  \label{eq:rfc:time-step-cfl}
+  \Delta t_{\text{fl}} = \mathrm{min} \bigg( 0.25 \; \frac{h}{c + |U|} ,  0.25 \; \frac{h^2}{\nu},  0.25 \; \frac{h^2}{g} \bigg),
+\end{equation}
+where $|U|$ is the maximum velocity magnitude, $c$ is the speed of sound
+typically chosen as $10 |U|$ for fluids in this work. For solid body, the time
+step is constrained \cite{cundall_discrete_1979} as,
+\begin{equation}
+  \label{eq:rfc:time-step-body-force}
+  \Delta t_{\text{rb}} \leq \frac{\pi}{50} \sqrt{\frac{m}{k_r}}.
+\end{equation}
+A minimum timestep is chosen as
+\begin{equation}
+  \label{eq:rfc:time-step-body-force}
+  \Delta t = min(\Delta t_{\text{fl}}, \Delta t_{\text{rb}}).
+\end{equation}
+
+\subsection*{Fluid particles update}
+We use the kick-drift-kick scheme \cite{monaghan-review:2005} for the time
+integration. We move the velocities of the fluid and the solid particles to
+half time step,
+\begin{equation}
+  \label{eq:velocity-update-stage-1}
+  \ten{u}_a^{t+\frac{1}{2} \Delta t} = \ten{u}_a^{t} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^t,
+\end{equation}
+here, $()_a^t$ represents the properties of particle $a$ at time $t$ and
+$()_a^{t+\frac{1}{2} \Delta t}$ corresponds to the halfway point between time
+$t$ and $t + \Delta t$. Then the time derivative of density is calculated using
+\cref{eq:sph-discretization-continuity}, with velocities at half time step
+employed for the calculation.  The updated density and particle position
+are determined by,
+\begin{equation}
+  \label{eq:density-update-stage-2}
+  \rho_{a}^{t+\Delta t} = \rho_{a}^{t} + \Delta t \; \bigg(\frac{d\rho_{a}}{dt}\bigg)^{t+\frac{1}{2} \Delta t},
+\end{equation}
+\begin{equation}
+  \label{eq:position-update-stage-2}
+  \ten{r}_{a}^{t+\Delta t} = \ten{r}_{a}^{t} + \Delta t \; \ten{u}_{a}^{t+\frac{1}{2}\Delta t}.
+\end{equation}
+%
+Finally, at new time-step particle position, the momentum velocity is updated
+\begin{equation}
+  \label{eq:velocity-update-stage-3}
+  \ten{u}_a^{t+\Delta t} = \ten{u}_a^{t+\frac{1}{2}\Delta t} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^{t+\frac{1}{2}\Delta t}.
+\end{equation}
+
+\subsection*{Solid particles update}
 We evolve the state of the rigid body through the integration of the
-\cref{eq:rfc:balance_linear_mom,eq:rfc:balance_angular_mom}. The linear velocity of the
-center of mass ($\ten{v}_{cm}$) and angular momentum ($\ten{L}$) at the next
-timestep are computed as,
+\cref{eq:rfc:balance_linear_mom,eq:rfc:balance_angular_mom}. Following the
+kick-drift-kick integration scheme, the linear velocity of the center of mass
+($\ten{v}_{cm}$) and angular momentum ($\ten{L}$) are first updated to half
+timestep as,
 \begin{equation}
   \label{eq:rfc:lin_vel_cm_update}
-  \ten{v}_{cm}^{n+1} = \ten{v}_{cm}^{n} + \frac{\ten{F}_{cm}}{M} \; \Delta t,
+  \ten{v}_{cm}^{t+\frac{1}{2} \Delta t} = \ten{v}_{cm}^{t} + \frac{\Delta t}{2} \frac{\ten{F}_{cm}}{M} \;
 \end{equation}
@@
   \label{eq:rfc:ang_mom_update}
-  \ten{L}^{n+1} = \ten{L}^{n} + \teng{\tau}_{cm} \; \Delta t.
-\end{equation}
-Here, $\ten{F}_{cm} = \sum_i \ten{F}_i$.
-
-The position of the center of mass and the rotation matrix ($\ten{R}$) are updated
-by,
+  \ten{L}^{t+\frac{1}{2} \Delta t} = \ten{L}^{t} + \frac{\Delta t}{2} \teng{\tau}_{cm} \;.
+\end{equation}
+Here, $\ten{F}_{cm} = \sum_i \ten{F}_i + \ten{F}_{\text{contact}}$.
+
+With the velocities at half time step, we update position of the center of
+mass and the rotation matrix ($\ten{R}$) to the next time step as,
 \begin{equation}
   \label{eq:rfc:lin_pos_cm_update}
-  \ten{x}_{cm}^{n+1} = \ten{x}_{cm}^{n} + \ten{v}_{cm}^{n} \; \Delta t,\\
-  \ten{R}^{n+1} = \ten{R}^{n} + \tilde{\teng{\omega}}^{n} \, \ten{R}^{n} \; \Delta t,
-\end{equation}
-where $\tilde{\teng{\omega}}^{n}$ is matrix formulation of angular velocity
-$\omega$. The angular velocity at the new time step is computed with
+  \ten{x}_{cm}^{t+\Delta t} = \ten{x}_{cm}^{t} + \ten{v}_{cm}^{t+\frac{1}{2} \Delta t} \; \Delta t,\\
+  \ten{R}^{t+ \Delta t} = \ten{R}^{t} + \tilde{\teng{\omega}}^{t+\frac{1}{2} \Delta t} \, \ten{R}^{t} \; \Delta t,
+\end{equation}
+where $\tilde{\teng{\omega}}^{t+\frac{1}{2} \Delta t}$ is matrix formulation of angular
+velocity $\omega$. Here, the angular velocity is computed with
 \begin{equation}
   \label{eq:rfc:ang_velocity_update}
-  \teng{\omega}^{n+1} = (\textit{\teng{I}}^{-1})^{n+1} \; \ten{L}^{n+1}.
+  \teng{\omega}^{t+\frac{1}{2} \Delta t} = (\textit{\teng{I}}^{-1})^{t} \; \ten{L}^{t+\frac{1}{2} \Delta t}.
 \end{equation}
@@
   \label{eq:rfc:moi_update}
-  (\textit{\teng{I}}^{-1})^{n+1} = \ten{R}^{n+1} \textit{\teng{\overline{I}}}^{-1} (\ten{R}^{n+1})^T.
+  (\textit{\teng{I}}^{-1})^{t} = \ten{R}^{t} \textit{\teng{\overline{I}}}^{-1} (\ten{R}^{t})^T.
 \end{equation}
@@
 
-The position and velocity of the particles of the rigid body are updated by
+The position and velocity of the ghost particles comprising the rigid body are
+updated based on the properties of the center of mass by
 \begin{eqnarray}
@@
 
-The force acting on particle $i$ is composed of interaction with the other rigid
-bodies, and the fluid, given as
-\begin{eqnarray}
-  \label{eq:rfc:rb_particle_pos_update}
-  \ten{F}_i = \ten{F}_{\text{Fl}}^i + \ten{F}_{\text{cont}}^i
-\end{eqnarray}
-We follow \cref{sec:dem} to compute force
-$\ten{F}_{\text{cont}}^a$ acting on particle $i$ due to the interaction with
-the rigid bodies. The force $\ten{F}_{\text{rfc}}^i$ acting due to the
-interaction with the fluid particles follows \cref{sec:rfc}.
-
-\FloatBarrier%
-\subsection{Contact models}
-\label{sec:dem}
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.7\textwidth]{images/spherical_particles_dem_representation}
-  \caption{Demonstration of contact handling between two rigid spherical
-    particles immersed in a fluid tank.}
-  \label{fig:spherical-particles-in-tank-dem}
-\end{figure}
-
-We resolve the contact among the spherical particles using the discrete
-element method \cite{luding_dem_2008}. In the current work we have utilized a
-non-linear contact force model. In DEM, the force acting on a particle $a$ due
-to the interaction with the particle $b$ is resolved into a normal and
-tangential component. The normal force component represents a repulsive force,
-while the tangential component is used to model the friction between the
-interacting particles.  The normal force ($\teng{F}_a^{n}$) on particle $a$
-due to the interaction with the particles $b$ is given by a non-linear,
-Hetzian model \cite{brilliantov1996model}, including damping is given as,
-\begin{equation}
-  \label{eq:contact-algorithm-normal}
-  \ten{F}_a^n = k_n \delta_{n} \ten{n} - \eta_n (\ten{v}_{ab} \cdot \ten{n}) \ten{n}.
-\end{equation}
-Here, $\ten{v}_{ab} = \ten{v}_{a} - \ten{v}_b$ is the relative velocity of
-particle $a$ with respect to the contacting particle $b$,
-$\ten{n}$ normal unit vector passing from particle $b$ to $a$, and the overlap $\delta_{n}$ is computed
-using the radius of particle $a$ ($R_a$) and particle $b$ ($R_b$) as
-\begin{equation}
-  \label{eq:cf-overlap}
-  \delta_{n} = R_{a} + R_{b} - r_{ab},
-\end{equation}
-$k_n$ and $\eta_n$ are the normal spring stiffness and damping coefficient, which
-are computed using the material properties of the bodies in contact and the
-coefficient of restitution among the interacting bodies, given by:
-\begin{equation}
-  \label{eq:kf-stiffness}
-  k_n = \frac{4}{3} \; E^{*} \; \sqrt{R^{*} \delta_n},
-\end{equation}
-\begin{equation}
-  \label{eq:kf-stiffness}
-  \eta_n = -2 \sqrt{\frac{5}{6}} \beta \; \sqrt{S_n m^*}.
-\end{equation}
-Where the other parameters are given as:
-\begin{equation}
-  \label{eq:kf-stiffness}
-  \frac{1}{E^{*}} = \frac{1 -\nu_a^2}{E_a} + \frac{1 -\nu_b^2}{E_b}
-\end{equation}
-\begin{equation}
-  \label{eq:kf-stiffness}
-  \beta = \frac{\ln{e}}{\ln{e}^2 + \pi},
-\end{equation}
-here, $e$ is the coefficient of restitution.
-\begin{equation}
-  \label{eq:kf-stiffness}
-  R^{*} = \frac{R_a R_b}{R_a + R_b}
-\end{equation}
-\begin{equation}
-  \label{eq:kf-stiffness}
-  m^{*} = \frac{m_a m_b}{m_a + m_b}
-\end{equation}
-\begin{equation}
-  \label{eq:kf-stiffness}
-  S_n = 2 E^{*} \sqrt{R^{*} \delta_n}
-\end{equation}
-
-\subsection{Tangential force computation}
-\label{sec:tangential-force-computation}
-To handle the frictional contact, we associate a tangential spring attached to
-particle $a$ and particle $b$ to compute the tangential force, which initially has
-a magnitude of zero ($|\Delta \textit{\textbf{l}}_a|=0$). The tangential spring
-is activated when the particle comes into contact with particle $b$. The
-tangential force is history-dependent. The contact friction force is
-proportional to the tangential displacement, which is integrated over
-the contact time as
-\begin{equation}
-  \label{eq:tangential-force}
-  \ten{F}_{a}^{t^{n+1}} =
-  -k_t \Delta \textit{\textbf{l}}_a^{\,n + 1} - \eta_t \ten{v}_t =
-  -k_t \big[\big(\Delta {\textit{\textbf{l}}}_a^{\,n} \
-  + \ten{v}_{ab}^{n + 1} \Delta t\big) \cdot \ten{t}_a^{n + 1} \big] \
-  \ten{t}_a^{n + 1} - \eta_t \ten{v}_t,
-\end{equation}
-where $\Delta t$ is the time step,
-and $k_t$ is the tangential spring stiffness coefficient. The tangential unit
-vector is computed by,
-\begin{equation}
-  \label{eq:tangential-vect}
-  \ten{t}_a = \frac{\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}) \ten{n}}{|\ten{v}_{ab} - (\ten{v}_{ab} \cdot \ten{n}) \ten{n}|}.
-\end{equation}
-The tangential spring stiffness ($k_t$) and the tangential damping coefficient
-$\eta_t$ are given as:
-\begin{equation}
-  \label{eq:kf-stiffness}
-  k_t = 8 \; G^{*} \; \sqrt{R^{*} \delta_n},
-\end{equation}
-\begin{equation}
-  \label{eq:kf-stiffness}
-  \eta_t = -2 \sqrt{\frac{5}{6}} \beta \; \sqrt{S_t m^*},
-\end{equation}
-with $G^*$ and $S_t$ are given as,
-\begin{equation}
-  \label{eq:kf-stiffness}
-  \frac{1}{G^{*}} = \frac{2 (2 - \nu_a) (1 + \nu_a)}{E_a} +  \frac{2 (2 - \nu_b) (1 + \nu_b)}{E_b},
-\end{equation}
-\begin{equation}
-  \label{eq:kf-stiffness}
-  S_t = 8 G^{*} \sqrt{R^{*} \delta_n},
-\end{equation}
-where, $G$ is the shear modulus of the particles, $\nu$ is the Poisson's ratio.
-
-The tangential force is coupled to the normal force through the Coulomb's law,
-\begin{equation}
-  \label{eq:Coulomb-law}
-  \ten{F}_{a}^{t} = \min(\mu |\ten{F}_{a}^{n}|, |\ten{F}_{a}^{t}|) \
-  \frac{\ten{F}_{a}^{t}}{|\ten{F}_{a}^{t}|}.
-\end{equation}
-This allows us to impose the sliding friction condition between the
-interacting solids. Finally, the total force acting on the particle $a$ due to
-the interaction with particle $b$ is:
-\begin{equation}
-  \label{eq:contact-force}
-  \ten{F}_{a}^{\text{cont}} = \ten{F}_{a}^{n} + \ten{F}_{a}^{t}
-\end{equation}
-
-An equal and opposite force of the same magnitude is applied to
-particle $b$, given as
-\begin{equation}
-  \label{eq:contact-force}
-  \ten{F}_{b}^{\text{cont}} = - \ten{F}_{a}^{\text{cont}}.
-\end{equation}
-
-\FloatBarrier%
-\section{Rigid fluid coupling}
-\label{sec:rfc}
-
-% Coupling equation with single particles he2017coupled
-% Coupling with dummy particles \cite{guan2024numerical}
-% A different coupling equation meng2022hydroelastic
-
-\begin{figure}[!htpb]
-  \centering
-  \begin{subfigure}{0.22\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/real_spherical_particles}
-    \subcaption{A rigid spherical particle}%\label{fig:rings:ipst-nu-0.47-0}
-  \end{subfigure}\hspace{15mm}%
-  \begin{subfigure}{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{images/rfc_explantion_schematic/sph_sampled_spherical_particles}
-    \subcaption{A rigid spherical particle sampled with dummy SPH particles}%\label{fig:rings:ipst-nu-0.47-1}
-  \end{subfigure}
-  \caption{A rigid particle being discretized into several dummy SPH
-    particles, to handle the interaction with surrounding fluid.}
-\label{fig:real_particle_sph_sampling}
-\end{figure}
-To calculate the force exerted on the rigid particle due to the surrounding
-fluid, we employ a method involving the sampling of the spherical particle
-using dummy Smoothed Particle Hydrodynamics (SPH) particles, depicted in
-\cref{fig:real_particle_sph_sampling}. These SPH particles are evenly
-distributed and remain stationary, moving in tandem with the velocity of the
-rigid particle at any given location.  They serve as SPH boundary particles
-and contribute to the computation of fluid particle density and acceleration
-according to \Cref{eq:sph-discretization-continuity,eq:sph-momentum-fluid}.
-To establish the pressure of these SPH particles, we utilize the fixed ghost
-particle boundary technique outlined in \cref{sec:boundary_conditions}.
-
-With rigid particles being discretized into SPH particles and immersed in
-fluid can be seen in \cref{fig:many_rb_in_fluid_sph_particles}.
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.7\textwidth]{images/rfc_zoomed_combined}
-  \caption{A rigid spherical particle sampled with dummy SPH particles being
-    immersed in a fluid tank. An SPH particle representation.}
-  \label{fig:many_rb_in_fluid_sph_particles}
-\end{figure}
-The force on the fluid particle due to the
-interaction with the sampled dummy SPH particles is considered in the momentum
-\cref{eq:sph-momentum-fluid} and the continuity
-\cref{eq:sph-discretization-continuity}. The force acting on the sampled dummy
-SPH particle due to the interaction with the fluid is given by,
-\begin{equation}
-  \label{eq:rfc-force}
-  \ten{F}_{\text{rfc}}^a = -m_a \sum_{f} m_f \bigg(\frac{p_f}{\rho_{f}^2} +
-  \frac{p_a}{\rho_{a}^2}\bigg) \nabla_{a} W(x_{af}) +
-  m_a \sum_{f} m_f \frac{4 \eta \nabla_a W_{af}\cdot
-    \ten{r}_{af}}{(\rho_a + \rho_f) (r_{af}^2 + 0.01 h_{af}^2)} \ten{u}_{af}
-\end{equation}
-where, $m_a$ signifies the hydrodynamic mass of the sampled dummy SPH particle,
-and $\rho_a$ represents its hydrodynamic density. While $m_f$, $p_f$ and
-$\rho_f$ are mass, pressure and density of the fluid particle.
-
-\FloatBarrier%
-\section{Time Integration}
-
-We use the kick-drift-kick scheme \cite{monaghan-review:2005} for the time integration. We move the
-velocities of the fluid and the solid particles to half time step,
-\begin{equation}
-  \label{eq:velocity-update-stage-1}
-  \ten{u}_a^{t+\frac{1}{2} \Delta t} = \ten{u}_a^{t} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^t,
-\end{equation}
-here, $()_a^t$ represents the properties of particle $a$ at time $t$ and
-$()_a^{t+\frac{1}{2} \Delta t}$ corresponds to the halfway point between time
-$t$ and $t + \Delta t$. Then the time derivative of density is calculated using the
-\cref{eq:sph-discretization-continuity}, with velocities at half time step
-employed for the calculation.  The updated density and particle position for
-the new time step are determined by,
-\begin{equation}
-  \label{eq:density-update-stage-2}
-  \rho_{a}^{t+\Delta t} = \rho_{a}^{t} + \Delta t \; \bigg(\frac{d\rho_{a}}{dt}\bigg)^{t+\frac{1}{2} \Delta t},
-\end{equation}
-\begin{equation}
-  \label{eq:position-update-stage-2}
-  \ten{r}_{a}^{t+\Delta t} = \ten{r}_{a}^{t} + \Delta t \; \ten{u}_{a}^{t+\Delta t}.
-\end{equation}
-%
-Finally, at new time-step particle position, the momentum velocity is updated
-\begin{equation}
-  \label{eq:velocity-update-stage-3}
-  \ten{u}_a^{t+\Delta t} = \ten{u}_a^{t+\frac{1}{2}\Delta t} + \frac{\Delta t}{2} \bigg(\frac{d\ten{u}_{a}}{dt}\bigg)^{t+\Delta t}.
-\end{equation}
-
-The modeling of rigid-rigid interaction requires a smaller time step than the
-fluid. We choose the minimum of these two timesteps to move the system forward
-in time. For the numerical stability of fluid, the time step depends on the
-Courant–Friedrichs–Lewy (CFL) condition \cite{monaghan-review:2005} as,
-\begin{equation}
-  \label{eq:rfc:time-step-cfl}
-  \Delta t_{\text{fluid}} = \mathrm{min} \bigg( 0.25 \; \frac{h}{c + |U|} ,  0.25 \; \frac{h^2}{\nu},  0.25 \; \frac{h^2}{g} \bigg),
-\end{equation}
-where $|U|$ is the maximum velocity magnitude, $c$ is the speed of sound
-typically chosen as $10 |U|$ for fluids in this work. For rigid body, the time
-step is constrained \cite{cundall_discrete_1979} as,
-\begin{equation}
-  \label{eq:rfc:time-step-body-force}
-  \Delta t_{\text{rb}} \leq \frac{\pi}{50} \sqrt{\frac{m}{k_r}}.
-\end{equation}
-A minimum timestep is chosen as
-\begin{equation}
-  \label{eq:rfc:time-step-body-force}
-  \Delta t = min(\Delta t_{\text{fluid}}, \Delta t_{\text{rb}}).
-\end{equation}
-
-\FloatBarrier%
-\section{Results}
-\label{sec:results}
+Finally, at new time-step particle position, the velocity and angular moment
+to the new time step are updated
+\begin{equation}
+  \label{eq:rfc:lin_vel_cm_update}
+  \ten{v}_{cm}^{t+\Delta t} = \ten{v}_{cm}^{t+\frac{1}{2} \Delta t} + \frac{\Delta t}{2} \frac{\ten{F}_{cm}}{M} \;
+\end{equation}
+\begin{equation}
+  \label{eq:rfc:ang_mom_update}
+  \ten{L}^{t+\Delta t} = \ten{L}^{t+\frac{1}{2} \Delta t} + \frac{\Delta t}{2} \teng{\tau}_{cm} \;.
+\end{equation}
+
+\FloatBarrier%
+\section{Model validation}
+\label{sec:validation}
 Initially, we validate our fluid solver through the resolution of the
@@
 coupled SPH-DEM solver with simulations involved like a circular particle
-entering a steady tank, a cube settling in a water tank.  Lastly, we
-investigate the mixing behavior of spherical particles under a stirrer,
-examining cases with varying particle diameters and stirrer speeds.
+entering a steady tank, a cube settling in a water tank.
 
@@
 
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $\rho$, Fluid density & $1000$ kg\,m\textsuperscript{-3} \\
+    $\alpha$, Artificial viscosity & $0$ \\
+    $\zeta$, Kinematic viscosity & $0.01$ m\textsuperscript{2}s\textsuperscript{-1}\\
+    $dx$, Particle spacing & $\frac{1}{60}$m \\
+    Time of simulation & 50 s \\
+    % Gravity $[g_x, g_y, g_z]$ & $[0.0, 0.0, 0.0]$\\
+    \bottomrule
+  \end{tabular}
+  \caption{Material and numerical parameters used for modeling of Poiseuille's
+    flow with SPH.}%
+  \label{tab:dem_validation_1}
+\end{table}
 \begin{figure}[!htpb]
@@
 \end{figure}
-We study unsteady flow between two infinite, parallel paltes at rest in
+We study unsteady flow between two infinite, parallel plates at rest in
 presence of pressure gradient to validate our fluid solver implementation.
@@
 exact conditions, the Navier-Stokes equations admit the time dependent
-solution given in \cref{eq:poiseuille_exact_soln}, as given by
-\citet{morris1997modeling}
+solution, as given by \citet{morris1997modeling} as,
 \begin{equation}
   \label{eq:poiseuille_exact_soln}
-  v_x(y, t) = \frac{F}{2 \nu}y(y - L) + \sum_{n=0}^{\infty}\frac{4FL^2}{\nu \pi^3 (2n + 1)^3} \sin\bigg(\frac{\pi y}{L} (2 n + 1) \bigg) \exp\bigg(\frac{ (2 n + 1)^2 \pi^2 \nu}{L^2} t\bigg)
-\end{equation}
-$\nu$ is kinematic viscosity ($\frac{\mu}{\rho_0}$). This test case serves to
+  v_x(y, t) = \frac{F}{2 \zeta}y(y - L) + \sum_{n=0}^{\infty}\frac{4FL^2}{\zeta \pi^3 (2n + 1)^3} \sin\bigg(\frac{\pi y}{L} (2 n + 1) \bigg) \exp\bigg(\frac{ (2 n + 1)^2 \pi^2 \zeta}{L^2} t\bigg)
+\end{equation}
+$\zeta$ is kinematic viscosity. This test case serves to
+%  kinematic viscosity ($\frac{\mu}{\rho_0}$)
 validate the no-slip boundary condition of our developed scheme. We use
@@
 \Cref{fig:poiseuille_soln_graph} depicts the variation of the u-velocity in
-y-direction, compared to the analytical formula given in
+y-direction, compared to the analytical solution given in
 \cref{eq:poiseuille_exact_soln}.  By observing
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.png}
+  \includegraphics[width=0.7\textwidth]{figures/plane_poiseuille_flow_2D/case_1/comparison.pdf}
   \caption{Velocity profile of the Poiseuille flow compared against the
@@
 
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $E$, Young's modulus & $48$ GPa \\
+    $\nu$, Poisson's ratio & $0.2$ \\
+    $\rho$, Density & $2800$ kg\,m\textsuperscript{-3} \\
+    $\mu$, Friction coefficient & $0$ \\
+    $e$, Coefficient of restitution & $1$ \\
+    Time of simulation & 80 $\mu$s \\
+    Gravity $[g_x, g_y, g_z]$ & $[0.0, 0.0, 0.0]$\\
+    \bottomrule
+  \end{tabular}
+  \caption{Material parameters used for the normal impact of spherical particle.}%
+  \label{tab:dem_validation_1}
+\end{table}
 \begin{figure}[!htpb]
@@
 moving towards each other with an initial velocity of $10$
-m\,s\textsuperscript{-1}.  Each particle has a radius of $0.01$ m and is composed
-of glass. The glass material has a Young's modulus of $4.8 \times 10^{10}$
-N\,m\textsuperscript{-2}, a Poisson's ratio of $0.2$, and a density of $2,800$
-kg\,m\textsuperscript{-3}.  For the current scenario, we assume there is no
-friction among the particles and no gravity acting on the particles.
-\Cref{fig:result:dem_1_force_vs_overlap} depicts the variation of the normal
-force and the amount of overlap, compared to the analytical findings presented
-in \cite{chung2011benchmark}. The force curve generated by our current
-implementation closely matches the analytical result, hereby confirming the
-validation of our DEM solver's model for normal contact force.
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.8\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_vs_overlap}
+m\,s\textsuperscript{-1}.  Each particle has a radius of $0.01$ m and is
+composed of glass. The material properties of the glass material are given in
+\Cref{tab:dem_validation_1}. \Cref{fig:result:dem_1_force_vs_overlap} depicts
+the variation of the normal force and the amount of overlap, compared to the
+analytical findings presented in \cite{chung2011benchmark}. The force curve
+generated by our model closely matches the analytical result, hereby
+confirming the validation of our DEM solver's model for normal contact force.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/benchmark_1_ss_colliding_elastic/fn_overlap}
   \caption{Variation of the normal impact force with overlap of the impacting
@@
 \FloatBarrier%
-\subsection{DEM validation 2: Particle wall impact}
+\subsection{DEM validation 2: Particle wall oblique impact}
 \label{sec:DEM_validation_2_particle_wall_impact}
+
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $E$, Particle's young's modulus & $380$ GPa \\
+    $\nu$, Particle's poisson's ratio & $0.23$ \\
+    $\rho$, Particle's density & $4000$ kg\,m\textsuperscript{-3} \\
+    $E$, Wall's young's modulus & $70$ GPa \\
+    $\nu$, Wall's poisson's ratio & $0.25$ \\
+    $\mu$, Friction coefficient between particle and the wall & $0.092$ \\
+    $e$, Coefficient of restitution & $1$ \\
+    Impact angle of particle & Varies \\
+    Time of simulation & 60 $\mu$s \\
+    gravity $[g_x, g_y, g_z]$ & $[0.0, 0.0, 0.0]$\\
+    \bottomrule
+  \end{tabular}
+  \caption{Material parameters of the sphere and the wall in particle wall
+    oblique impact problem.}%
+  \label{tab:dem_validation_2}
+\end{table}
 \begin{figure}[!htpb]
@@
 \cite{di2004comparison} and \cite{golshan2023lethe}.  The schematic of the
-body and wall is shown in \cref{fig:result:dem_sw_contact_schematic}.
-The dimensions and material properties of both the particle and the wall are
-set based on the study of \cite{di2004comparison,kharaz2001experimental}. The
+body and wall is shown in \cref{fig:result:dem_sw_contact_schematic}.  The
+dimensions and material properties of both the particle and the wall are set
+based on the study of \cite{di2004comparison,kharaz2001experimental}. The
 radius of the impacting particle is $2.5 \times 10^{-3}$ m and is made of aluminium
-oxide. The particle has a Young's modulus of $3.8 \times 10^{11}$
-N\,m\textsuperscript{-2}, a Poisson's ratio of $0.23$, and a density of $4,000$
-kg\,m\textsuperscript{-3}. The wall's Young's modulus is $70\times 10^{9}$
-N\,m\textsuperscript{-2}, with a Poisson's ratio of $0.25$.  The impact velocity
-has a magnitude of $3.9$ m\,s\textsuperscript{-1}. The coefficient of friction
-between the wall and the particle is $0.092$.
+oxide. The material properties of both the impacting particle and the wall are
+listed in \Cref{tab:dem_validation_2}.  The impact velocity has a magnitude of
+$3.9$ m\,s\textsuperscript{-1}.
 
@@
 experimental data from \citet{kharaz2001experimental}.  The angular velocity
-variation generated by our present implementation closely aligns with the
+variation generated by our model closely aligns with the
 experimental data, thereby validating the tangential
@@
   \caption{Variation of the rebound angular velocity of the impacting particle
-    with the incidence angle, compared to the experimental result and Lethe
-    DEM solver by \cite{golshan2023lethe}.}
+    with the incidence angle, compared to the experimental result and Lethe DEM \cite{golshan2023lethe}.}
   \label{fig:result:dem_sw_contact_omega_vs_theta}
@@
 \end{figure}
-
 To validate the rigid-fluid coupling solver, we examine the motion of a
@@
 different densities for the disc. This scenario has been investigated
-experimentally by
-\citet{greenhow1983nonlinear} and
-numerically by various studies, including
-\citet{sun2006water} using the Boundary Element Method
-and \cite{sun2018accurate} employing the $\delta^+$-SPH technique.
-\Cref{fig:results_rfc_01_skillen_2013}
-illustrates the initial setup, with the cylinder positioned $0.5$ meters from
-the free surface. The cylinder's radius is $0.11$ meters, and we investigate
-cases with densities of $500$ and $1000$ kg\,m\textsuperscript{-3}.
-The cylinder descends due to gravity into the tank. We perform tests using
-three different spacings to assess convergence: resolving the cylinder
-diameter into 20, 50, and 80 particles, resulting in spacings of $5.5 \times 10^{-3}$ m,
-$2.2 \times 10^{-3}$ m, and $1.375 \times 10^{-3}$ m respectively. We employ a kinematic viscosity of
-$1 \times 10^{-6}$ m\textsuperscript{2}/s for water and do not utilize artificial
-viscosity in this case. The simulation runs for a total time of $0.16$
-seconds, utilizing a smoothing length (h) equal to the particle spacing in
-each scenario. The speed of sound is set to ten times the maximum fluid
-velocity attainable.
+experimentally by \citet{greenhow1983nonlinear} and numerically by various
+studies, including \citet{sun2006water} using the Boundary Element Method and
+\cite{sun2018accurate} employing the SPH technique.
+\Cref{fig:results_rfc_01_skillen_2013} illustrates the initial setup, with the
+cylinder positioned $0.5$ meters from the free surface. The cylinder's radius
+is $0.11$ meters. Material and numertical peoperties of the fluid and the
+solid particle are specified in \Cref{tab:rfc_validation_1}. The cylinder
+descends due to gravity into the tank. We perform tests using three different
+spacings to assess convergence: resolving the cylinder diameter into 20, 50,
+and 80 particles respectively. The speed of sound is set to ten times the
+maximum fluid velocity attainable.
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $\rho_{\text{fluid}}$, Fluid density & $1,000$ kg\,m\textsuperscript{-3} \\
+    $\rho_{\text{solid}}$, Solid density & $500$ and $1,000$ kg\,m\textsuperscript{-3} \\
+    $\alpha$, Artificial viscosity & $0.0$ \\
+    $\zeta$, Kinematic viscosity & $10^{-6}$ m\textsuperscript{2}s\textsuperscript{-1}\\
+    $dx$, Particle spacing & $5.5 \times 10^{-3}$ m, $2.2 \times 10^{-3}$ m, and
+$1.375 \times 10^{-3}$m \\
+    Time of simulation & $0.16$ s \\
+    Gravity $[g_x, g_y, g_z]$ & $[0.0, -9.81, 0.0]$\\
+    \bottomrule
+  \end{tabular}
+  \caption{Material and numerical parameters used for the solid particle
+    entry in a steady tank.}%
+  \label{tab:rfc_validation_1}
+\end{table}
 
@@
 side length of $20$ mm. While the dimentions of the water tank is 150 mm
-$\times$ 140 mm $\times$ 140 mm. While the water depth is taken as $131$ mm. The density
-of the water is taken as $1000$ kg\,m\textsuperscript{-3}, and the density of
-the cube is $2,120$ kg\,m\textsuperscript{-3}. The schemtic of the initial
-configuration is shown in \cref{fig:results_rfc_02_falling}. We show that the
-current solver can handle 3D problems with this test case.
+$\times$ 140 mm $\times$ 140 mm. While the water depth is taken as $131$ mm. The cube
+center is initially placed at a height of $131$ mm, immersed half way in
+water. The density of the water is taken as $1,000$ kg\,m\textsuperscript{-3},
+and the density of the cube is $2,120$ kg\,m\textsuperscript{-3}. The schemtic
+of the initial configuration is shown in \cref{fig:results_rfc_02_falling}. We
+show that the current solver can handle 3D problems with this test case.
 \begin{figure}[!htpb]
@@
 \FloatBarrier%
+\section{Results and discussion}
+\label{sec:results}
+We investigate the mixing behavior of spherical particles under a stirrer,
+examining cases with varying particle diameters and stirrer speeds.
+
 \subsection{Mixing of spherical particles in a fluid tank}
 \label{sec:mixing-spherical-particles-in-fluid-tank-homogeneous}
-
 In this section, we investigate particle dispersion within a tank under
 various stirrer velocities. Each circular particle has a radius of $0.055$ m,
-with a total of $54$ particles. The fluid's dimensions in the tank are set to
-a length of $3.3$ m and a height of $1.65$ m. The stirrer, positioned on the left
-side, has a height of $0.75$ m, half of which is submerged into the fluid, and
-a length of $0.11$ m. After allowing the particles to settle for $1$ second,
-the stirrer oscillates throughout the fluid length. We examine three stirrer
-speeds: $1$, $3$ m\,s\textsuperscript{-1}.  The schematic of the figure is
-given in \Cref{fig:schematic-Dinesh-mixer-homogeneous}. The solid particles
-have a Young's modulus of $10^{9}$ N\,m\textsuperscript{-2}, a Poisson's ratio
-of $0.23$ and a density of $1050$ kg\,m\textsuperscript{-3} is considered.
+with a total of $54$ particles. The tank are set to a length of $3.3$ m and a
+height of $1.65$ m. The stirrer, positioned on the left side, has a lenght of
+$0.75$ m, half of which is submerged into the fluid, and a width of $0.11$
+m. After allowing the particles to settle for $1$ second, the stirrer
+oscillates throughout the fluid length. We examine three stirrer speeds: $1$,
+$3$ m\,s\textsuperscript{-1}.  The schematic of the figure is given in
+\Cref{fig:schematic-Dinesh-mixer-homogeneous}. The solid particles have a
+Young's modulus of $10^{9}$ N\,m\textsuperscript{-2}, a Poisson's ratio of
+$0.23$, a density of $1050$ kg\,m\textsuperscript{-3}, and a friction
+coefficient of $0.5$ is assumed among the solid particles.
 \begin{figure}[!htpb]
@@
 \label{sec:mixing-spherical-particles-in-fluid-tank-inhomogeneous}
-In this section, similar to the case discussed in
-\Cref{sec:mixing-spherical-particles-in-fluid-tank-homogeneous}, we analyze circular
+In this section, we analyze mixing of circular
 particles with two different radii. These particles have a ratio of $1.2$
 between the larger and smaller particle, with the smaller particle having a
-radius of $0.11$ m. The schematic of the figure is provided in
+radius of $0.055$ m. The schematic of the figure is provided in
 \Cref{fig:schematic-Dinesh-mixer-inhomogeneous}
@@
 \label{sec:conclusions}
-In this study, mixing efficiency in a two-dimensional tank is examined using a
-similar stirrer type, employing a fully resolved SPH-DEM solver. The fluid
-phase is represented using a weakly compressible SPH formulation, while the
-interaction and dynamics of spherical particles are modeled using the Discrete
-Element Method (DEM). The interaction between the fluid and discrete particles
-is managed by associating the spherical particles with surrogate SPH
-particles. The coupled SPH-DEM solver is developed within the PySPH software
-framework \cite{ramachandran2021pysph}. Validation of the weakly compressible
-SPH method is performed using the Poiseuille flow problem, while the DEM
-solver is validated against particle-level benchmarks including head-on
-collisions between two spherical particles and particle-wall collisions. The
-validation of the coupled solver includes scenarios such as a circular
-particle entering a tank and a cube settling in a three-dimensional tank.  The
+In this study, the particle mixing efficiency in a two-dimensional fluid tank
+due to a stirrer is examined, employing a fully resolved SPH-DEM solver. The
+fluid phase is represented using a weakly compressible SPH formulation, while
+the interaction and dynamics of spherical particles are modeled using the
+Discrete Element Method (DEM). The interaction between the fluid and discrete
+particles is modelled by associating the spherical particles with surrogate
+SPH particles. The coupled SPH-DEM solver is developed within the PySPH
+software framework \cite{ramachandran2021pysph} and throughly validated.  The
 influence of stirrer speed on particle dispersion in a 2D tank was thoroughly
 investigated. Different stirrer speeds were examined, revealing distinct
-behaviors. At lower stirrer speeds, particles tended to aggregate and remain
+behaviours. At lower stirrer speeds, particles tended to aggregate and remain
 in center within the tank, influenced due to the surrounding fluid
 velocity. While, higher stirrer speeds generated fluid circulation, causing
-some particles to settle at the tank corners, thus hindering their
-participation in mixing. The same behaviour was found even in scenarios involving
-particles with varying radii.
+some particles to settle at the tank corners, thus hindering their mixing. The
+same behaviour was found even in scenarios involving particles with different
+radii.
 

### 2024-08-13 automate.py

@@ -512,8 +512,8 @@ class Wu2014FallingSolid3D(Problem):
 
             plt.plot(t_current, z_current, label=self.case_info[name][1])
 
-        plt.xlabel('time')
-        plt.ylabel('z - amplitude')
+        plt.xlabel('time (seconds)')
+        plt.ylabel('z - amplitude (m)')
         plt.legend()
         # plt.tight_layout(pad=0)
         plt.savefig(self.output_path('z_vs_t.pdf'))
@@ -611,7 +611,6 @@ class Zhang2009SolidFluidMixtureVerification2d(Problem):
             file_names = os.listdir(source)
 
             for file_name in file_names:
-                # print(file_name)
                 if file_name.endswith((".jpg", ".pdf", ".png")):
                     # print(target_dir)
                     shutil.copy(os.path.join(source, file_name), target_dir)
@@ -677,7 +676,7 @@ class Dinesh2024MixingWithStirrerHomogeneous2d(Problem):
 
             for file_name in file_names:
                 # print(file_name)
-                if file_name.endswith((".jpg", ".pdf", ".png")):
+                if file_name.endswith((".jpg", ".pdf", ".png", ".mp4")):
                     # print(target_dir)
                     shutil.copy(os.path.join(source, file_name), target_dir)
 
@@ -745,7 +744,7 @@ class Dinesh2024MixingWithStirrerInHomogeneous2d(Problem):
 
             for file_name in file_names:
                 # print(file_name)
-                if file_name.endswith((".jpg", ".pdf", ".png")):
+                if file_name.endswith((".jpg", ".pdf", ".png", ".mp4")):
                     # print(target_dir)
                     shutil.copy(os.path.join(source, file_name), target_dir)
 

### 2024-08-13 code/dinesh_2024_mixing_with_stirrer_2d.py

@@ -628,6 +628,7 @@ class Problem(Application):
             tank = data['arrays']['tank']
             stirrer = data['arrays']['stirrer']
             rigid_body = data['arrays']['rigid_body_combined_slave']
+            rigid_body_master = data['arrays']['rigid_body_combined_master']
 
             c_min = min((fluid.u[:]**2. + fluid.v[:]**2. + fluid.w[:]**2.)**0.5)
             c_max = max((fluid.u[:]**2. + fluid.v[:]**2. + fluid.w[:]**2.)**0.5)
@@ -641,25 +642,75 @@ class Problem(Application):
             axs.scatter(tank.x, tank.y, s=s, c="k")
             axs.scatter(stirrer.x, stirrer.y, s=s, c="k")
             axs.scatter(rigid_body.x, rigid_body.y, s=s, c="r")
-            tmp = axs.scatter(fluid.x, fluid.y, s=s, c=vmag, vmin=c_min,
-                              vmax=c_max, cmap="jet", rasterized=True)
+            # # =====================================================
+            # # Color the rigid body particles based on the radius
+            # # =====================================================
+            # if len(rigid_body.x) < 1804:
+            #     axs.scatter(rigid_body.x, rigid_body.y, s=s, c="r")
+            # else:
+            #     self.dx = 0.11 / 6
+            #     x1, y1 = create_circle_1(0.11, self.dx)
+            #     small_radius_indices = np.array([])
+            #     for k in range(27):
+            #         small_radius_indices = np.concatenate([small_radius_indices, np.zeros_like(x1)])
+
+            #     x1, y1 = create_circle_1(1.2 * 0.11, self.dx)
+            #     big_radius_indices = np.array([])
+            #     for k in range(27):
+            #         big_radius_indices = np.concatenate([big_radius_indices, np.ones_like(x1)])
+            #     all_indices = np.concatenate([small_radius_indices, big_radius_indices])
+            #     small_indices = np.where(all_indices==0.)[0]
+            #     axs.scatter(rigid_body.x[small_indices], rigid_body.y[small_indices], s=s, color="red")
+
+            #     big_indices = np.where(all_indices==1.)[0]
+            #     axs.scatter(rigid_body.x[big_indices], rigid_body.y[big_indices], s=s, color="black")
+
+
+            # # print(all_indices)
+
+            # # get the body ids which have same radius
+
+
+            # # max_body_id = max(rigid_body.body_id)
[…]
